### 2022-08-16 analysis.qmd
wip

---
title: "Analysis"
format: html
---

```{r}
# Packages
library(scales)
library(patchwork)
library(ggh4x)
library(brms)
library(ggstance)
library(bayestestR)
library(tidyverse)

# Plotting theme
theme_set(
  theme_linedraw(
    base_size = 9,
    # base_family = Font
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
      axis.text = element_text(size = rel(0.75))
    )
)

# For ordering outcomes
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences"
)

# Directories for files
dir.create("models", FALSE)
dir.create("out", FALSE)
```

## Prepare data

```{r}
# Load and merge processed data
d_fb <- read_csv("data/fb.csv")
d_outcome <- read_rds("data/outcome.rds") %>% 
  mutate(outcome = factor(outcome, levels = oo))
d_pop <- read_rds("data/population.rds")

# Convert fb metrics into country-year proportions
d_fb <- d_fb %>% 
  left_join(d_pop) %>% 
  mutate(
    dau = dau / pop,
    mau = mau / pop
  )

# Merge
d <- left_join(d_fb, d_outcome) %>% 
  mutate(age = factor(age, levels = c("13-34", "35+")))
```

## Data figure

```{r}
# Figure of all variables over time
p_a <- d %>% 
  select(year:mau) %>% 
  pivot_longer(c(dau, mau), names_to = "outcome", values_to = "val") %>% 
  mutate(outcome = if_else(outcome == "dau", "Daily FB users", "Monthly FB users")) %>% 
  ggplot(aes(year, val, col = age, group = interaction(age, country))) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(
    "Percentage of population", 
    expand = expansion(.03),
    breaks = extended_breaks(),
    labels = ~percent(.)
  ) +
  scale_x_continuous(
    "Year", 
    breaks = seq(2008, 2018, by = 2), 
    minor_breaks = seq(2009, 2019, by = 2)
  ) +
  geom_line(size = .25) +
  facet_grid(age~outcome) +
  theme(
    legend.position = "none",
    axis.title.x = element_blank()
  )

p_b <- d %>% 
  select(-c(mau, dau)) %>% 
  # Exclude rows where FB data existed but not GWP data
  drop_na(val) %>% 
  # Actual lowest age in GWP
  mutate(age = factor(age, labels = c("15-34", "35+"))) %>% 
  ggplot(aes(year, val, col = age, group = interaction(age, country))) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(
    "Value", 
    expand = expansion(.01),
    breaks = extended_breaks()
  ) +
  scale_x_continuous(
    "Year", 
    breaks = seq(2008, 2018, by = 2), 
    minor_breaks = seq(2009, 2019, by = 2)
  ) +
  geom_line(size = .25) +
  facet_grid(age~outcome, labeller = as_labeller(~str_replace(., "_", " "))) +
  theme(legend.position = "none")

p_a / p_b
ggsave("out/Fig-data.png", width = 16, height = 10, units = "cm", dpi = 400)
```

## Models

```{r}
# Set global contrasts
options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))

# Prepare data
dm <- d %>% 
  # Centering predictors
  # Grand mean centering so both components are zero-centered
  mutate(across(c(dau, mau), ~. - mean(., na.rm = TRUE))) %>% 
  group_by(country) %>%
  mutate(
    # Between
    dau_cb = mean(dau, na.rm = TRUE),
    mau_cb = mean(mau, na.rm = TRUE),
    # Within
    dau_cw = dau - dau_cb, 
    mau_cw = mau - mau_cb
  ) %>% 
  ungroup() %>% 
  # Center year so that intercepts are at 2014
  mutate(year = year - 2014) %>% 
  # Remove rows where predictor existed but outcome didn't
  drop_na(val)

# Model formula
model_dau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + dau_cw) * age + dau_cb +
    ((year + dau_cw) * age | country),
  family = gaussian()
)
model_mau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + mau_cw) * age + mau_cb +
    ((year + mau_cw) * age | country),
  family = gaussian()
)

fits <- dm %>% 
  select(outcome, year, country, age, contains("_c"), val, se) %>% 
  group_by(outcome) %>% 
  nest() %>% 
  mutate(
    dau = map2(
      data, outcome,
      ~brm(
        model_dau,
        cores = 8, chains = 4, threads = 2,
        backend = "cmdstanr",
        adapt_delta = .95,
        iter = 4000,
        data = .x,
        file = str_glue("models/brm-dau-{.y}")
      )
    ),
    mau = map2(
      data, outcome,
      ~brm(
        model_mau,
        cores = 8, chains = 4, threads = 2,
        backend = "cmdstanr",
        adapt_delta = .95,
        iter = 4000,
        data = .x,
        file = str_glue("models/brm-mau-{.y}")
      )
    )
  )
```

```{r}
# Calculate contrasts for each outcome
h_dau <- c(
  "Average" = "dau_cw = 0",
  "13-34" = "dau_cw + dau_cw:age1 * -1 = 0",
  "35+" = "dau_cw + dau_cw:age1 * 1 = 0",
  "Between-country" = "dau_cb = 0"
)
h_mau <- c(
  "Average" = "mau_cw = 0",
  "13-34" = "mau_cw + mau_cw:age1 * -1 = 0",
  "35+" = "mau_cw + mau_cw:age1 * 1 = 0",
  "Between-country" = "mau_cb = 0"
)
coefs <- fits %>% 
  ungroup() %>% 
  mutate(h = if_else(predictor == "dau", list(h_dau), list(h_mau))) %>% 
  mutate(
    world = map2(
      fit, h,
      ~hypothesis(.x, .y) %>% 
        .[["hypothesis"]] %>% 
        tibble()
    ),
    country = map2(
      fit, h,
      ~hypothesis(.x, .y, scope = "coef", group = "country") %>% 
        .[["hypothesis"]] %>% 
        tibble()
    )
  ) %>% 
  select(-fit, -h)

coefs <- coefs %>% 
  pivot_longer(c(world, country)) %>% 
  unnest(value) %>% 
  mutate(country = if_else(name == "country", as.character(Group), "World")) %>% 
  mutate(country = fct_relevel(country, "World")) %>% 
  # Between country contrast not country-specific!
  filter(!(Hypothesis == "Between-country" & country != "World"))
coefs %>%   
  filter(Hypothesis %in% c("13-34", "35+")) %>% 
  mutate(
    panel_order = interaction(predictor, outcome, country),
    panel_order = fct_reorder(panel_order, Estimate)
  ) %>% 
  ggplot(aes(Estimate, panel_order, col = Hypothesis)) +
  scale_color_brewer("Age", palette = "Dark2") +
  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
  geom_pointrangeh(
    aes(xmin = CI.Lower, xmax = CI.Upper),
    size = .25, fatten = 2
    ) +
  facet_grid2(predictor~outcome, independent = "all", scales = "free") +
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    legend.position = "none"
    )
```

```{r}
coefs %>% 
  filter(Hypothesis == "Between-country")
```

### 2022-08-16 clean.qmd
wip

## Gallup World Poll

```{r}
library(haven)
library(knitr)
library(janitor)
library(here)
library(labelled)
library(countrycode)
library(tidyverse)
```

```{r gallup-codebook}
# Understand variables & values
# Codes NOTE 1: yes 2: no!
read_spss(
  "data-raw/Gallup/The_Gallup_042722.sav",
  n_max = 1,
  col_select = c(
    WPID, 
    # WP1220,  # Age
    WP16,
    WP60, WP61, WP63, WP65, WP67,
    WP68, WP69, WP70, WP71, WP74
  )
) %>%
  generate_dictionary()
```

```{r gallup-clean}
# First liberate the data from the slow SPSS file and save to disk
gwp_path <- here("data-raw/Gallup/gwp-processed.rds")
if (!file.exists(gwp_path)) {
  gwp <- read_spss(
    here("data-raw/Gallup/The_Gallup_042722.sav"),
    col_select = c(
      YEAR_CALENDAR,
      COUNTRYNEW,
      WPID, WP1220, 
      WP16,
      WP60, WP61, WP63, WP65, WP67,
      WP68, WP69, WP70, WP71, WP74
    )
  )

  # Get rid of SPSS attributes
  gwp <- gwp %>%
    zap_labels() %>%
    zap_label() %>%
    zap_widths() %>%
    zap_formats()

  # Save into a good format
  write_rds(gwp, gwp_path)
} else {
  gwp <- read_rds(gwp_path)
}

# Rename and recode variables
gwp <- gwp %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  )

# Scale scores note rescaling
gwp <- gwp %>%
  mutate(
    Life_satisfaction = Life_satisfaction / 10,
    Negative_experiences =
      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
    Positive_experiences =
      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
  ) %>%
  select(-c(wp60:wp74))

# Categorize ages
gwp <- gwp %>%
  mutate(
    age = factor(if_else(age <= 34, "13-34", "35+"))
  )

# Some age values are missing, drop those
gwp <- drop_na(gwp, age)

# Include only years in fb data
gwp <- gwp %>% 
  filter(between(year, 2008, 2019))
```

```{r gallup-summarise}
gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  drop_na(val) %>% 
  group_by(country, year, age, outcome) %>%
  summarise(
    n = n(),
    se = sd(val, na.rm = TRUE) / sqrt(n),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()

# Note that if there is no response variance, SE will be zero, and if there is only 1 response, SE will be NA. Here we fix those by assigning them the maximum SE (0.5)
gwp <- gwp %>% 
  mutate(
    se = if_else(is.na(se) | se == 0, 0.5, se)
  )
```

```{r gwp-harmonise-countries}
# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising

# Harmonise old names and replace only if harmonised name found
gwp <- gwp %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  # Prevent north cyprus from becoming cyprus
  mutate(
    country_harmonised = ifelse(
      country == "Northern Cyprus",
      "Northern Cyprus",
      country_harmonised
    )
  ) %>%
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)
```

Limit to countries in FB data

```{r}
fb_countries <- c(
  'Argentina', 'Armenia', 'Australia', 'Austria', 'Bangladesh', 'Belgium', 'Bolivia', 'Bosnia', 'Brazil', 'Bulgaria', 'Costa Rica', 'Croatia', 'Cyprus', 'Denmark', 'Dominican Republic', 'Ecuador', 'Egypt', 'El Salvador', 'Finland', 'France', 'Germany', 'Greece', 'Guatemala', 'Haiti', 'Honduras', 'Hungary', 'India', 'Iraq', 'Ireland', 'Israel', 'Italy', 'Japan', 'Jordan', 'Kenya', 'Libya', 'Lithuania', 'Malawi', 'Malaysia', 'Mexico', 'Morocco', 'Mozambique', 'Netherlands', 'New Zealand', 'Nicaragua', 'Nigeria', 'North Macedonia', 'Norway', 'Pakistan', 'Panama', 'Paraguay', 'Peru', 'Poland', 'Portugal', 'Puerto Rico', 'Qatar', 'Serbia', 'Slovakia', 'Slovenia', 'South Africa', 'Spain', 'Sri Lanka', 'Sweden', 'Switzerland', 'Taiwan', 'Thailand', 'Tunisia', 'Turkey', 'UK', 'United Arab Emirates', 'Uruguay', 'US', 'Venezuela'
  )
gwp <- gwp %>% 
  filter(country %in% fb_countries)
```

Yearly population estimates from world bank, except Taiwan from Wikipedia.

```{r}
pop <- read_csv(
  "data-raw/wb/API_SP.POP.TOTL_DS2_en_csv_v2_4335082.csv", 
  skip = 3
)
pop <- pop %>% 
  select(
    country = `Country Code`,
    `2008`:`2019`
  ) %>% 
  mutate(
    country = countrycode(country, origin = "iso3c", destination = "cldr.short.en")
    ) %>% 
  filter(country %in% fb_countries) %>% 
  pivot_longer(`2008`:`2019`, names_to = "year", values_to = "pop") %>% 
  mutate(year = as.numeric(year))

tw <- tibble(
  country = "Taiwan",
  year = 2008:2019,
  pop = c(23037031, 23119772, 23162123, 23224912, 23315822, 23373517, 23433753, 23492074, 23539816, 23571227, 23588932, 23600903)
)
pop <- bind_rows(pop, tw)
```

```{r gallup-save}
# Save
dir.create("data", FALSE)
write_rds(gwp, "data/outcome.rds")
write_rds(pop, "data/population.rds")
```

### 2022-08-16 analysis.qmd
Adjust iterations

@@
         adapt_delta = .95,
-        iter = 4000,
+        iter = 3000,
         data = .x,

### 2022-08-16 analysis.qmd
Include gender

@@
 library(scales)
+library(knitr)
 library(patchwork)
@@
 )
+W <- 24
 
@@
 d_fb <- read_csv("data/fb.csv")
-d_outcome <- read_rds("data/outcome.rds") %>% 
+d_gwp <- read_rds("data/gwp.rds") 
+# d_gwp <- read_rds("data/gwp-SYNTHETIC.rds") # If real data not available
+d_gwp <- d_gwp %>% 
   mutate(outcome = factor(outcome, levels = oo))
@@
 # Merge
-d <- left_join(d_fb, d_outcome) %>% 
+d <- left_join(d_gwp, d_fb) %>% 
   mutate(age = factor(age, levels = c("13-34", "35+")))
@@
 # Figure of all variables over time
-p_a <- d %>% 
-  select(year:mau) %>% 
+p_a <- d_fb %>% 
   pivot_longer(c(dau, mau), names_to = "outcome", values_to = "val") %>% 
@@
   ) +
-  geom_line(size = .25) +
+  # Aggregate over sex
+  stat_summary(fun = mean, geom = "line", size = .25) +
   facet_grid(age~outcome, labeller = as_labeller(~str_replace(., "_", " "))) +
@@
 p_a / p_b
-ggsave("out/Fig-data.png", width = 16, height = 10, units = "cm", dpi = 400)
+ggsave("out/Fig-data.png", width = W, height = W*.66, units = "cm", dpi = 400)
 ```
@@
   val | se(se, sigma = TRUE) ~
-    (year + dau_cw) * age + dau_cb +
-    ((year + dau_cw) * age | country),
+    (year + dau_cw) * age * sex + dau_cb +
+    ((year + dau_cw) * age * sex | country),
   family = gaussian()
@@
   val | se(se, sigma = TRUE) ~
-    (year + mau_cw) * age + mau_cb +
-    ((year + mau_cw) * age | country),
+    (year + mau_cw) * age * sex + mau_cb +
+    ((year + mau_cw) * age * sex | country),
   family = gaussian()
@@
 fits <- dm %>% 
-  select(outcome, year, country, age, contains("_c"), val, se) %>% 
+  select(outcome, year, country, sex, age, contains("_c"), val, se) %>% 
   group_by(outcome) %>% 
@@
 
+## Forest plot
+
 ```{r}
@@
   ungroup() %>% 
+  pivot_longer(c(dau, mau), names_to = "predictor", values_to = "fit") %>% 
   mutate(h = if_else(predictor == "dau", list(h_dau), list(h_mau))) %>% 
@@
   ) %>% 
-  select(-fit, -h)
+  select(-fit, -h, -data)
 
@@
   filter(!(Hypothesis == "Between-country" & country != "World"))
-coefs %>%   
-  filter(Hypothesis %in% c("13-34", "35+")) %>% 
-  mutate(
-    panel_order = interaction(predictor, outcome, country),
-    panel_order = fct_reorder(panel_order, Estimate)
-  ) %>% 
-  ggplot(aes(Estimate, panel_order, col = Hypothesis)) +
-  scale_color_brewer("Age", palette = "Dark2") +
-  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
-  geom_pointrangeh(
-    aes(xmin = CI.Lower, xmax = CI.Upper),
-    size = .25, fatten = 2
-    ) +
-  facet_grid2(predictor~outcome, independent = "all", scales = "free") +
-  theme(
-    axis.ticks.y = element_blank(),
-    axis.text.y = element_blank(),
-    legend.position = "none"
-    )
+
+# Both predictor and outcome are 0-1, so scale can be interpreted as % change as a function of % change
 ```
@@
 coefs %>%   
-  filter(Hypothesis == "Between-country")
+  filter(Hypothesis %in% c("13-34", "35+")) %>% 
+  mutate(
+    predictor = if_else(
+      predictor == "dau", 
+      "Daily FB users", 
+      "Monthly FB users"
+    )
+  ) %>%
+  mutate(
+    # Order countries on increasing magnitude per panel
+    country_order = interaction(predictor, outcome, country),
+    country_order = as.numeric(fct_reorder(country_order, Estimate)),
+    # But also ensure that average ("World") is in bottom
+    country_order = if_else(
+      country == "World", country_order-10000, country_order
+    ),
+    country_order = factor(country_order)
+  ) %>% 
+  ggplot(aes(Estimate, country_order, col = Hypothesis, shape = Star)) +
+  scale_y_discrete("Country", expand = expansion(.015)) +
+  scale_x_continuous(
+    "Estimated association"
+  ) +
+  scale_shape_manual(values = c(21, 19)) +
+  scale_color_brewer("Age", palette = "Dark2") +
+  scale_size_manual(values = c(0.75, 1.5)) +
+  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
+  geom_linerangeh(
+    aes(xmin = CI.Lower, xmax = CI.Upper),
+    size = .2, position = position_dodgev(.4)
+  ) +
+  geom_point(
+    fill = "white", aes(size = name),
+    position = position_dodgev(.4)
+  ) +
+  facet_grid2(
+    predictor~outcome, independent = "all", scales = "free",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(
+    axis.text.y = element_blank(),
+    legend.position = "none"
+  )
+
+ggsave("out/Fig-forest.png", width = W, height = W*.66, units = "cm", dpi = 400)
 ```
+
+```{r}
+# Between-country associations
+coefs %>% 
+  filter(Hypothesis == "Between-country") %>% 
+  select(predictor, outcome, Estimate, CI.Lower, CI.Upper) %>% 
+  arrange(predictor, outcome)
+  kable()
+```
+
+## Conditional effects plot
+
+```{r}
+# Create a predictor table with evenly spaced mau_cw values for each country
+newx_country <- fits$data[[1]] %>% 
+  group_by(country, age, mau_cb) %>% 
+  filter(mau_cw %in% c(min(mau_cw), max(mau_cw))) %>% 
+  select(country, age, mau_cb, mau_cw) %>% 
+  # For above groupings, create a sequence of dau_cws from min to max
+  group_modify(
+    ~tibble(mau_cw = seq(min(.$mau_cw), max(.$mau_cw), length = 31))
+    ) %>% 
+  ungroup() %>% 
+  mutate(year = 0, se = 0)
+
+newx_world <- fits$data[[1]] %>% 
+  group_by(age) %>% 
+  filter(mau_cw %in% c(min(mau_cw), max(mau_cw))) %>% 
+  select(age, mau_cw) %>% 
+  # For above groupings, create a sequence of mau_cws from min to max
+  group_modify(
+    ~tibble(mau_cw = seq(min(.$mau_cw), max(.$mau_cw), length = 31))
+    ) %>% 
+  ungroup() %>% 
+  mutate(mau_cb = 0, year = 0, se = 0)
+
+newy <- fits %>% 
+  mutate(
+    country = map(
+      mau, 
+      ~bind_cols(newx_country, fitted(.x, newx_country))
+      ),
+    world = map(
+      mau, 
+      ~bind_cols(newx_world, fitted(.x, newx_world, re_formula = NA))
+      )
+  ) %>% 
+  select(outcome, country, world)
+```
+
+```{r}
+newy %>% 
+  pivot_longer(c(country, world)) %>% 
+  unnest(value) %>% 
+  ungroup() %>% 
+  mutate(country = if_else(name == "world", "World", country)) %>% 
+  ggplot(aes(mau_cw, Estimate, group = country, col = age, fill = age)) +
+  scale_color_brewer(
+    "Age", 
+    palette = "Dark2", 
+    aesthetics = c("color", "fill")
+  ) +
+  scale_y_continuous(
+    "Estimated outcome",
+    breaks = extended_breaks()
+  ) +
+  scale_x_continuous(
+    "Country-mean deviated monthly FB users",
+    breaks = extended_breaks(),
+    labels = ~percent(.)
+  ) +
+  scale_size_manual(values = c(.2, .4)) +
+  geom_ribbon(
+    data = . %>% filter(name == "world"),
+    aes(ymin = Q2.5, ymax = Q97.5),
+    alpha = .2, col = NA
+  ) +
+  geom_line(aes(size = name)) +
+  facet_grid(
+    age~outcome, scales = "free_y",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(legend.position = "none")
+ggsave("out/Fig-mau-conditional.png", width = W, height = W*.5, units = "cm", dpi = 400)
+```

### 2022-08-16 clean.qmd
Include gender

@@
-## Gallup World Poll
+## Data cleaning
 
@@
   col_select = c(
-    WPID, 
+    WPID, WP1219,
     # WP1220,  # Age
@@
       COUNTRYNEW,
-      WPID, WP1220, 
+      WPID, WP1220, WP1219,
       WP16,
@@
     id = wpid,
+    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
     age = wp1220,
@@
 # Some age values are missing, drop those
-gwp <- drop_na(gwp, age)
+gwp <- drop_na(gwp, age, sex)
 
@@
   drop_na(val) %>% 
-  group_by(country, year, age, outcome) %>%
+  group_by(country, year, sex, age, outcome) %>%
   summarise(
@@
 
+### Synthetic GWP data
+
+Create synthetic GWP data.
+
+```{r mock-gwp-data}
+gwp_mock_path <- here("data/gwp-SYNTHETIC.rds")
+if (!file.exists(gwp_mock_path)) {
+  library(synthpop)
+  gwp_syn <- gwp %>% 
+    drop_na()
+  gwp_syn <- syn(
+    gwp_syn, 
+    method = c("", "", "", "", "", "normrank", "normrank", "normrank"),
+    maxfaclevels = 72
+  )
+  gwp_syn <- tibble(gwp_syn$syn)
+  saveRDS(gwp_syn, gwp_mock_path)
+}
+```
+
+### Population
+
 Yearly population estimates from world bank, except Taiwan from Wikipedia.
@@
 pop <- read_csv(
-  "data-raw/wb/API_SP.POP.TOTL_DS2_en_csv_v2_4335082.csv", 
+  "data/API_SP.POP.TOTL_DS2_en_csv_v2_4335082.csv", 
   skip = 3
@@
 
+### Save
+
 ```{r gallup-save}
@@
 dir.create("data", FALSE)
-write_rds(gwp, "data/outcome.rds")
+write_rds(gwp, "data/gwp.rds")
 write_rds(pop, "data/population.rds")

### 2022-08-19 ms.Rmd
Move analysis to reproducible rmarkdown manuscript

---
title: The association between Facebook adoption and well-being
shorttitle: Facebook and well-being
leftheader: Facebook and well-being
author: 
  - name: Matti Vuorre
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - Design
      - Administration
      - Analysis
      - Visualization
      - Writing
  - name: Andrew K. Przybylski
    affiliation: 1
    corresponding: yes
    address: Oxford Internet Institute, University of Oxford
    email: andy.przybylski@oii.ox.ac.uk
    role:
      - Design
      - Administration
      - Funding
      - Resources
      - Supervision
      - Visualization
      - Writing

affiliation:
  - id: 1
    institution: Oxford Internet Institute, University of Oxford

authornote: |
  \noindent \textbf{This manuscript is not yet peer-reviewed.}

  This research was supported by the Huo Family Foundation and Economic and Social Research Council Grant ES/T008709/1. All code supporting this manuscript is available at X. This draft is available under [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/) at X.

  The authors declare no conflicts of interest.

  The analytic code is available at (LINK). Researchers can contact Facebook (WHERE?) to access our code, the Facebook data, and a synthetic version of the Gallup data for reproducing and extending our analyses. 
  This study and methodology was reviewed and approved by the Oxford Internet Institute's Departmental Research Ethics Committee (SSH_OII_CIA_21_084).

abstract: | 
  Abstract.

keywords: well-being, social media
# wordcount: 
bibliography: "references.bib"
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: jou
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
editor_options: 
  chunk_output_type: console
always_allow_html: true
---

```{r setup, include = FALSE}
# Packages
library(papaja)
library(scales)
library(knitr)
library(patchwork)
library(ggh4x)
library(brms)
library(ggstance)
library(bayestestR)
library(tidyverse)

# For ordering outcomes
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences"
)

# Directories for files
dir.create("models", FALSE)
dir.create("out", FALSE)

# Document options
opts_chunk$set(
  eval = TRUE,
  cache = TRUE,
  include = FALSE,
  warning = FALSE,
  dpi = 300,
  fig.align = "center"
)

# For tables: Show NAs as blanks
options(knitr.kable.NA = '')

# Plotting options
theme_set(
  theme_linedraw(
    base_size = 8
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
      axis.text = element_text(size = rel(0.7)),
      axis.ticks = element_line(size = rel(0.4))
    )
)
W <- 24
```

```{r data-prepare}
# Load and merge processed data
d_fb <- read_csv("data/fb.csv")
d_gwp <- read_rds("data/gwp.rds") 
# d_gwp <- read_rds("data/gwp-SYNTHETIC.rds") # If real data not available
d_gwp <- d_gwp %>% 
  mutate(outcome = factor(outcome, levels = oo))
d_pop <- read_rds("data/population.rds")

# Convert fb metrics into country-year proportions
d_fb <- d_fb %>% 
  left_join(d_pop) %>% 
  mutate(
    dau = dau / pop,
    mau = mau / pop
  )

# Merge
d <- left_join(d_gwp, d_fb) %>% 
  mutate(age = factor(age, levels = c("13-34", "35+")))
```

```{r models}
# Set global contrasts
options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))

# Prepare data
dm <- d %>% 
  # Centering predictors
  # Grand mean centering so both components are zero-centered
  mutate(across(c(dau, mau), ~. - mean(., na.rm = TRUE))) %>% 
  group_by(country) %>%
  mutate(
    # Between
    dau_cb = mean(dau, na.rm = TRUE),
    mau_cb = mean(mau, na.rm = TRUE),
    # Within
    dau_cw = dau - dau_cb, 
    mau_cw = mau - mau_cb
  ) %>% 
  ungroup() %>% 
  # Center year so that intercepts are at 2014
  mutate(year = year - 2014) %>% 
  # Remove rows where predictor existed but outcome didn't
  drop_na(val)

# Model formula
model_dau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + dau_cw) * age * sex + dau_cb +
    ((year + dau_cw) * age * sex | country),
  family = gaussian()
)
model_mau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + mau_cw) * age * sex + mau_cb +
    ((year + mau_cw) * age * sex | country),
  family = gaussian()
)

fits <- dm %>% 
  select(outcome, year, country, sex, age, contains("_c"), val, se) %>% 
  group_by(outcome) %>% 
  nest() %>% 
  mutate(
    dau = map2(
      data, outcome,
      ~brm(
        model_dau,
        cores = 8, chains = 4, threads = 2,
        backend = "cmdstanr",
        adapt_delta = .95,
        iter = 3000,
        data = .x,
        file = str_glue("models/brm-dau-{.y}")
      )
    ),
    mau = map2(
      data, outcome,
      ~brm(
        model_mau,
        cores = 8, chains = 4, threads = 2,
        backend = "cmdstanr",
        adapt_delta = .95,
        iter = 3000,
        data = .x,
        file = str_glue("models/brm-mau-{.y}")
      )
    )
  )
```

# Results

```{r fig-data}
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 5.4
#| fig.cap: Time courses of key variables. A. Daily and monthly Facebook users in two age brackets for 72 countries from 2008 to 2019. B. Mean responses to three well-being scales in the Gallup World Poll from 72 countries from 2008 to 2019.

# Figure of all variables over time
p_a <- d_fb %>% 
  pivot_longer(c(dau, mau), names_to = "outcome", values_to = "val") %>% 
  mutate(outcome = if_else(outcome == "dau", "Daily FB users", "Monthly FB users")) %>% 
  mutate(panel = str_glue("{outcome} ({age})")) %>% 
  ggplot(aes(year, val, group = country)) +
  scale_y_continuous(
    "Percentage of population", 
    expand = expansion(.03),
    breaks = extended_breaks(),
    labels = ~percent(.)
  ) +
  scale_x_continuous(
    "Year", 
    breaks = seq(2008, 2018, by = 2), 
    minor_breaks = seq(2009, 2019, by = 2)
  ) +
  geom_line(size = .2, col = "gray30") +
  geom_smooth(group = 1, method = "gam", se = F) +
  facet_wrap("panel", nrow = 1) +
  theme(
    legend.position = "none",
    axis.title.x = element_blank()
  )

p_b <- d %>% 
  select(-c(mau, dau)) %>% 
  # Exclude rows where FB data existed but not GWP data
  drop_na(val) %>% 
  # Actual lowest age in GWP
  mutate(age = factor(age, labels = c("15-34", "35+"))) %>% 
  mutate(panel = str_glue("{outcome} ({age})")) %>% 
  ggplot(aes(year, val, group = country)) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(
    "Value", 
    expand = expansion(.01),
    breaks = extended_breaks()
  ) +
  scale_x_continuous(
    "Year", 
    breaks = seq(2008, 2018, by = 2),
    labels = ~str_replace(., "20", "'")
  ) +
  # Aggregate over sex
  geom_line(size = .2, col = "gray30") +
  geom_smooth(group = 1, method = "gam", se = F) +
  facet_grid(sex~panel, labeller = as_labeller(~str_replace(., "_", " "))) +
  theme(legend.position = "none")

(p_a / p_b) +
  plot_layout(heights = c(4, 6)) +
  plot_annotation(tag_levels = "A")
# ggsave("out/Fig-data.png", width = W, height = W*.66, units = "cm", dpi = 400)
```

```{r fig-forest-prepare}
# Calculate contrasts for each outcome
h_dau <- c(
  "Average" = "dau_cw = 0",
  "13-34_Female" = 
    "dau_cw + dau_cw:age1 * -1 + dau_cw:sex1 * -1 + dau_cw:age1:sex1 * 1 = 0",
  "13-34_Male" = 
    "dau_cw + dau_cw:age1 * -1 + dau_cw:sex1 * 1 + dau_cw:age1:sex1 * -1 = 0",
  "35+_Female" = 
    "dau_cw + dau_cw:age1 * 1 + dau_cw:sex1 * -1 + dau_cw:age1:sex1 * -1 = 0",
  "35+_Male" = 
    "dau_cw + dau_cw:age1 * 1 + dau_cw:sex1 * 1 + dau_cw:age1:sex1 * 1 = 0",
  "13-34" = "dau_cw + dau_cw:age1 * -1 = 0",
  "35+" = "dau_cw + dau_cw:age1 * 1 = 0",
  "Female" = "dau_cw + dau_cw:sex1 * -1 = 0",
  "Male" = "dau_cw + dau_cw:sex1 * 1 = 0",
  "Between-country" = "dau_cb = 0"
)
h_mau <- c(
  "Average" = "mau_cw = 0",
  "13-34_Female" = 
    "mau_cw + mau_cw:age1 * -1 + mau_cw:sex1 * -1 + mau_cw:age1:sex1 * 1 = 0",
  "13-34_Male" = 
    "mau_cw + mau_cw:age1 * -1 + mau_cw:sex1 * 1 + mau_cw:age1:sex1 * -1 = 0",
  "35+_Female" = 
    "mau_cw + mau_cw:age1 * 1 + mau_cw:sex1 * -1 + mau_cw:age1:sex1 * -1 = 0",
  "35+_Male" = 
    "mau_cw + mau_cw:age1 * 1 + mau_cw:sex1 * 1 + mau_cw:age1:sex1 * 1 = 0",
  "13-34" = "mau_cw + mau_cw:age1 * -1 = 0",
  "35+" = "mau_cw + mau_cw:age1 * 1 = 0",
  "Female" = "mau_cw + mau_cw:sex1 * -1 = 0",
  "Male" = "mau_cw + mau_cw:sex1 * 1 = 0",
  "Between-country" = "mau_cb = 0"
)
coefs <- fits %>% 
  ungroup() %>% 
  pivot_longer(c(dau, mau), names_to = "predictor", values_to = "fit") %>% 
  mutate(h = if_else(predictor == "dau", list(h_dau), list(h_mau))) %>% 
  mutate(
    world = map2(
      fit, h,
      ~hypothesis(.x, .y) %>% 
        .[["hypothesis"]] %>% 
        tibble()
    ),
    country = map2(
      fit, h,
      ~hypothesis(.x, .y, scope = "coef", group = "country") %>% 
        .[["hypothesis"]] %>% 
        tibble()
    )
  ) %>% 
  select(-fit, -h, -data)

coefs <- coefs %>% 
  pivot_longer(c(world, country)) %>% 
  unnest(value) %>% 
  mutate(country = if_else(name == "country", as.character(Group), "World")) %>% 
  mutate(country = fct_relevel(country, "World")) %>% 
  # Between country contrast not country-specific!
  filter(!(Hypothesis == "Between-country" & country != "World"))

# Both predictor and outcome are 0-1, so scale can be interpreted as % change as a function of % change
```

```{r fig-forest}
#| include: true

coefs %>%   
  filter(str_detect(Hypothesis, "_")) %>% 
  mutate(
    predictor = if_else(
      predictor == "dau", 
      "Daily FB users", 
      "Monthly FB users"
    )
  ) %>%
  separate(Hypothesis, c("Age", "Sex"), sep = "_") %>% 
  mutate(outcome = str_glue("{outcome} ({Age})")) %>% 
  mutate(
    # Order countries on increasing magnitude per panel
    country_order = interaction(predictor, outcome, country),
    country_order = as.numeric(fct_reorder(country_order, Estimate)),
    # But also ensure that average ("World") is in bottom
    country_order = if_else(
      country == "World", country_order-10000, country_order
    ),
    country_order = factor(country_order)
  ) %>% 
  ggplot(aes(Estimate, country_order, col = Sex, shape = Star)) +
  scale_y_discrete("Country", expand = expansion(.015)) +
  scale_x_continuous(
    "Estimated association"
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_color_brewer("Sex", palette = "Set1") +
  scale_size_manual(values = c(0.75, 1.5)) +
  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
  geom_linerangeh(
    aes(xmin = CI.Lower, xmax = CI.Upper),
    size = .2, position = position_dodgev(.4)
  ) +
  geom_point(
    fill = "white", aes(size = name),
    position = position_dodgev(.6)
  ) +
  facet_grid2(
    predictor~outcome, independent = "all", scales = "free",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  guides(shape = "none", size = "none") +
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    legend.position = "bottom"
  )

ggsave("out/Fig-forest.png", width = W, height = W*.66, units = "cm", dpi = 400)
```

```{r tab-between}
#| include: true

# Between-country associations
coefs %>% 
  mutate(
    predictor = if_else(
      predictor == "dau", 
      "Daily FB users", 
      "Monthly FB users"
    )
  ) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>% 
  filter(Hypothesis == "Between-country") %>% 
  select(
    Predictor = predictor, Outcome = outcome, Estimate, CI.Lower, CI.Upper
  ) %>% 
  arrange(Predictor, Outcome) %>% 
  apa_table()
```

```{r fig-ce-prepare}
# Create a predictor table with evenly spaced mau_cw values for each country
newx_country <- fits$data[[1]] %>% 
  group_by(country, age, sex, mau_cb) %>% 
  filter(mau_cw %in% c(min(mau_cw), max(mau_cw))) %>% 
  select(country, age, sex, mau_cb, mau_cw) %>% 
  # For above groupings, create a sequence of dau_cws from min to max
  group_modify(
    ~tibble(mau_cw = seq(min(.$mau_cw), max(.$mau_cw), length = 31))
    ) %>% 
  ungroup() %>% 
  mutate(year = 0, se = 0)

newx_world <- fits$data[[1]] %>% 
  group_by(age, sex) %>% 
  filter(mau_cw %in% c(min(mau_cw), max(mau_cw))) %>% 
  select(age, sex, mau_cw) %>% 
  # For above groupings, create a sequence of mau_cws from min to max
  group_modify(
    ~tibble(mau_cw = seq(min(.$mau_cw), max(.$mau_cw), length = 31))
    ) %>% 
  ungroup() %>% 
  mutate(mau_cb = 0, year = 0, se = 0)

newy <- fits %>% 
  mutate(
    country = map(
      mau, 
      ~bind_cols(newx_country, fitted(.x, newx_country))
      ),
    world = map(
      mau, 
      ~bind_cols(newx_world, fitted(.x, newx_world, re_formula = NA))
      )
  ) %>% 
  select(outcome, country, world)
```

```{r fig-ce}
#| include: true

newy %>% 
  pivot_longer(c(country, world)) %>% 
  unnest(value) %>% 
  ungroup() %>% 
  mutate(country = if_else(name == "world", "World", country)) %>% 
  ggplot(
    aes(mau_cw, Estimate, group = interaction(country, sex), col = sex, fill = sex)
    ) +
  scale_color_brewer(
    "Age", 
    palette = "Dark2", 
    aesthetics = c("color", "fill")
  ) +
  scale_y_continuous(
    "Estimated outcome",
    breaks = extended_breaks()
  ) +
  scale_x_continuous(
    "Country-mean deviated monthly FB users",
    breaks = extended_breaks(),
    labels = ~percent(.)
  ) +
  scale_size_manual(values = c(.2, .4)) +
  geom_ribbon(
    data = . %>% filter(name == "world"),
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .2, col = NA
  ) +
  geom_line(aes(size = name)) +
  facet_grid(
    age~outcome, scales = "free_y",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(legend.position = "none")
ggsave("out/Fig-mau-conditional.png", width = W, height = W*.5, units = "cm", dpi = 400)
```

# Discussion

# References

::: {#refs}
:::

# Supporting information

## Extended Methods

### Facebook engagement

```{r}
# Text list of countries
countries <- sort(unique(d_fb$country))
countries[length(countries)] <- paste("and", countries[length(countries)])
countries <- str_c(countries, collapse = ", ")
```

We studied two metrics of Facebook adoption, daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (`r countries`). FB estimates yearly DAU & MAU with their corresponding means from June 1 to August 31, and rounds values greater than 10,000,000 to three significant digits, and values less than 10,000,000 to the nearest 10,000. These estimates are calculated separately for individuals aged 13-34 and 35+. User age is determined based on Facebook profile information, which can be inaccurate (e.g. young individuals report an older age.) Accordingly, 0.008% of total MAU were trimmed to exclude accounts with unrealistic on non-reported age. An account's country is determined on a number of factors including the user's IP address and self-reported location.

Facebook defines users as individuals who visited Facebook or used Messenger during the appropriate period. Although accurately captured, these numbers are not perfect indicators of actual user numbers because of possible duplicate and false accounts. FB estimates those accounts to count for 11% and 5% of global MAUs, and that the former may be more likely in developing regions. Because internal criteria and methodology for determining duplicate and false accounts can change over time, estimates of MAU and DAU can also change.

### Well-being

```{r}
# N is max N over different outcomes
gwp_n <- d_gwp %>% 
  group_by(outcome) %>% 
  summarise(n = sum(n)) %>% 
  pull(n) %>% 
  max()

# N groups same logic
gwp_n_groups <- count(d_gwp, outcome) %>% 
  pull(n) %>% 
  max()
```

Gallup World Poll (GWP) is a nationally representative annual survey of 1,000 civilian, non-institutionalised individuals aged 15 years or older from 164 countries conducted since 2005. The surveys are conducted face-to-face or on the phone in the respondents’ native language and by local interviewers (for details, see [@gallupGallupWorldPoll2020; @gallupHowDoesGallup2014]). We studied Positive (PE) and Negative Experiences (NE), and life satisfaction. PE and NE measure respondents’ experienced well-being on the day before the survey with five items each. For PE, these items are: "Did you feel well-rested yesterday?", "Were you treated with respect all day yesterday?", "Did you smile or laugh a lot yesterday?", "Did you learn or do something interesting yesterday?, and "(Did you experience the following feelings during a lot of the day yesterday?) How about enjoyment?".

The NE items are responses to "Did you experience the following feelings during a lot of the day yesterday?" for physical pain, worry, sadness, stress, and anger? For analyses we used the means of these scales. Life satisfaction in the moment was measured with one 11-step Likert item, "Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top. The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you. On which step of the ladder would you say you personally feel you stand at this time?". For analyses, we scaled these variables to percentages, and aggregated the `r number(gwp_n, big.mark = ",")` individuals’ data to means and standard errors for each country, year, sex, and age (15-34 and 35+) combination (`r number(gwp_n_groups, big.mark = ",")` cells).

### Data analysis

Before analysing the data, we converted Facebook DAU and MAU to proportions of each country's yearly population sizes using population data from World Bank (midyear estimates; <https://data.worldbank.org/indicator/SP.POP.TOTL>). For Taiwan, we used population data from Wikipedia (<https://en.wikipedia.org/wiki/Demographics_of_Taiwan#Population_census>), because the World Bank data does not include Taiwan.

We examined the association between Facebook adoption and well-being through bayesian hierarchical regression models, estimated separately for DAU and MAU, and each of the three well-being outcomes. We regressed the outcome $y$ on time (decades, centered on 2014), within-country centered $x$ (DAU / MAU), age, sex, all the interactions except time by $x$, and the between-country centered DAU. We allowed all coefficients to vary randomly across the 72 countries, except the between-country predictor. Because we aggregated the outcomes, we included to standard errors of the outcome in the model to account for the varying group sizes.

We conducted all data analyses with the R language for statistical computing [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan’s Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021]. We used default noninformative priors, 4 HMC chains with 3,000 iterations and first 1,500 as warmup for 6,000 total iterations; we report all parameters with their posterior means and 95% credible intervals (posterior 2.5 and 97.5 percentiles; CI), and other posterior probabilities as indicated in text.

### 2022-09-16 data-prepare.Rmd
rename

--- 2022-08-16 clean.qmd
@@
-## Data cleaning
+# Data cleaning
 
@@
 ```
+
+## Gallup
 
@@
 
-### Population
+## Population
 
-Yearly population estimates from world bank, except Taiwan from Wikipedia.
+From <https://population.un.org/wpp/Download/Standard/Population/>.
 
 ```{r}
-pop <- read_csv(
-  "data/API_SP.POP.TOTL_DS2_en_csv_v2_4335082.csv", 
-  skip = 3
+library(readxl)
+pop <- read_excel(
+  "data/WPP2022_POP_F01_1_POPULATION_SINGLE_AGE_BOTH_SEXES.xlsx", 
+  sheet = 1, 
+  skip = 16,
+  col_types = "text",
+  .name_repair = make_clean_names
   )
 pop <- pop %>% 
+  drop_na(iso3_alpha_code) %>% 
   select(
-    country = `Country Code`,
-    `2008`:`2019`
+    iso3_alpha_code, year, starts_with("x")
   ) %>% 
   mutate(
-    country = countrycode(country, origin = "iso3c", destination = "cldr.short.en")
+    country = countrycode(
+      iso3_alpha_code, 
+      origin = "iso3c", 
+      destination = "cldr.short.en"
+    )
+  )
+pop <- pop %>% 
+  filter(
+    country %in% fb_countries,
+    between(year, 2008, 2019)
   ) %>% 
-  filter(country %in% fb_countries) %>% 
-  pivot_longer(`2008`:`2019`, names_to = "year", values_to = "pop") %>% 
-  mutate(year = as.numeric(year))
+  pivot_longer(
+    starts_with("x"), 
+    names_to = "age",
+    values_to = "pop",
+    names_transform = ~str_remove(., "x") %>% as.numeric, 
+    values_transform = ~ as.numeric(.) * 1000
+  ) %>% 
+  filter(between(age, 13, 100)) %>% 
+  mutate(
+    age = cut(age, c(0, 34.5, 1000), labels = c("13-34", "35+"))
+  )
+pop <- pop %>% 
+  mutate(year = as.numeric(year)) %>% 
+  group_by(country, year, age) %>% 
+  summarise(pop = sum(pop)) %>% 
+  ungroup()
+```
 
-tw <- tibble(
-  country = "Taiwan",
-  year = 2008:2019,
-  pop = c(23037031, 23119772, 23162123, 23224912, 23315822, 23373517, 23433753, 23492074, 23539816, 23571227, 23588932, 23600903)
+## Synthetic Facebook data
+
+Here we create simple time trend data that can be used for reproducing the computations when the actual Facebook data is not available.
+It does not represent any statistical properties of the Facebook data and is created simply to help run the computations.
+
+```{r}
+fb_mock_path <- here("data/fb-SYNTHETIC.rds")
+if (!file.exists(fb_mock_path)) {
+  library(extraDistr)
+  set.seed(999)
+  slopes <- distinct(pop, country) %>% 
+    mutate(slope = rnorm(72, 0.75, 0.1))
+  fb_syn <- pop %>% 
+    left_join(slopes) %>% 
+    rowwise() %>% 
+    mutate(
+      dau = rprop(1, 50, plogis(-4 + slope*(year-2008))),
+      mau = rprop(1, 100, plogis(-5 + slope*(year-2008)))
     )
-pop <- bind_rows(pop, tw)
+  saveRDS(fb_syn, fb_mock_path)
+}
 ```

### 2022-09-16 Manuscript.Rmd
Getting closer to a draft

---
title: The association between Facebook adoption and well-being
shorttitle: Facebook and well-being
leftheader: Facebook and well-being
author: 
  - name: Matti Vuorre
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - Design
      - Administration
      - Analysis
      - Visualization
      - Writing
  - name: Andrew K. Przybylski
    affiliation: 1
    corresponding: yes
    address: Oxford Internet Institute, University of Oxford
    email: andy.przybylski@oii.ox.ac.uk
    role:
      - Design
      - Administration
      - Funding
      - Resources
      - Supervision
      - Visualization
      - Writing

affiliation:
  - id: 1
    institution: Oxford Internet Institute, University of Oxford

authornote: |
  \noindent \textbf{This manuscript is not yet peer-reviewed.}

  This research was supported by the Huo Family Foundation and Economic and Social Research Council Grant ES/T008709/1.

  The analytic code is available at (LINK). This manuscript is available under [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/) at (LINK). Researchers can contact Facebook (ccobb@fb.com) to access our code, the Facebook data, and a synthetic version of the Gallup data for reproducing and extending our analyses.
  This study and methodology was reviewed and approved by the Oxford Internet Institute's Departmental Research Ethics Committee (SSH_OII_CIA_21_084). The authors declare no conflicts of interest.

abstract: | 
  \textbf{Abstract} Although social media's potential effects on well-being have received considerable research interest, much of past work is hampered by an exclusive focus on demographics in the Global North and the use of inaccurate self-reports. We describe associations linking 72 countries' Facebook adoption to the well-being of 946,798 individuals from 2008 to 2019. We found no associations suggesting that the global penetration of social media has caused widespread psychological harm: Facebook adoption predicted life satisfaction and positive experiences positively, and negative experiences negatively, both between countries and within countries but over time. Facebook adoption was more positively associated with well-being for younger individuals, but country-specific results were mixed. In order to move beyond studying aggregates and to better understand social media's causal effects, we need more transparent collaborative research between independent scientists and the technology industry.

  \textbf{Significance statement} Billions of individuals across the globe use social media on a regular basis. The widespread adoption of social media---most prominently Facebook---has fundamentally shifted how humans conduct their lives. Consequently, researchers, healthcare professionals, and policy makers have repeatedly raised alarms that the spread of social media may be negatively affecting individuals, particularly young ones, mental health and well-being on a global scale. We examined the plausibility of this idea by associating 72 nations' yearly Facebook adoption rates to the well-being of 946,798 individuals from 2008 to 2019. Overall, we found that increased rates of daily and monthly active Facebook users predicted greater levels of well-being, when comparing countries to other countries, or countries to themselves but over time. These findings should guide debate surrounding social media towards more empirical foundations: The importance of this topic requires that independent scientists gain access to more detailed data from the technology industry in order to better determine how and why modern online platforms might be affecting their users.

keywords: well-being, social media
# wordcount: 
bibliography: "references.bib"
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
header-includes:
  - |
    \setlength{\parskip}{2pt}
    \setlength\parindent{24pt}

csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: jou
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
always_allow_html: true
---

```{r setup, include = FALSE}
# Packages
library(papaja)
library(scales)
library(knitr)
library(patchwork)
library(ggh4x)
library(brms)
library(ggstance)
library(bayestestR)
library(tidyverse)

# Directories for files
dir.create("models", FALSE)

# Document options
opts_chunk$set(
  eval = TRUE,
  cache = TRUE,
  include = FALSE,
  warning = FALSE,
  dpi = 300,
  fig.align = "center"
)

# For tables: Show NAs as blanks
options(knitr.kable.NA = '')

# Plotting options
theme_set(
  theme_linedraw(
    base_size = 8
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
      axis.text = element_text(size = rel(0.7)),
      axis.ticks = element_line(size = rel(0.4))
    )
)
```

```{r data-prepare}
# Load and merge data
# Facebook -- this data only exists on FORT
d_fb <- read_csv("data/fb.csv")
# If you are not conducting these analyses on FORT, the above data is not 
# available. Uncomment below to use a synthetic dataset instead.
# d_fb <- read_csv("data/fb-SYNTHETIC.csv")  # If real FB data not available

# Gallup
d_gwp <- read_rds("data/gwp.rds") 
# d_gwp <- read_rds("data/gwp-SYNTHETIC.rds") # If real Gallup data not available

# Population estimates
d_pop <- read_rds("data/population.rds")

# Convert fb metrics into country-year proportions
d_fb <- d_fb %>% 
  left_join(d_pop) %>% 
  mutate(
    dau = dau / pop,
    mau = mau / pop
  ) %>% 
  select(-pop)

# Merge
d <- left_join(d_gwp, d_fb) %>% 
  mutate(age = factor(age, levels = c("13-34", "35+")))
```

```{r models}
# Set global contrasts
options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))

# Prepare data
dm <- d %>% 
  # Centering predictors
  # Grand mean centering so both components are zero-centered
  mutate(across(c(dau, mau), ~. - mean(., na.rm = TRUE))) %>% 
  group_by(country) %>%
  mutate(
    # Between
    dau_cb = mean(dau, na.rm = TRUE),
    mau_cb = mean(mau, na.rm = TRUE),
    # Within
    dau_cw = dau - dau_cb, 
    mau_cw = mau - mau_cb
  ) %>% 
  ungroup() %>% 
  # Center year so that intercepts are at 2014
  mutate(year = year - 2014) %>% 
  # Remove rows where predictor existed but outcome didn't
  drop_na(val)

# Model formula
model_dau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + dau_cw) * age * sex + dau_cb +
    ((year + dau_cw) * age * sex | country),
  family = gaussian()
)
model_mau <- bf(
  val | se(se, sigma = TRUE) ~
    (year + mau_cw) * age * sex + mau_cb +
    ((year + mau_cw) * age * sex | country),
  family = gaussian()
)
fits <- dm %>% 
  select(outcome, year, country, sex, age, contains("_c"), val, se) %>% 
  group_by(outcome) %>% 
  nest() %>% 
  crossing(
    nesting(
      model = list(model_dau, model_mau),
      predictor = c("dau", "mau")
    )
  ) %>% 
  mutate(
    fit = pmap(
      list(model, data, outcome, predictor),
      ~brm(
        ..1,
        cores = 4, chains = 4,
        backend = "rstan",
        control = list(adapt_delta = .95),
        iter = 3000,
        data = ..2,
        file = str_glue("models/brm-{..3}-{..4}")
      )
    )
  )
```

```{r coefficients-calculate}
path <- "models/coefficients.rds"
if (!file.exists(path)) {
  # Calculate contrasts for each outcome
  h_dau <- c(
    "Average" = "dau_cw = 0",
    "13-34_Female" = 
      "dau_cw + dau_cw:age1 * -1 + dau_cw:sex1 * -1 + dau_cw:age1:sex1 * 1 = 0",
    "13-34_Male" = 
      "dau_cw + dau_cw:age1 * -1 + dau_cw:sex1 * 1 + dau_cw:age1:sex1 * -1 = 0",
    "35+_Female" = 
      "dau_cw + dau_cw:age1 * 1 + dau_cw:sex1 * -1 + dau_cw:age1:sex1 * -1 = 0",
    "35+_Male" = 
      "dau_cw + dau_cw:age1 * 1 + dau_cw:sex1 * 1 + dau_cw:age1:sex1 * 1 = 0",
    "13-34" = "dau_cw + dau_cw:age1 * -1 = 0",
    "35+" = "dau_cw + dau_cw:age1 * 1 = 0",
    "Female" = "dau_cw + dau_cw:sex1 * -1 = 0",
    "Male" = "dau_cw + dau_cw:sex1 * 1 = 0",
    "Between-country" = "dau_cb = 0",
    "X by age" = "dau_cw:age1 = 0",
    "X by sex" = "dau_cw:sex1 = 0",
    "X by age by sex" = "dau_cw:age1:sex1 = 0"
  )
  h_mau <- c(
    "Average" = "mau_cw = 0",
    "13-34_Female" = 
      "mau_cw + mau_cw:age1 * -1 + mau_cw:sex1 * -1 + mau_cw:age1:sex1 * 1 = 0",
    "13-34_Male" = 
      "mau_cw + mau_cw:age1 * -1 + mau_cw:sex1 * 1 + mau_cw:age1:sex1 * -1 = 0",
    "35+_Female" = 
      "mau_cw + mau_cw:age1 * 1 + mau_cw:sex1 * -1 + mau_cw:age1:sex1 * -1 = 0",
    "35+_Male" = 
      "mau_cw + mau_cw:age1 * 1 + mau_cw:sex1 * 1 + mau_cw:age1:sex1 * 1 = 0",
    "13-34" = "mau_cw + mau_cw:age1 * -1 = 0",
    "35+" = "mau_cw + mau_cw:age1 * 1 = 0",
    "Female" = "mau_cw + mau_cw:sex1 * -1 = 0",
    "Male" = "mau_cw + mau_cw:sex1 * 1 = 0",
    "Between-country" = "mau_cb = 0",
    "X by age" = "mau_cw:age1 = 0",
    "X by sex" = "mau_cw:sex1 = 0",
    "X by age by sex" = "mau_cw:age1:sex1 = 0"
  )
  coefs <- fits %>% 
    select(-data, -model) %>% 
    mutate(h = if_else(predictor == "dau", list(h_dau), list(h_mau))) %>% 
    mutate(
      world = map2(
        fit, h,
        ~hypothesis(.x, .y) %>% 
          .[["hypothesis"]] %>%
          tibble()
      ),
      country = map2(
        fit, h,
        ~hypothesis(.x, .y, scope = "coef", group = "country") %>%
          .[["hypothesis"]] %>%
          tibble()
      )
    ) %>% 
    select(-fit, -h)

  # Both predictor and outcome are 0-1, so scale can be interpreted as % change as a function of % change

  coefs <- coefs %>% 
    pivot_longer(c(world, country)) %>% 
    unnest(value) %>% 
    mutate(
      country = if_else(name == "country", as.character(Group), "World")
    ) %>% 
    # Between country contrast not country-specific!
    filter(!(Hypothesis == "Between-country" & country != "World")) %>% 
    # Neatly formatted result string
    mutate(
      across(c(Estimate, CI.Lower, CI.Upper), list("str" = ~number(., .01))),
      result = str_glue("{Estimate_str}% [{CI.Lower_str}, {CI.Upper_str}]")
    )

  saveRDS(coefs, path)

} else {coefs <- readRDS(path)}
```

The ways in which people use technology for most domains in life has changed dramatically since the mass introduction of the internet in the 1990s, and the subsequent technologies facilitated by it. Most prominently, the popularization of modern social media platforms in 2008 precipitated widespread changes to human activities via features such as marketplaces, personalized news feeds, photo sharing, live streaming, and other features that the "metaverse" promises to build on. The first social media with global adoption, MySpace (launched 2003) saw 115 million users in 2008---the year in which it was replaced as the leading platform by Facebook (2004). Today (2022-Q1), Facebook reports 2.94 billion monthly active users [@metaMetaReportsFirst2022], or about one third of the global population. Along with social media's global penetration, debate surrounding their potential effects on individual and collective well-being has intensified.

Although reports of negative psychological outcomes associated social media are common in academic writing [@krossFacebookUsePredicts2013] and popular media [@thompsonSocialMediaAttention2021], evidence for harms is, on balance, more speculative than conclusive [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020; @ophirNewMediaScreenTime2020]. Recent results on the associations between social media use and well-being are mixed and shown to critically depend on arbitrary analytic choices [@orbenSocialMediaEnduring2019]. Other studies have reported that there have been few if any changes in associations linking technology use to mental health in this period of social media's global adoption [@vuorreThereNoEvidence2021]. A general lack of validated measures, poorly specified causal models, and inadequate data have yielded a large number of low quality studies [@parrySystematicReviewMetaanalysis2021; @sewallDoesObjectivelyMeasured2022]. Furthermore, because nearly all investigations have focused on samples from the Global North [@ghaiSocialMediaAdolescent2022], we have next to no idea of how the wide adoption of social media platforms relates to psychological well-being across the world.

To better understand the plausible range of associations, we linked data tracking Facebook's global adoption with three indicators of global well-being. We examined 72 countries' per capita daily active Facebook users (DAU) in two age brackets (13-34 and 35+ years) as predictors of life satisfaction (LS), negative (NE), and positive psychological experiences (PE) at the level of years spanning 2008 to 2019. The well-being data represented 946,798 individuals' responses from the nationally representative Gallup World Poll Survey [@gallupHowDoesGallup2014]. We joined these unique datasets to conduct a descriptive study to answer three basic yet important questions: First, to what extent did Facebook adoption predict well-being? Second, do these associations differ by age or sex. And finally, to what extent might these associations have differed between countries?

```{r tab-world}
#| include: true

# Average within- and between-country associations
tab_world <- coefs %>% 
  filter(
    name == "world",
    Hypothesis %in% c("Average", "Between-country")
  ) %>% 
  mutate(
    outcome = case_when(
      outcome == "Life_satisfaction" ~ "LS",
      outcome == "Negative_experiences" ~ "NE",
      outcome == "Positive_experiences" ~ "PE"
    )
  ) %>% 
  select(
    predictor, Outcome = outcome, Hypothesis, result
  ) %>% 
  pivot_wider(names_from = Hypothesis, values_from = result) %>% 
  rename(
    `Within country` = Average,
    `Between country` = `Between-country`
  ) %>% 
  select(predictor, Outcome, `Between country`, `Within country`) %>% 
  arrange(predictor, Outcome)

tab_world %>% 
  filter(predictor == "dau") %>% 
  select(-predictor) %>% 
  mutate(
    across(
      ends_with("country"), 
      ~if_else(str_starts(., "-"), ., paste0("\\phantom{-}", .))
    )
  ) %>% 
  apa_table(
    caption = "Average Facebook DAU and well-being associations",
    font_size = "small",
    note = "LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences. Numbers indicate posterior means and 95\\%CIs.",
    span_text_columns = FALSE,
    escape = FALSE,
    placement = "htb",
    align = 'llll'
  )
```

```{r}
# How many people in GWP data
d_gwp %>% 
  group_by(outcome) %>% 
  summarise(n = sum(n)) %>% 
  pull(n) %>% max %>% number

# Percentages of countries where DAU was over 25% by year
tmp <- d_fb %>% 
  group_by(year, age) %>% 
  summarise(median_dau = percent(median(dau))) %>% 
  pivot_wider(names_from = age, values_from = median_dau)
tmp
```

```{r fig-data}
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 5
#| fig.cap: "A. 72 countries' daily active Facebook users in two age brackets from 2008 to 2019. (Percentages may exceed 100\\% due to inaccurate estimation of either DAU or population size.) B. The same 72 countries' mean responses to three well-being scales in the Gallup World Poll from 2008 to 2019, separated by age category and sex. LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences."

# Figure of all variables over time
p_a <- d_fb %>% 
  ggplot(aes(year, dau, group = country)) +
  scale_y_continuous(
    "Percentage of population", 
    expand = expansion(.03),
    breaks = extended_breaks(),
    labels = ~percent(.)
  ) +
  scale_x_continuous(
    "Year", 
    breaks = seq(2008, 2018, by = 2), 
    labels = ~str_replace(., "20", "'"),
    expand = expansion(0.01)
  ) +
  geom_line(size = .125) +
  # geom_smooth(group = 1, method = "gam", se = F) +
  facet_wrap("age", nrow = 1) +
  theme(
    legend.position = "none",
    axis.title.x = element_blank()
  )

p_b <- d %>% 
  # Exclude rows where FB data existed but not GWP data
  drop_na(val) %>% 
  # Actual lowest age in GWP
  mutate(age = factor(age, labels = c("15-34", "35+"))) %>% 
  mutate(
    outcome = case_when(
      outcome == "Life_satisfaction" ~ "LSAT",
      outcome == "Negative_experiences" ~ "NPE",
      outcome == "Positive_experiences" ~ "PPE"
    )
  ) %>% 
  mutate(panel = str_glue("{age} ({sex})")) %>% 
  ggplot(aes(year, val, group = country)) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(
    "Value", 
    expand = expansion(.01),
    breaks = extended_breaks(),
    labels = ~percent(.)
  ) +
  scale_x_continuous(
    "Year", 
    breaks = seq(2008, 2018, by = 2),
    labels = ~str_replace(., "20", "'")
  ) +
  geom_line(size = .125) +
  facet_grid(
    outcome~panel, 
    scales = "free_y",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(legend.position = "none")

(p_a / p_b) +
  plot_layout(heights = c(3, 7)) +
  plot_annotation(tag_levels = "A")
```

Facebook adoption increased markedly from 2008 when the median per capita DAU across these 72 countries was `r tmp[1,2]` (ages 13-34) and `r tmp[1,3]`% (35+), to `r tmp[12,2]` (13-34) and `r tmp[12,3]` (35+; Figure \@ref(fig:fig-data)A) in 2019. During this period Facebook adoption by younger individuals plateaued before saturation in many countries, but not for older individuals. At the same time, we did not observe correspondingly large and uniform changes across measures of well-being (Figure \@ref(fig:fig-data)B) [@vuorreGlobalWellbeingMental2022].

To answer our first question of how Facebook adoption might relate to well-being, we specified a Bayesian multilevel linear meta-regression model of each well-being outcome on time, sex, age, and DAU (both within- and between-country-centered, see SI). We included all interactions between sex, age, and time, and sex, age, and DAU (within-country-centered), and allowed all parameters to vary randomly across countries. We first examined whether the relative standing of countries on their average Facebook adoption predicted well-being (the model's between-country associations). We found that countries with greater average DAU had somewhat higher levels of life satisfaction and positive experiences, and lower levels of negative experiences than countries with lower DAU (Table \@ref(tab:tab-world)). However, there are large and important differences between countries in factors that might underlie differences in both social media adoption and well-being, such as socioeconomic conditions. As such, while descriptively informative, these associations are likely to indicate between-country confounding factors.

```{r fig-forest}
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 4.6
#| fig.cap: "Forest plot of estimated associations between country-year level per-capita daily active Facebook users (DAU) and life satisfaction (LS), negative experiences (NE), and positive experiences (PE). Units indicate percentage change in outcome as function of percentage increase in within-country centered DAU. Filled points indicate estimates whose posterior 95\\%CI excluded zero. See the online supplementary materials for corresponding figure but with MAU as predictor."

tmp <- coefs %>%   
  filter(
    # name != "world",
    str_detect(Hypothesis, "_")
  ) %>% 
  separate(Hypothesis, c("Age", "Sex"), sep = "_") %>% 
  mutate(
    outcome = case_when(
      outcome == "Life_satisfaction" ~ "LS",
      outcome == "Negative_experiences" ~ "NE",
      outcome == "Positive_experiences" ~ "PE"
    )
  ) %>% 
  # mutate(outcome = str_glue("{outcome} ({Sex})")) %>% 
  filter(predictor == "dau")

tmp %>%
  ggplot() +
  aes(
    x = Estimate, 
    y = fct_rev(country), 
    col = Age, 
    fill = interaction(Age, Star, sep = " "), 
    shape = Sex
  ) +
  scale_y_discrete(
    "Country",
    expand = expansion(.015),
    labels = ~str_replace(., "World", "Average")
  ) +
  scale_x_continuous(
    "Association with daily active Facebook users (95%CI)",
    breaks = extended_breaks(7),
    expand = expansion(.1)
  ) +
  scale_shape_manual(
    values = c(21, 22)
  ) +
  scale_color_brewer(
    "Age", palette = "Set1", aesthetics = c("color")
  ) +
  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
  geom_linerangeh(
    aes(xmin = CI.Lower, xmax = CI.Upper),
    size = .15, position = position_dodge2v(.7), 
    show.legend = FALSE
  ) +
  geom_point(
    size = .65, stroke = .45,
    position = position_dodge2v(.7)
  ) +
  facet_wrap(
    "outcome", scales = "free_x", nrow = 1,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  guides(
    fill = "none",
    color = guide_legend(override.aes = list(size = 1.5)),
    shape = guide_legend(override.aes = list(size = 1.5))
  ) +
  theme(
    axis.text.y = element_text(size = rel(0.7)),
    axis.title.y = element_blank(),
    panel.grid.major.y = element_line(
      size = .1, linetype = 2, color = "gray60"
    ),
    legend.position = "right"
  )
```

Variations in such confounding factors are likely to be significantly smaller within countries over time. We therefore next focused on the model's within-country associations, which measure the extent to which Facebook adoption in a given country predicted well-being in that country adjusting for general linear temporal trends in the well-being outcome. On average across countries, age, and sex, we found that years with greater than the average country's average DAU were associated with greater levels of life satisfaction and positive experiences, and lower levels of negative experiences (Table \@ref(tab:tab-world)). For the average country in our sample of 72, Facebook adoption positively predicted well-being. While these associations indicate relations within countries and adjust for confounders that vary linearly with time, by including time as a predictor, they are still susceptible to confounders and do not indicate causal relations. Rather, this association describes the fact that, all else being equal, years with greater Facebook adoption tended to be those with greater levels of well-being.

```{r demographics}
coefs %>% 
  filter(
    str_detect(Hypothesis, " by "), 
    name == "world"
  ) %>% 
  select(
    Predictor = predictor, Outcome = outcome, Hypothesis, result
  ) %>% 
  pivot_wider(names_from = Outcome, values_from = result)
coefs %>% 
  filter(
    Hypothesis %in% c("13-34", "35+", "Female", "Male"),
    name == "world"
  ) %>% 
  select(
    Predictor = predictor, Outcome = outcome, Hypothesis, result
  ) %>% 
  pivot_wider(names_from = Outcome, values_from = result)

tab_demo <- coefs %>% 
  filter(
    str_detect(Hypothesis, "_"),
    name == "world"
  ) %>% 
  select(
    Predictor = predictor, Outcome = outcome, Hypothesis, result
  ) %>% 
  pivot_wider(names_from = Outcome, values_from = result)
tab_demo
```

We then turned to our second question and assessed whether within-country associations linking Facebook adoption to well-being differed between the demographic groups. Differences in the association linking Facebook adoption and well-being were greater between the younger and older demographics than they were between females and males (Figure \@ref(fig:fig-forest), Average). DAU predicted life satisfaction more positively in the younger age bracket, but these estimates' CIs did not exclude zero. DAU predicted negative experiences negatively in the younger age group, but positively for older males. These differences were less pronounced for positive experiences, which were positively associated with DAU only in the 13-34 year old male group. These results show that Facebook adoption was, for the average nation in our sample, more positively predictive of well-being for individuals below 35, and that differences between males and females were generally smaller than those between age groups.

```{r}
# Can we show regions in the forest plot as secondary axis? 
# Table of percentages of countries with credible associations
tmp <- coefs %>% 
  filter(name == "country", Hypothesis == "Average") %>% 
  group_by(predictor, outcome, Star, direction=sign(Estimate)) %>% 
  count() %>% 
  group_by(predictor, outcome) %>% 
  # mutate(n = percent(n / sum(n), 1)) %>% 
  mutate(x = interaction(Star, direction)) %>% 
  select(-Star, -direction) %>% 
  pivot_wider(names_from=x, values_from=n) %>% 
  replace_na(list(`.-1` = 0, `.1` = 0, `*.1` = 0, `*.-1` = 0))
tmp
coefs %>% 
  filter(predictor == "dau", name == "country", Hypothesis == "Average") %>% 
  filter(Star=="*") %>% 
  arrange(outcome, country) %>% 
  select(outcome, country, Estimate:CI.Upper)
```

However, while informative aggregates, these results do not describe associations between Facebook adoption and well-being for any individual country, but rather their averages. To answer our third question, we computed country-specific estimates for each sex and age group (Figure \@ref(fig:fig-forest)). On average, for life satisfaction, `r tmp[1, 5]` countries credibly positive associations. For negative experiences, `r tmp[2, 6]` countries had a credibly negative association, and `r tmp[3, 5]` countries had a credibly positive association between DAU and positive experiences. There were no credible (at the 95% level) country-level negative associations between DAU and life-satisfaction. Although many country-level estimates were uncertain, these results aligned with the general pattern of positive associations between Facebook adoption and country-level well-being.

```{r fig-ce-prepare}
#| eval: false
# Create a predictor table with evenly spaced mau_cw values for each country
newx_country <- fits$data[[1]] %>% 
  group_by(country, age, sex, mau_cb) %>% 
  filter(mau_cw %in% c(min(mau_cw), max(mau_cw))) %>% 
  select(country, age, sex, mau_cb, mau_cw) %>% 
  # For above groupings, create a sequence of dau_cws from min to max
  group_modify(
    ~tibble(mau_cw = seq(min(.$mau_cw), max(.$mau_cw), length = 31))
  ) %>% 
  ungroup() %>% 
  mutate(year = 0, se = 0)

newx_world <- fits$data[[1]] %>% 
  group_by(age, sex) %>% 
  filter(mau_cw %in% c(min(mau_cw), max(mau_cw))) %>% 
  select(age, sex, mau_cw) %>% 
  # For above groupings, create a sequence of mau_cws from min to max
  group_modify(
    ~tibble(mau_cw = seq(min(.$mau_cw), max(.$mau_cw), length = 31))
  ) %>% 
  ungroup() %>% 
  mutate(mau_cb = 0, year = 0, se = 0)

newy <- fits %>% 
  mutate(
    country = map(
      mau, 
      ~bind_cols(newx_country, fitted(.x, newx_country))
    ),
    world = map(
      mau, 
      ~bind_cols(newx_world, fitted(.x, newx_world, re_formula = NA))
    )
  ) %>% 
  select(outcome, country, world)
```

```{r fig-ce}
#| eval: false
#| include: true

newy %>% 
  pivot_longer(c(country, world)) %>% 
  unnest(value) %>% 
  ungroup() %>% 
  mutate(country = if_else(name == "world", "World", country)) %>% 
  ggplot(
    aes(mau_cw, Estimate, group = interaction(country, sex), col = sex, fill = sex)
  ) +
  scale_color_brewer(
    "Age", 
    palette = "Dark2", 
    aesthetics = c("color", "fill")
  ) +
  scale_y_continuous(
    "Estimated outcome",
    breaks = extended_breaks()
  ) +
  scale_x_continuous(
    "Country-mean deviated monthly FB users",
    breaks = extended_breaks(),
    labels = ~percent(.)
  ) +
  scale_size_manual(values = c(.2, .4)) +
  geom_ribbon(
    data = . %>% filter(name == "world"),
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .2, col = NA
  ) +
  geom_line(aes(size = name)) +
  facet_grid(
    age~outcome, scales = "free_y",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(legend.position = "none")
```

We found that, on the whole, Facebook adoption positively predicted well-being. This association held when comparing countries to other countries, and individual countries over time. While these descriptive results do not speak to causal effects, they align with other recent findings suggesting that technology has not become increasingly harmful over time [@vuorreThereNoEvidence2021], and that increased adoption of general internet technologies are not, overall, associated with psychological harms [@vuorreGlobalWellbeingMental2022]. That said, these conclusions are qualified because our focus on daily active users could miss those who use Facebook less regularly. To test this idea, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor. Those results were substantively the same (see online supplement).

It is widely accepted that social media and the Internet more broadly have changed how humans socialize, organize, and seek leisure, but it is not obvious or necessary that their wide adoption has influenced well-being. In this study we used the best data available to describe how global Facebook adoption relates to well-being across 72 countries over a 12-year period. We found generally positive associations between Facebook adoption and well-being which were partially qualified by demographics and not uniform across countries.

We did not find evidence that increased social media adoption is consistently negatively associated with well-being. Nevertheless, our analyses cannot and do not rule out that possibility because more fine-grained data needed to do so either do not exist or are not available. If we are to move past description to prediction or intervention, independent scientists and online platforms will need to collaborate in new, transparent ways. As it stands now, only a handful of scientists working in the technology industry have the data needed to advance this line of inquiry. If we are to understand and improve well-being in the digital age, this must change.

# References

::: {#refs}
:::

# Supporting information

## Data availability

Both datasets (Facebook and Gallup) are proprietary and we therefore could not share them with this manuscript.  The analytic code, along with synthetic datasets, is available at (LINK). Researchers can contact Facebook (ccobb@fb.com) to access our code, the Facebook data, and a synthetic version of the Gallup data for reproducing and extending our analyses. The Gallup data are available online to subscribing institutions.

## Facebook data

```{r}
# Text list of countries
countries <- sort(unique(d_fb$country))
countries[length(countries)] <- paste("and", countries[length(countries)])
countries <- str_c(countries, collapse = ", ")
```

We studied two metrics of Facebook adoption, daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (see Figure \@ref(fig:fig-forest)). FB estimates yearly DAU & MAU with their corresponding means from June 1 to August 31, and rounds values greater than 10,000,000 to three significant digits, and values less than 10,000,000 to the nearest 10,000. We report analyses based on DAU in the main manuscript, and MAU in the online supplement. DAU and MAU estimates are calculated separately for individuals aged 13-34 and 35+. User age is determined based on Facebook profile information, which can be inaccurate (e.g. young individuals report an older age.) Accordingly, 0.008% of total MAU were trimmed to exclude accounts with unrealistic on non-reported age.

In personal communication, Facebook representatives explained the selection of countries as "The countries provided were selected based upon geographic and cultural diversity and criteria related to data quality, including that geographic and age attribution error is believed to be relatively small." A given user's country is determined based on a number of factors, including the user's IP address and self-reported location.

Facebook defines users as individuals who visited Facebook or used Messenger during the appropriate period. Although accurately captured, these numbers are not perfect indicators of actual user numbers because of possible duplicate and false accounts. FB estimates those accounts to count for 11% and 5% of global MAUs, and that the former may be more likely in developing regions. Because internal criteria and methodology for determining duplicate and false accounts can change over time, estimates of MAU and DAU can also change.

The Facebook adoption data were made available to us on Facebook's Open Research Tool platform. Other researchers can contact Facebook (ccobb@fb.com) to access the dataset.

## Well-being

```{r}
# N is max N over different outcomes
gwp_n <- d_gwp %>% 
  group_by(outcome) %>% 
  summarise(n = sum(n)) %>% 
  pull(n) %>% 
  max()

# N groups same logic
gwp_n_groups <- count(d_gwp, outcome) %>% 
  pull(n) %>% 
  max()
```

Gallup World Poll (GWP) is a nationally representative annual survey of 1,000 civilian, non-institutionalised individuals aged 15 years or older from 164 countries conducted since 2005. The surveys are conducted face-to-face or on the phone in the respondents’ native language and by local interviewers (for details, see [@gallupHowDoesGallup2014]). We studied Positive (PE) and Negative Experiences (NE), and life satisfaction. PE and NE measure respondents’ experienced well-being on the day before the survey with five items each. For PE, these items are: "Did you feel well-rested yesterday?", "Were you treated with respect all day yesterday?", "Did you smile or laugh a lot yesterday?", "Did you learn or do something interesting yesterday?, and "(Did you experience the following feelings during a lot of the day yesterday?) How about enjoyment?".

The NE items are responses to "Did you experience the following feelings during a lot of the day yesterday?" for physical pain, worry, sadness, stress, and anger? For analyses we used the means of these scales. Life satisfaction in the moment was measured with one 11-step Likert item, "Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top. The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you. On which step of the ladder would you say you personally feel you stand at this time?". For analyses, we scaled these variables to percentages, and aggregated the `r number(gwp_n, big.mark = ",")` individuals’ data to means and standard errors for each country, year, sex, and age (15-34 and 35+) combination (`r number(gwp_n_groups, big.mark = ",")` cells).

## Data analysis

Before analysing the data, we converted Facebook DAU and MAU to proportions of each country's and age group's yearly population sizes using population data from the United Nations Department of Economic and Social affairs (<https://population.un.org/wpp/Download/Standard/Population/>).

We examined the association between Facebook adoption and well-being through bayesian hierarchical regression models, estimated separately for DAU and MAU, and each of the three well-being outcomes. We regressed the outcome $y$ on time (decades, centered on 2014), within-country centered $x$ (DAU / MAU), age, sex, all the interactions except time by $x$, and the between-country centered DAU. We allowed all coefficients to vary randomly across the 72 countries, except the between-country predictor. Because we aggregated the outcomes, we included to standard errors of the outcome in the model to account for the varying group sizes. Formally, we specified the model as

$$
\begin{aligned} 
y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i) \\
\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \\
&\quad\ (\alpha_{1} + \beta_{1\text{country}[i]})\text{Sex}_i + \\
&\quad\ (\alpha_{2} + \beta_{2\text{country}[i]})\text{Age}_i + \\
&\quad\ (\alpha_{3} + \beta_{3\text{country}[i]})\text{Time}_i + \\
&\quad\ (\alpha_{4} + \beta_{4\text{country}[i]})\text{DAU}^{\text{CW}}_i + \\
&\quad\ (\alpha_{5} + \beta_{5\text{country}[i]})\text{Sex}_i \times \text{Time}_i + \\
&\quad\ (\alpha_{6} + \beta_{6\text{country}[i]})\text{Age}_i \times \text{Time}_i + \\
&\quad\ (\alpha_{7} + \beta_{7\text{country}[i]})\text{Sex}_i \times \text{Age}_i + \\
&\quad\ (\alpha_{8} + \beta_{8\text{country}[i]})\text{Sex}_i \times \text{Age}_i \times \text{Time}_i + \\
&\quad\ (\alpha_{9} + \beta_{9\text{country}[i]})\text{Sex}_i \times \text{DAU}^{\text{CW}}_i + \\
&\quad\ (\alpha_{10} + \beta_{10\text{country}[i]})\text{Age}_i \times \text{DAU}^{\text{CW}}_i + \\
&\quad\ (\alpha_{11} + \beta_{11\text{country}[i]})\text{Sex}_i \times \text{Age}_i \times \text{DAU}^{\text{CW}}_i + \\
&\quad\ \alpha_{12} \text{DAU}^{\text{CB}}_i
\\
\pmb{\beta} &\sim \text{MVN}(\pmb{0}, \Sigma)
\end{aligned}
$$

Where $y_i$ is the outcome (e.g. life satisfaction) on row $i$, $v_i$ its sampling variance, $\alpha$ are the population-level coefficients, $\beta_{0, \dots, 11\text{country}[i]}$ are the country-specific coefficients for the country indicated on row $i$, $\text{DAU}^{\text{CW}}_i$ the within-country centered year-aggregated daily (or monthly) active Facebook users, and $\text{DAU}^{\text{CB}}_i$ the between-country centered DAU (or MAU).

We conducted all data analyses with the R language for statistical computing [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan’s Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017]. We used default noninformative priors, 4 HMC chains with 4,000 iterations and first 2,000 as warmup for 8,000 total iterations; we report all parameters with their posterior means and 95% credible intervals (posterior 2.5 and 97.5 percentiles; CI), and other posterior probabilities as indicated in text.

\newpage

# Online supplement to The association between Facebook adoption and well-being (Vuorre and Przybylski): Monthly active users

<!-- Prepend table & figure numbers with S and reset counters -->
\setcounter{page}{1}
\setcounter{table}{0}
\setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}

In the main document, we analysed associations between well-being and daily active Facebook users (DAU). Here, we repeat those analyses but use monthly active users (MAU) as the predictor

```{r fig-data-mau}
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 2.3
#| fig.cap: "72 countries' monthly active Facebook users in two age brackets from 2008 to 2019. (Percentages may exceed 100\\% due to inaccurate estimation of either DAU or population size.) "
p_a + aes(y = mau)
```

Figure \@ref(fig:fig-data-mau) shows that the trends of Facebook adoption observed for DAU for mostly similar for MAU, but the overall rates were somewhat greater. We estimated the same model as in the main analyses; the key association parameters are shown in Table \@ref(tab:tab-world-mau). Overall, the results were qualitatively similar, but the associations with MAU tended to be smaller. In addition the within-country associations between life satisfaction and negative experiences and MAU were no longer credible at the 95% level.

```{r tab-world-mau}
#| include: true
tab_world %>% 
  filter(predictor == "mau") %>% 
  select(-predictor) %>% 
  mutate(
    across(
      ends_with("country"), 
      ~if_else(str_starts(., "-"), ., paste0("\\phantom{-}", .))
    )
  ) %>% 
  apa_table(
    caption = "Average Facebook MAU and well-being associations",
    font_size = "small",
    note = "LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences. Numbers indicate posterior means and 95\\%CIs.",
    span_text_columns = FALSE,
    escape = FALSE,
    placement = "htb",
    align = 'llll'
  )
```

Overall, the average results across demographics mirrored those with DAU (Figure \@ref(fig:fig-forest-mau)). However, many of the country-specific associations differed (individual countries in Figure \@ref(fig:fig-forest-mau)). In sum, these results suggest that for associations at the level of countries, the aggregate intensity of use (monthly or daily) did not play a large role.

```{r fig-forest-mau}
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 4.6
#| fig.cap: "Forest plot of estimated associations between country-year level per-capita monthly active Facebook users (MAU) and life satisfaction (LS), negative experiences (NE), and positive experiences (PE). Units indicate percentage change in outcome as function of percentage increase in within-country centered MAU. Filled points indicate estimates whose posterior 95\\%CI excluded zero."

tmp <- coefs %>%   
  filter(
    # name != "world",
    str_detect(Hypothesis, "_")
  ) %>% 
  separate(Hypothesis, c("Age", "Sex"), sep = "_") %>% 
  mutate(
    outcome = case_when(
      outcome == "Life_satisfaction" ~ "LS",
      outcome == "Negative_experiences" ~ "NE",
      outcome == "Positive_experiences" ~ "PE"
    )
  ) %>% 
  # mutate(outcome = str_glue("{outcome} ({Sex})")) %>% 
  filter(predictor == "mau")

tmp %>% 
  ggplot() +
  aes(
    x = Estimate, 
    y = fct_rev(country), 
    col = Age, 
    fill = interaction(Age, Star, sep = " "), 
    shape = Sex
  ) +
  scale_y_discrete(
    "Country",
    expand = expansion(.015),
    labels = ~str_replace(., "World", "Average")
  ) +
  scale_x_continuous(
    "Association with monthly active Facebook users (95%CI)",
    breaks = extended_breaks(7),
    expand = expansion(.1)
  ) +
  scale_shape_manual(
    values = c(21, 22)
  ) +
  scale_color_brewer(
    "Age", palette = "Set1", aesthetics = c("color")
  ) +
  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
  geom_linerangeh(
    aes(xmin = CI.Lower, xmax = CI.Upper),
    size = .15, position = position_dodge2v(.7), 
    show.legend = FALSE
  ) +
  geom_point(
    size = .65, stroke = .45,
    position = position_dodge2v(.7)
  ) +
  facet_wrap(
    "outcome", scales = "free_x", nrow = 1,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  guides(
    fill = "none",
    color = guide_legend(override.aes = list(size = 1.5)),
    shape = guide_legend(override.aes = list(size = 1.5))
  ) +
  theme(
    # axis.ticks.y = element_blank(),
    axis.text.y = element_text(size = rel(0.7)),
    axis.title.y = element_blank(),
    panel.grid.major.y = element_line(
      size = .1, linetype = 2, color = "gray60"
    ),
    legend.position = "right"
  )
```

### 2022-09-16 ms.Rmd
Use PNAS template

@@
 ---
-title: The association between Facebook adoption and well-being
-shorttitle: Facebook and well-being
-leftheader: Facebook and well-being
+title: Estimating the association between Facebook adoption and well-being
+
+# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
 author:
   - name: Matti Vuorre
-    affiliation: 1
-    address: Oxford Internet Institute, University of Oxford
-    email: matti.vuorre@oii.ox.ac.uk
-    role:
-      - Design
-      - Administration
-      - Analysis
-      - Visualization
-      - Writing
+    affiliation: a
   - name: Andrew K. Przybylski
-    affiliation: 1
-    corresponding: yes
-    address: Oxford Internet Institute, University of Oxford
-    email: andy.przybylski@oii.ox.ac.uk
-    role:
-      - Design
-      - Administration
-      - Funding
-      - Resources
-      - Supervision
-      - Visualization
-      - Writing
+    affiliation: a,1
+address:
+  - code: a
+    address: Oxford Internet Institute, University of Oxford, 1 St Giles, Oxford OX1 3JS, United Kingdom
 
-affiliation:
-  - id: 1
-    institution: Oxford Internet Institute, University of Oxford
+corresponding_author:
+  code: 1
+  text: "To whom correspondence should be addressed. E-mail: andy.przybylski@oii.ox.ac.uk"
 
-authornote: |
-  \noindent \textbf{This manuscript is not yet peer-reviewed.}
+# For footer text
+lead_author_surname: Vuorre
 
-  This research was supported by the Huo Family Foundation and Economic and Social Research Council Grant ES/T008709/1.
-All code supporting this manuscript is available at X.
-This draft is available under [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/) at X.
+author_contributions: |
+  The authors made the following contributions.
+Matti Vuorre: Design, Administration, Analysis, Visualization, Writing; Andrew K.
+Przybylski: Design, Administration, Funding, Resources, Super- vision, Visualization, Writing.
 
+## Remove this if not required
+conflict_of_interest: |
   The authors declare no conflicts of interest.
 
-  The analytic code is available at (LINK).
-Researchers can contact Facebook (WHERE?) to access our code, the Facebook data, and a synthetic version of the Gallup data for reproducing and extending our analyses.
-  This study and methodology was reviewed and approved by the Oxford Internet Institute's Departmental Research Ethics Committee (SSH_OII_CIA_21_084).
+abstract: |
+  Social media's potential effects on well-being have received considerable research interest, but much of past work is hampered by an exclusive focus on demographics in the Global North and inaccurate self-reports of social media engagement.
+We describe associations linking 72 countries' Facebook adoption to the well-being of 946,798 individuals from 2008 to 2019.
+We found no associations suggesting that the global penetration of social media has caused widespread psychological harm: Facebook adoption predicted life satisfaction and positive experiences positively, and negative experiences negatively, both between countries and within countries but over time.
+Facebook adoption was more positively associated with well-being for younger individuals, but country-specific results were mixed.
+In order to move beyond studying aggregates and to better understand social media's causal effects, we need more transparent collaborative research between independent scientists and the technology industry.
 
-abstract: | 
-  Abstract.
+significance: |
+  Billions of individuals across the globe use social media on a regular basis.
+The widespread adoption of social media---most prominently Facebook---has fundamentally shifted how humans conduct their lives.
+Consequently, researchers, healthcare professionals, and policy makers have repeatedly raised alarms that the spread of social media may be negatively affecting individuals, particularly young ones, mental health and well-being on a global scale.
+We examined the plausibility of this idea by associating 72 nations' yearly Facebook adoption rates to the well-being of 946,798 individuals from 2008 to 2019.
+Overall, we found that increased rates of daily and monthly active Facebook users predicted greater levels of well-being, when comparing countries to other countries, or countries to themselves but over time.
+These findings should guide debate surrounding social media towards more empirical foundations: The importance of this topic requires that independent scientists gain access to more detailed data from the technology industry in order to better determine how and why modern online platforms might be affecting their users.
 
-keywords: well-being, social media
-# wordcount: 
-bibliography: "references.bib"
-floatsintext: yes
-linenumbers: no
-draft: no
-mask: no
-figurelist: no
-tablelist: no
-footnotelist: no
-header-includes:
-  - |
-    \makeatletter
-    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-1em}%
-      {\normalfont\normalsize\bfseries\typesectitle}}
+# acknowledgements: |
+#   Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.
 
-    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-\z@\relax}%
-      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-    \makeatother
+keywords:
+  - well-being
+  - social media
 
-csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
-documentclass: apa7
-classoption: jou
+## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
+pnas_type: pnasresearcharticle
+
+bibliography: references.bib
+csl: pnas.csl
+
+## change to true to add optional line numbering
+lineno: true
+
 output: 
-  papaja::apa6_pdf:
-    number_sections: false
+  rticles::pnas_article:
     keep_tex: false
-  papaja::apa6_docx: 
-    number_sections: false
-editor_options: 
-  chunk_output_type: console
-always_allow_html: true
 ---
@@
 library(brms)
+library(kableExtra)
 library(ggstance)
@@
 
-# For ordering outcomes
-oo <- c(
-  "Life_satisfaction", "Negative_experiences", "Positive_experiences"
-)
-
 # Directories for files
 dir.create("models", FALSE)
-dir.create("out", FALSE)
 
@@
   cache = TRUE,
+  echo = FALSE,
   include = FALSE,
@@
 )
-W <- 24
 ```
@@
 ```{r data-prepare}
-# Load and merge processed data
+# Load and merge data
+# Facebook -- this data only exists on FORT
 d_fb <- read_csv("data/fb.csv")
+# If you are not conducting these analyses on FORT, the above data is not 
+# available. Uncomment below to use a synthetic dataset instead.
+# d_fb <- read_csv("data/fb-SYNTHETIC.csv")  # If real FB data not available
+
+# Gallup
 d_gwp <- read_rds("data/gwp.rds") 
-# d_gwp <- read_rds("data/gwp-SYNTHETIC.rds") # If real data not available
-d_gwp <- d_gwp %>% 
-  mutate(outcome = factor(outcome, levels = oo))
+# d_gwp <- read_rds("data/gwp-SYNTHETIC.rds") # If real Gallup data not available
+
+# Population estimates
 d_pop <- read_rds("data/population.rds")
@@
     mau = mau / pop
-  )
+  ) %>% 
+  select(-pop)
 
@@
 )
-
 fits <- dm %>% 
@@
   nest() %>% 
+  crossing(
+    nesting(
+      model = list(model_dau, model_mau),
+      predictor = c("dau", "mau")
+    )
+  ) %>% 
   mutate(
-    dau = map2(
-      data, outcome,
+    fit = pmap(
+      list(model, data, outcome, predictor),
       ~brm(
-        model_dau,
-        cores = 8, chains = 4, threads = 2,
-        backend = "cmdstanr",
-        adapt_delta = .95,
+        ..1,
+        cores = 4, chains = 4,
+        backend = "rstan",
+        control = list(adapt_delta = .95),
         iter = 3000,
-        data = .x,
-        file = str_glue("models/brm-dau-{.y}")
-      )
-    ),
-    mau = map2(
-      data, outcome,
-      ~brm(
-        model_mau,
-        cores = 8, chains = 4, threads = 2,
-        backend = "cmdstanr",
-        adapt_delta = .95,
-        iter = 3000,
-        data = .x,
-        file = str_glue("models/brm-mau-{.y}")
+        data = ..2,
+        file = str_glue("models/brm-{..3}-{..4}")
       )
@@
 
-# Results
-
-```{r fig-data}
-#| include: true
-#| out.width: "\\textwidth"
-#| fig.env: "figure*"
-#| fig.height: 5.4
-#| fig.cap: Time courses of key variables.
-A.
-Daily and monthly Facebook users in two age brackets for 72 countries from 2008 to 2019.
-B.
-Mean responses to three well-being scales in the Gallup World Poll from 72 countries from 2008 to 2019.
-
-# Figure of all variables over time
-p_a <- d_fb %>% 
-  pivot_longer(c(dau, mau), names_to = "outcome", values_to = "val") %>% 
-  mutate(outcome = if_else(outcome == "dau", "Daily FB users", "Monthly FB users")) %>% 
-  mutate(panel = str_glue("{outcome} ({age})")) %>% 
-  ggplot(aes(year, val, group = country)) +
-  scale_y_continuous(
-    "Percentage of population", 
-    expand = expansion(.03),
-    breaks = extended_breaks(),
-    labels = ~percent(.)
-  ) +
-  scale_x_continuous(
-    "Year", 
-    breaks = seq(2008, 2018, by = 2), 
-    minor_breaks = seq(2009, 2019, by = 2)
-  ) +
-  geom_line(size = .2, col = "gray30") +
-  geom_smooth(group = 1, method = "gam", se = F) +
-  facet_wrap("panel", nrow = 1) +
-  theme(
-    legend.position = "none",
-    axis.title.x = element_blank()
-  )
-
-p_b <- d %>% 
-  select(-c(mau, dau)) %>% 
-  # Exclude rows where FB data existed but not GWP data
-  drop_na(val) %>% 
-  # Actual lowest age in GWP
-  mutate(age = factor(age, labels = c("15-34", "35+"))) %>% 
-  mutate(panel = str_glue("{outcome} ({age})")) %>% 
-  ggplot(aes(year, val, group = country)) +
-  scale_color_brewer(palette = "Dark2") +
-  scale_y_continuous(
-    "Value", 
-    expand = expansion(.01),
-    breaks = extended_breaks()
-  ) +
-  scale_x_continuous(
-    "Year", 
-    breaks = seq(2008, 2018, by = 2),
-    labels = ~str_replace(., "20", "'")
-  ) +
-  # Aggregate over sex
-  geom_line(size = .2, col = "gray30") +
-  geom_smooth(group = 1, method = "gam", se = F) +
-  facet_grid(sex~panel, labeller = as_labeller(~str_replace(., "_", " "))) +
-  theme(legend.position = "none")
-
-(p_a / p_b) +
-  plot_layout(heights = c(4, 6)) +
-  plot_annotation(tag_levels = "A")
-# ggsave("out/Fig-data.png", width = W, height = W*.66, units = "cm", dpi = 400)
-```
-
-```{r fig-forest-prepare}
+```{r coefficients-calculate}
+path <- "models/coefficients.rds"
+if (!file.exists(path)) {
   # Calculate contrasts for each outcome
@@
     "Male" = "dau_cw + dau_cw:sex1 * 1 = 0",
-  "Between-country" = "dau_cb = 0"
+    "Between-country" = "dau_cb = 0",
+    "X by age" = "dau_cw:age1 = 0",
+    "X by sex" = "dau_cw:sex1 = 0",
+    "X by age by sex" = "dau_cw:age1:sex1 = 0"
   )
@@
     "Male" = "mau_cw + mau_cw:sex1 * 1 = 0",
-  "Between-country" = "mau_cb = 0"
+    "Between-country" = "mau_cb = 0",
+    "X by age" = "mau_cw:age1 = 0",
+    "X by sex" = "mau_cw:sex1 = 0",
+    "X by age by sex" = "mau_cw:age1:sex1 = 0"
   )
   coefs <- fits %>% 
-  ungroup() %>% 
-  pivot_longer(c(dau, mau), names_to = "predictor", values_to = "fit") %>% 
+    select(-data, -model) %>% 
     mutate(h = if_else(predictor == "dau", list(h_dau), list(h_mau))) %>% 
@@
     ) %>% 
-  select(-fit, -h, -data)
+    select(-fit, -h)
+
+  # Both predictor and outcome are 0-1, so scale can be interpreted as % change as a function of % change
 
@@
     unnest(value) %>% 
-  mutate(country = if_else(name == "country", as.character(Group), "World")) %>% 
-  mutate(country = fct_relevel(country, "World")) %>% 
+    mutate(
+      country = if_else(name == "country", as.character(Group), "World")
+    ) %>% 
     # Between country contrast not country-specific!
-  filter(!(Hypothesis == "Between-country" & country != "World"))
+    filter(!(Hypothesis == "Between-country" & country != "World")) %>% 
+    # Neatly formatted result string
+    mutate(
+      across(c(Estimate, CI.Lower, CI.Upper), list("str" = ~number(., .01))),
+      result = str_glue("{Estimate_str}% [{CI.Lower_str}, {CI.Upper_str}]")
+    )
 
-# Both predictor and outcome are 0-1, so scale can be interpreted as % change as a function of % change
+  saveRDS(coefs, path)
+
+} else {coefs <- readRDS(path)}
 ```
 
-```{r fig-forest}
+The ways in which people use technology for most domains in life has changed dramatically since the mass introduction of the internet in the 1990s, and the subsequent technologies facilitated by it.
+Most prominently, the popularization of modern social media platforms in 2008 precipitated widespread changes to human activities via features such as marketplaces, personalized news feeds, photo sharing, live streaming, and other features that the "metaverse" promises to build on.
+The first social media with global adoption, MySpace (launched 2003) saw 115 million users in 2008---the year in which it was replaced as the leading platform by Facebook (2004).
+Today (2022-Q1), Facebook reports 2.94 billion monthly active users [@metaMetaReportsFirst2022], or about one third of the global population.
+Along with social media's global penetration, debate surrounding their potential effects on individual and collective well-being has intensified.
+
+Although reports of negative psychological outcomes associated social media are common in academic writing [@krossFacebookUsePredicts2013] and popular media [@thompsonSocialMediaAttention2021], evidence for harms is, on balance, more speculative than conclusive [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020].
+Recent results on the associations between social media use and well-being are mixed and depend on arbitrary analytic choices [@orbenSocialMediaEnduring2019].
+Other studies have reported that there have been few if any changes in associations linking technology use to mental health in this period of social media's global adoption [@vuorreThereNoEvidence2021].
+A general lack of validated measures, poorly specified causal models, and inadequate data have yielded a large number of low-quality studies [@parrySystematicReviewMetaanalysis2021; @sewallDoesObjectivelyMeasured2022].
+Furthermore, because nearly all investigations have focused on samples from the Global North [@ghaiSocialMediaAdolescent2022], we have next to no idea of how the wide adoption of social media platforms relates to psychological well-being across the world.
+
+To better understand the plausible range of associations, we linked data tracking Facebook's global adoption with three indicators of global well-being.
+We examined 72 countries' per capita daily active Facebook users (DAU) in two age brackets (13-34 and 35+ years) as predictors of life satisfaction (LS), negative (NE), and positive psychological experiences (PE) at the level of years spanning 2008 to 2019.
+The well-being data represented 946,798 individuals' responses from the nationally representative Gallup World Poll Survey [@gallupHowDoesGallup2014].
+We joined these unique datasets to conduct a descriptive study to answer three basic yet important questions: First, to what extent did Facebook adoption predict well-being?
+Second, do these associations differ by age or sex.
+And finally, how might these associations have differed between countries?
+
+```{r tab-world}
+#| echo: false
 #| include: true
 
-coefs %>%   
-  filter(str_detect(Hypothesis, "_")) %>% 
+# Average within- and between-country associations
+tab_world <- coefs %>% 
+  filter(
+    name == "world",
+    Hypothesis %in% c("Average", "Between-country")
+  ) %>% 
   mutate(
-    predictor = if_else(
-      predictor == "dau", 
-      "Daily FB users", 
-      "Monthly FB users"
+    outcome = case_when(
+      outcome == "Life_satisfaction" ~ "LS",
+      outcome == "Negative_experiences" ~ "NE",
+      outcome == "Positive_experiences" ~ "PE"
     )
   ) %>% 
+  select(
+    predictor, Outcome = outcome, Hypothesis, result
+  ) %>% 
+  pivot_wider(names_from = Hypothesis, values_from = result) %>% 
+  rename(
+    `Within country` = Average,
+    `Between country` = `Between-country`
+  ) %>% 
+  select(predictor, Outcome, `Between country`, `Within country`) %>% 
+  arrange(predictor, Outcome)
+
+tab_world %>% 
+  filter(predictor == "dau") %>% 
+  select(-predictor) %>% 
+  mutate(
+    across(
+      ends_with("country"), 
+      ~if_else(str_starts(., "-"), ., paste0("\\phantom{-}", .))
+    )
+  ) %>% 
+  apa_table(
+    caption = "Average Facebook DAU and well-being associations",
+    font_size = "small",
+    note = "LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences. Numbers indicate posterior means and 95\\%CIs.",
+    span_text_columns = FALSE,
+    escape = FALSE,
+    placement = "htb",
+    align = 'llll'
+  )
+```
+
+```{r}
+# How many people in GWP data
+d_gwp %>% 
+  group_by(outcome) %>% 
+  summarise(n = sum(n)) %>% 
+  pull(n) %>% max %>% number
+
+# Percentages of countries where DAU was over 25% by year
+tmp <- d_fb %>% 
+  group_by(year, age) %>% 
+  summarise(median_dau = percent(median(dau))) %>% 
+  pivot_wider(names_from = age, values_from = median_dau)
+tmp
+```
+
+Facebook adoption increased markedly from 2008 when the median per capita DAU across these 72 countries was `r tmp[1,2]` (ages 13-34) and `r tmp[1,3]`% (35+), to `r tmp[12,2]` (13-34) and `r tmp[12,3]` (35+; Figure 1A) in 2019.
+During this period Facebook adoption by younger individuals plateaued before saturation in many countries, but not for older individuals.
+At the same time, we did not observe correspondingly large and uniform changes across measures of well-being (Figure 1B) [@vuorreGlobalWellbeingMental2022].
+
+```{r fig-data, fig.pos = "H"}
+#| include: true
+#| fig.height: 3.6
+#| fig.width: 3.5
+#| fig.cap: "A.
+72 countries' daily active Facebook users in two age brackets from 2008 to 2019.
+(Percentages may exceed 100\\% due to inaccurate estimation of either DAU or population size.) B.
+The same 72 countries' mean responses to three well-being scales in the Gallup World Poll from 2008 to 2019, separated by age category and sex.
+LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences."
+
+# Figure of all variables over time
+p_a <- d_fb %>% 
+  ggplot(aes(year, dau, group = country)) +
+  scale_y_continuous(
+    "Percentage of population", 
+    expand = expansion(.03),
+    breaks = extended_breaks(),
+    labels = ~percent(.)
+  ) +
+  scale_x_continuous(
+    "Year", 
+    breaks = seq(2008, 2018, by = 2), 
+    labels = ~str_replace(., "20", "'"),
+    expand = expansion(0.01)
+  ) +
+  geom_line(size = .125) +
+  # geom_smooth(group = 1, method = "gam", se = F) +
+  facet_wrap("age", nrow = 1) +
+  theme(
+    legend.position = "none",
+    axis.title.x = element_blank()
+  ) +
+  theme(text = element_text(size = 5))
+
+p_b <- d %>% 
+  # Exclude rows where FB data existed but not GWP data
+  drop_na(val) %>% 
+  # Actual lowest age in GWP
+  mutate(age = factor(age, labels = c("15-34", "35+"))) %>% 
+  mutate(
+    outcome = case_when(
+      outcome == "Life_satisfaction" ~ "LS",
+      outcome == "Negative_experiences" ~ "NE",
+      outcome == "Positive_experiences" ~ "PE"
+    )
+  ) %>% 
+  mutate(panel = str_glue("{age} ({sex})")) %>% 
+  ggplot(aes(year, val, group = country)) +
+  scale_color_brewer(palette = "Dark2") +
+  scale_y_continuous(
+    "Value", 
+    expand = expansion(.01),
+    breaks = extended_breaks(),
+    labels = ~percent(.)
+  ) +
+  scale_x_continuous(
+    "Year", 
+    breaks = seq(2008, 2018, by = 2),
+    labels = ~str_replace(., "20", "'")
+  ) +
+  geom_line(size = .1) +
+  facet_grid(
+    outcome~panel, 
+    scales = "free_y",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(legend.position = "none") +
+  theme(text = element_text(size = 5))
+
+(p_a / p_b) +
+  plot_layout(heights = c(3, 7)) +
+  plot_annotation(tag_levels = "A")
+```
+
+To answer our first question of how Facebook adoption relates to well-being, we specified a multilevel linear meta-regression model of each well-being outcome on time, sex, age, and DAU (both within- and between-country-centered, see SI).
+We included all interactions between sex, age, and time, and sex, age, and DAU (within-country-centered), and allowed all parameters to vary randomly across countries.
+We first examined whether the relative standing of countries on their average Facebook adoption predicted well-being (the model's between-country associations).
+We found that countries with greater average DAU had somewhat higher levels of life satisfaction and positive experiences, and lower levels of negative experiences than countries with lower DAU (Table 1).
+However, there are large and important differences between countries in factors that might underlie differences in both social media adoption and well-being, such as socioeconomic conditions.
+As such, while descriptively informative, these associations are likely to indicate between-country confounding factors.
+
+```{r fig-forest, fig.pos="H"}
+#| echo: false
+#| include: true
+#| fig.height: 4.2
+#| fig.width: 3.5
+#| fig.cap: "Forest plot of estimated associations between country-year level per-capita daily active Facebook users (DAU) and life satisfaction (LS), negative experiences (NE), and positive experiences (PE).
+Units indicate percentage change in outcome as function of percentage increase in within-country centered DAU.
+Filled points indicate estimates whose posterior 95\\%CI excluded zero.
+See the online supplementary materials for corresponding figure but with MAU as predictor."
+
+tmp <- coefs %>%   
+  filter(
+    # name != "world",
+    str_detect(Hypothesis, "_")
+  ) %>% 
   separate(Hypothesis, c("Age", "Sex"), sep = "_") %>% 
-  mutate(outcome = str_glue("{outcome} ({Age})")) %>% 
   mutate(
-    # Order countries on increasing magnitude per panel
-    country_order = interaction(predictor, outcome, country),
-    country_order = as.numeric(fct_reorder(country_order, Estimate)),
-    # But also ensure that average ("World") is in bottom
-    country_order = if_else(
-      country == "World", country_order-10000, country_order
-    ),
-    country_order = factor(country_order)
+    outcome = case_when(
+      outcome == "Life_satisfaction" ~ "LS",
+      outcome == "Negative_experiences" ~ "NE",
+      outcome == "Positive_experiences" ~ "PE"
+    )
   ) %>% 
-  ggplot(aes(Estimate, country_order, col = Sex, shape = Star)) +
-  scale_y_discrete("Country", expand = expansion(.015)) +
+  # mutate(outcome = str_glue("{outcome} ({Sex})")) %>% 
+  filter(predictor == "dau")
+
+tmp %>%
+  ggplot() +
+  aes(
+    x = Estimate, 
+    y = fct_rev(country), 
+    col = Age, 
+    fill = interaction(Age, Star, sep = " "), 
+    shape = Sex
+  ) +
+  scale_y_discrete(
+    "Country",
+    expand = expansion(.015),
+    labels = ~str_replace(., "World", "Average")
+  ) +
   scale_x_continuous(
-    "Estimated association"
+    "Association with daily active Facebook users (95%CI)",
+    breaks = extended_breaks(7),
+    expand = expansion(.1)
   ) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_color_brewer("Sex", palette = "Set1") +
-  scale_size_manual(values = c(0.75, 1.5)) +
+  scale_shape_manual(
+    values = c(21, 22)
+  ) +
+  scale_color_brewer(
+    "Age", palette = "Set1", aesthetics = c("color")
+  ) +
+  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
   geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
@@
     aes(xmin = CI.Lower, xmax = CI.Upper),
-    size = .2, position = position_dodgev(.4)
+    size = .15, position = position_dodge2v(.7), 
+    show.legend = FALSE
   ) +
   geom_point(
-    fill = "white", aes(size = name),
-    position = position_dodgev(.6)
+    size = .65, stroke = .45,
+    position = position_dodge2v(.7)
   ) +
-  facet_grid2(
-    predictor~outcome, independent = "all", scales = "free",
+  facet_wrap(
+    "outcome", scales = "free_x", nrow = 1,
     labeller = as_labeller(~str_replace(., "_", " "))
   ) +
-  guides(shape = "none", size = "none") +
+  guides(
+    fill = "none",
+    color = guide_legend(override.aes = list(size = 1.5)),
+    shape = guide_legend(override.aes = list(size = 1.5))
+  ) +
   theme(
-    axis.ticks.y = element_blank(),
-    axis.text.y = element_blank(),
-    legend.position = "bottom"
+    text = element_text(size = 5),
+    axis.text.y = element_text(size = rel(0.9)),
+    axis.title.y = element_blank(),
+    panel.grid.major.y = element_line(
+      size = .1, linetype = 2, color = "gray60"
+    ),
+    legend.position = "bottom", 
+    legend.box.margin = margin(-15, 0, -10, 0, "pt"),
+    legend.background = element_rect(fill = NA),
+    legend.key = element_rect(fill = NA),
+    legend.text = element_text(size = rel(0.9))
   )
-
-ggsave("out/Fig-forest.png", width = W, height = W*.66, units = "cm", dpi = 400)
 ```
 
-```{r tab-between}
-#| include: true
+Variations in such confounding factors are likely to be significantly smaller within countries over time.
+We therefore next focused on the model's within-country associations, which measure the extent to which Facebook adoption in a given country predicted well-being in that country adjusting for general linear temporal trends in the well-being outcome.
+On average across countries, age, and sex, we found that years with greater than the average country's average DAU were associated with greater levels of life satisfaction and positive experiences, and lower levels of negative experiences (Table 1).
+For the average country in our sample, Facebook adoption positively predicted well-being.
+While these associations indicate relations within countries and adjust for confounders that vary linearly with time, by including time as a predictor, they are still susceptible to confounders and do not indicate causal relations.
+Rather, this association describes the fact that, all else being equal, years with greater Facebook adoption tended to be those with greater levels of well-being.
 
-# Between-country associations
+```{r demographics}
 coefs %>% 
-  mutate(
-    predictor = if_else(
-      predictor == "dau", 
-      "Daily FB users", 
-      "Monthly FB users"
-    )
+  filter(
+    str_detect(Hypothesis, " by "), 
+    name == "world"
   ) %>% 
-  mutate(outcome = str_replace(outcome, "_", " ")) %>% 
-  filter(Hypothesis == "Between-country") %>% 
   select(
-    Predictor = predictor, Outcome = outcome, Estimate, CI.Lower, CI.Upper
+    Predictor = predictor, Outcome = outcome, Hypothesis, result
   ) %>% 
-  arrange(Predictor, Outcome) %>% 
-  apa_table()
+  pivot_wider(names_from = Outcome, values_from = result)
+coefs %>% 
+  filter(
+    Hypothesis %in% c("13-34", "35+", "Female", "Male"),
+    name == "world"
+  ) %>% 
+  select(
+    Predictor = predictor, Outcome = outcome, Hypothesis, result
+  ) %>% 
+  pivot_wider(names_from = Outcome, values_from = result)
+
+tab_demo <- coefs %>% 
+  filter(
+    str_detect(Hypothesis, "_"),
+    name == "world"
+  ) %>% 
+  select(
+    Predictor = predictor, Outcome = outcome, Hypothesis, result
+  ) %>% 
+  pivot_wider(names_from = Outcome, values_from = result)
+tab_demo
 ```
 
+We then turned to our second question and assessed whether within-country associations linking Facebook adoption to well-being differed between the demographic groups.
+Differences in the association linking Facebook adoption and well-being were greater between the younger and older demographics than they were between females and males (Figure 2, Average).
+DAU predicted life satisfaction more positively in the younger age bracket, but these estimates' CIs did not exclude zero.
+DAU predicted negative experiences negatively in the younger age group, but positively for older males.
+These differences were less pronounced for positive experiences, which were positively associated with DAU only in the 13-34 year old male group.
+These results show that Facebook adoption was, for the average nation in our sample, more positively predictive of well-being for individuals below 35, and that differences between males and females were generally smaller than those between age groups.
+
+```{r}
+# Can we show regions in the forest plot as secondary axis? 
+# Table of percentages of countries with credible associations
+tmp <- coefs %>% 
+  filter(name == "country", Hypothesis == "Average") %>% 
+  group_by(predictor, outcome, Star, direction=sign(Estimate)) %>% 
+  count() %>% 
+  group_by(predictor, outcome) %>% 
+  # mutate(n = percent(n / sum(n), 1)) %>% 
+  mutate(x = interaction(Star, direction)) %>% 
+  select(-Star, -direction) %>% 
+  pivot_wider(names_from=x, values_from=n) %>% 
+  replace_na(list(`.-1` = 0, `.1` = 0, `*.1` = 0, `*.-1` = 0))
+tmp
+coefs %>% 
+  filter(predictor == "dau", name == "country", Hypothesis == "Average") %>% 
+  filter(Star=="*") %>% 
+  arrange(outcome, country) %>% 
+  select(outcome, country, Estimate:CI.Upper)
+```
+
+However, while informative aggregates, these results do not describe associations between Facebook adoption and well-being for any individual country, but rather their averages.
+To answer our third question, we computed country-specific estimates for each sex and age group (Figure 2).
+On average, for life satisfaction, `r tmp[1, 5]` countries credibly positive associations.
+For negative experiences, `r tmp[2, 6]` countries had a credibly negative association, and `r tmp[3, 5]` countries had a credibly positive association between DAU and positive experiences.
+There were no credible (at the 95% level) country-level negative associations between DAU and life-satisfaction.
+Although many country-level estimates were uncertain, these results aligned with the general pattern of positive associations between Facebook adoption and country-level well-being.
+
 ```{r fig-ce-prepare}
+#| eval: false
 # Create a predictor table with evenly spaced mau_cw values for each country
@@
 ```{r fig-ce}
+#| eval: false
 #| include: true
@@
   theme(legend.position = "none")
-ggsave("out/Fig-mau-conditional.png", width = W, height = W*.5, units = "cm", dpi = 400)
 ```
 
-# Discussion
+We found that, overall, Facebook adoption positively predicted well-being.
+This association held when comparing countries to other countries and to themselves over time.
+While these descriptive results do not speak to causal effects, they align with other recent findings suggesting that technology has not become increasingly harmful over time [@vuorreThereNoEvidence2021], and that increased adoption of general internet technologies are not, overall, associated with psychological harms [@vuorreGlobalWellbeingMental2022].
+That said, these conclusions are qualified because our focus on daily active users could miss those who use Facebook less regularly.
+To test this possibility, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor.
+Those results were substantively the same (see online supplement).
+
+It is widely accepted that social media and the Internet more broadly have changed how humans socialize, organize, and seek leisure, but it is not obvious or necessary that their wide adoption has influenced well-being.
+In this study we used the best data available to describe how global Facebook adoption relates to well-being across 72 countries over a 12-year period.
+We found generally positive associations between Facebook adoption and well-being which were partially qualified by demographics and not uniform across countries.
+
+We did not find evidence that increased social media adoption is consistently negatively associated with well-being.
+Nevertheless, our analyses cannot and do not rule out that possibility because more fine-grained data needed to demonstrate this more conclusively either do not exist or are not available.
+If we are to move past description to prediction or intervention, independent scientists and online platforms will need to collaborate in new, transparent ways.
+As it stands now, only a handful of scientists working in the technology industry have the data required to advance this line of inquiry.
+If we are to understand and improve well-being in the digital age, this must change.
 
@@
 
-## Extended Methods
+## Data availability
 
-### Facebook engagement
+Both datasets (Facebook and Gallup) are proprietary and we therefore could not share them with this manuscript.
+The analytic code, along with synthetic datasets, is available at (LINK).
+Researchers can contact Facebook (ccobb@fb.com) to access our code, the Facebook data, and a synthetic version of the Gallup data for reproducing and extending our analyses.
+The Gallup data are available online to subscribing institutions.
+
+## Facebook data
 
@@
 
-We studied two metrics of Facebook adoption, daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (`r countries`).
+We studied two metrics of Facebook adoption, daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (see Figure 2).
 FB estimates yearly DAU & MAU with their corresponding means from June 1 to August 31, and rounds values greater than 10,000,000 to three significant digits, and values less than 10,000,000 to the nearest 10,000.
-These estimates are calculated separately for individuals aged 13-34 and 35+.
+We report analyses based on DAU in the main manuscript, and MAU in the online supplement.
+DAU and MAU estimates are calculated separately for individuals aged 13-34 and 35+.
 User age is determined based on Facebook profile information, which can be inaccurate (e.g.
 young individuals report an older age.) Accordingly, 0.008% of total MAU were trimmed to exclude accounts with unrealistic on non-reported age.
-An account's country is determined on a number of factors including the user's IP address and self-reported location.
+
+In personal communication, Facebook representatives explained the selection of countries as "The countries provided were selected based upon geographic and cultural diversity and criteria related to data quality, including that geographic and age attribution error is believed to be relatively small." A given user's country is determined based on a number of factors, including the user's IP address and self-reported location.
 
@@
 
-### Well-being
+The Facebook adoption data were made available to us on Facebook's Open Research Tool platform. Other researchers can contact Facebook (ccobb@fb.com) to access the dataset.
+
+## Well-being
 
@@
 Gallup World Poll (GWP) is a nationally representative annual survey of 1,000 civilian, non-institutionalised individuals aged 15 years or older from 164 countries conducted since 2005.
-The surveys are conducted face-to-face or on the phone in the respondents’ native language and by local interviewers (for details, see [@gallupGallupWorldPoll2020; @gallupHowDoesGallup2014]).
+The surveys are conducted face-to-face or on the phone in the respondents’ native language and by local interviewers (for details, see [@gallupHowDoesGallup2014]).
 We studied Positive (PE) and Negative Experiences (NE), and life satisfaction.
@@
 
-### Data analysis
+## Data analysis
 
-Before analysing the data, we converted Facebook DAU and MAU to proportions of each country's yearly population sizes using population data from World Bank (midyear estimates; <https://data.worldbank.org/indicator/SP.POP.TOTL>).
-For Taiwan, we used population data from Wikipedia (<https://en.wikipedia.org/wiki/Demographics_of_Taiwan#Population_census>), because the World Bank data does not include Taiwan.
+Before analysing the data, we converted Facebook DAU and MAU to proportions of each country's and age group's yearly population sizes using population data from the United Nations Department of Economic and Social affairs (<https://population.un.org/wpp/Download/Standard/Population/>).
 
@@
 Because we aggregated the outcomes, we included to standard errors of the outcome in the model to account for the varying group sizes.
+Formally, we specified the model as
 
-We conducted all data analyses with the R language for statistical computing [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan’s Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021].
-We used default noninformative priors, 4 HMC chains with 3,000 iterations and first 1,500 as warmup for 6,000 total iterations; we report all parameters with their posterior means and 95% credible intervals (posterior 2.5 and 97.5 percentiles; CI), and other posterior probabilities as indicated in text.
+$$
+\begin{aligned} 
+y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i), \\
+\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \\
+&\quad\ (\alpha_{1} + \beta_{1\text{country}[i]})\text{Sex}_i + \\
+&\quad\ (\alpha_{2} + \beta_{2\text{country}[i]})\text{Age}_i + \\
+&\quad\ (\alpha_{3} + \beta_{3\text{country}[i]})\text{Time}_i + \\
+&\quad\ (\alpha_{4} + \beta_{4\text{country}[i]})\text{DAU}^{\text{CW}}_i + \\
+&\quad\ (\alpha_{5} + \beta_{5\text{country}[i]})\text{Sex}_i \times \text{Time}_i + \\
+&\quad\ (\alpha_{6} + \beta_{6\text{country}[i]})\text{Age}_i \times \text{Time}_i + \\
+&\quad\ (\alpha_{7} + \beta_{7\text{country}[i]})\text{Sex}_i \times \text{Age}_i + \\
+&\quad\ (\alpha_{8} + \beta_{8\text{country}[i]})\text{Sex}_i \times \text{Age}_i \times \text{Time}_i + \\
+&\quad\ (\alpha_{9} + \beta_{9\text{country}[i]})\text{Sex}_i \times \text{DAU}^{\text{CW}}_i + \\
+&\quad\ (\alpha_{10} + \beta_{10\text{country}[i]})\text{Age}_i \times \text{DAU}^{\text{CW}}_i + \\
+&\quad\ (\alpha_{11} + \beta_{11\text{country}[i]})\text{Sex}_i \times \text{Age}_i \times \text{DAU}^{\text{CW}}_i + \\
+&\quad\ \alpha_{12} \text{DAU}^{\text{CB}}_i,
+\\
+\pmb{\beta} &\sim \text{MVN}(\pmb{0}, \Sigma).
+\end{aligned}
+$$
+
+Where $y_i$ is the outcome (e.g.
+life satisfaction) on row $i$, $v_i$ its sampling variance, $\alpha$ are the population-level coefficients, $\beta_{0, \dots, 11\text{country}[i]}$ are the country-specific coefficients for the country indicated on row $i$, $\text{DAU}^{\text{CW}}_i$ the within-country centered year-aggregated daily (or monthly) active Facebook users, and $\text{DAU}^{\text{CB}}_i$ the between-country centered DAU (or MAU).
+
+We conducted all data analyses with the R language for statistical computing [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan’s Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017].
+We used default noninformative priors, 4 HMC chains with 4,000 iterations and first 2,000 as warmup for 8,000 total iterations; we report all parameters with their posterior means and 95% credible intervals (posterior 2.5 and 97.5 percentiles; CI), and other posterior probabilities as indicated in text.
+
+<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
+\showmatmethods
+<!-- \showacknow -->
+\pnasbreak
+
+\clearpage
+
+# Online supplement to The association between Facebook adoption and well-being (Vuorre and Przybylski): Monthly active users
+
+<!-- Prepend table & figure numbers with S and reset counters -->
+\setcounter{page}{1}
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+
+In the main document, we analysed associations between well-being and daily active Facebook users (DAU). Here, we repeat those analyses but use monthly active users (MAU) as the predictor
+
+```{r fig-data-mau, fig.pos="H"}
+#| include: true
+#| fig.height: 1.4
+#| fig.width: 3.5
+#| fig.cap: "72 countries' monthly active Facebook users in two age brackets from 2008 to 2019. (Percentages may exceed 100\\% due to inaccurate estimation of either DAU or population size.) "
+p_a + aes(y = mau)
+```
+
+Figure S1 shows that the trends of Facebook adoption observed for DAU for mostly similar for MAU, but the overall rates were somewhat greater.
+We estimated the same model as in the main analyses; the key association parameters are shown in Table S1.
+Overall, the results were qualitatively similar, but the associations with MAU tended to be smaller.
+In addition the within-country associations between life satisfaction and negative experiences and MAU were no longer credible at the 95% level.
+
+```{r tab-world-mau}
+#| include: true
+tab_world %>% 
+  filter(predictor == "mau") %>% 
+  select(-predictor) %>% 
+  mutate(
+    across(
+      ends_with("country"), 
+      ~if_else(str_starts(., "-"), ., paste0("\\phantom{-}", .))
+    )
+  ) %>% 
+  apa_table(
+    caption = "Average Facebook MAU and well-being associations",
+    font_size = "small",
+    note = "LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences. Numbers indicate posterior means and 95\\%CIs.",
+    span_text_columns = FALSE,
+    escape = FALSE,
+    placement = "htb",
+    align = 'llll'
+  )
+```
+
+Overall, the average results across demographics mirrored those with DAU (Figure S2).
+However, many of the country-specific associations differed (individual countries in Figure S2).
+In sum, these results suggest that for associations at the level of countries, the aggregate intensity of use (monthly or daily) did not play a large role.
+
+```{r fig-forest-mau, fig.pos="H"}
+#| echo: false
+#| include: true
+#| fig.height: 4.2
+#| fig.width: 3.5
+#| fig.cap: "Forest plot of estimated associations between country-year level per-capita monthly active Facebook users (MAU) and life satisfaction (LS), negative experiences (NE), and positive experiences (PE).
+Units indicate percentage change in outcome as function of percentage increase in within-country centered MAU.
+Filled points indicate estimates whose posterior 95\\%CI excluded zero."
+
+tmp <- coefs %>%   
+  filter(
+    # name != "world",
+    str_detect(Hypothesis, "_")
+  ) %>% 
+  separate(Hypothesis, c("Age", "Sex"), sep = "_") %>% 
+  mutate(
+    outcome = case_when(
+      outcome == "Life_satisfaction" ~ "LS",
+      outcome == "Negative_experiences" ~ "NE",
+      outcome == "Positive_experiences" ~ "PE"
+    )
+  ) %>% 
+  # mutate(outcome = str_glue("{outcome} ({Sex})")) %>% 
+  filter(predictor == "mau")
+
+tmp %>% 
+  ggplot() +
+  aes(
+    x = Estimate, 
+    y = fct_rev(country), 
+    col = Age, 
+    fill = interaction(Age, Star, sep = " "), 
+    shape = Sex
+  ) +
+  scale_y_discrete(
+    "Country",
+    expand = expansion(.015),
+    labels = ~str_replace(., "World", "Average")
+  ) +
+  scale_x_continuous(
+    "Association with monthly active Facebook users (95%CI)",
+    breaks = extended_breaks(7),
+    expand = expansion(.1)
+  ) +
+  scale_shape_manual(
+    values = c(21, 22)
+  ) +
+  scale_color_brewer(
+    "Age", palette = "Set1", aesthetics = c("color")
+  ) +
+  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
+  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
+  geom_linerangeh(
+    aes(xmin = CI.Lower, xmax = CI.Upper),
+    size = .15, position = position_dodge2v(.7), 
+    show.legend = FALSE
+  ) +
+  geom_point(
+    size = .65, stroke = .45,
+    position = position_dodge2v(.7)
+  ) +
+  facet_wrap(
+    "outcome", scales = "free_x", nrow = 1,
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  guides(
+    fill = "none",
+    color = guide_legend(override.aes = list(size = 1.5)),
+    shape = guide_legend(override.aes = list(size = 1.5))
+  ) +
+  theme(
+    text = element_text(size = 5),
+    axis.text.y = element_text(size = rel(0.9)),
+    axis.title.y = element_blank(),
+    panel.grid.major.y = element_line(
+      size = .1, linetype = 2, color = "gray60"
+    ),
+    legend.position = "bottom", 
+    legend.box.margin = margin(-15, 0, -10, 0, "pt"),
+    legend.background = element_rect(fill = NA),
+    legend.key = element_rect(fill = NA),
+    legend.text = element_text(size = rel(0.9))
+  )
+```

### 2022-09-16 ms.Rmd
edits

@@
 We describe associations linking 72 countries' Facebook adoption to the well-being of 946,798 individuals from 2008 to 2019.
-We found no associations suggesting that the global penetration of social media has caused widespread psychological harm: Facebook adoption predicted life satisfaction and positive experiences positively, and negative experiences negatively, both between countries and within countries but over time.
+We found no associations suggesting that the global penetration of social media has caused widespread psychological harm: Facebook adoption predicted life satisfaction and positive experiences positively, and negative experiences negatively, both between countries and within countries but over time, and the associations were small.
 Facebook adoption was more positively associated with well-being for younger individuals, but country-specific results were mixed.
@@
 The widespread adoption of social media---most prominently Facebook---has fundamentally shifted how humans conduct their lives.
-Consequently, researchers, healthcare professionals, and policy makers have repeatedly raised alarms that the spread of social media may be negatively affecting individuals, particularly young ones, mental health and well-being on a global scale.
+Consequently, researchers, healthcare professionals, and policy makers have repeatedly raised alarms that the spread of social media may be negatively affecting individuals', particularly young ones', mental health and well-being on a global scale.
 We examined the plausibility of this idea by associating 72 nations' yearly Facebook adoption rates to the well-being of 946,798 individuals from 2008 to 2019.
-Overall, we found that increased rates of daily and monthly active Facebook users predicted greater levels of well-being, when comparing countries to other countries, or countries to themselves but over time.
-These findings should guide debate surrounding social media towards more empirical foundations: The importance of this topic requires that independent scientists gain access to more detailed data from the technology industry in order to better determine how and why modern online platforms might be affecting their users.
+Overall, we found that increased rates of daily and monthly active Facebook users slightly predicted greater levels of well-being, when comparing countries to other countries, or countries to themselves but over time.
+These findings should guide debate surrounding social media towards more empirical foundations: The importance of this topic requires that independent scientists gain access to more detailed data from the technology industry in order to better determine how, when, and why modern online platforms might be affecting their users.
 
@@
 ---
+
+\raggedbottom
 
@@
 
-The ways in which people use technology for most domains in life has changed dramatically since the mass introduction of the internet in the 1990s, and the subsequent technologies facilitated by it.
-Most prominently, the popularization of modern social media platforms in 2008 precipitated widespread changes to human activities via features such as marketplaces, personalized news feeds, photo sharing, live streaming, and other features that the "metaverse" promises to build on.
-The first social media with global adoption, MySpace (launched 2003) saw 115 million users in 2008---the year in which it was replaced as the leading platform by Facebook (2004).
+The ways in which people use technology for most domains in life has changed dramatically since the mass introduction of the Internet in the 1990s, and the subsequent technologies facilitated by it.
+Most prominently, the popularization of modern social media platforms circa 2008 precipitated widespread changes to human activities via features such as marketplaces, personalized news feeds, photo sharing, live streaming, and other features that the "metaverse" now promises to build on.
+The first social media with broad adoption, MySpace (launched 2003) saw 115 million users in 2008---the year in which it was replaced as the leading platform by Facebook (2004).
 Today (2022-Q1), Facebook reports 2.94 billion monthly active users [@metaMetaReportsFirst2022], or about one third of the global population.
@@
 
-Although reports of negative psychological outcomes associated social media are common in academic writing [@krossFacebookUsePredicts2013] and popular media [@thompsonSocialMediaAttention2021], evidence for harms is, on balance, more speculative than conclusive [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020].
+Although reports of negative psychological outcomes associated with social media are common in academic and popular writing [@krossFacebookUsePredicts2013; @thompsonSocialMediaAttention2021], evidence for harms is, on balance, more speculative than conclusive [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020].
 Recent results on the associations between social media use and well-being are mixed and depend on arbitrary analytic choices [@orbenSocialMediaEnduring2019].
@@
 A general lack of validated measures, poorly specified causal models, and inadequate data have yielded a large number of low-quality studies [@parrySystematicReviewMetaanalysis2021; @sewallDoesObjectivelyMeasured2022].
-Furthermore, because nearly all investigations have focused on samples from the Global North [@ghaiSocialMediaAdolescent2022], we have next to no idea of how the wide adoption of social media platforms relates to psychological well-being across the world.
+Furthermore, because nearly all investigations have focused on samples from the Global North [@ghaiSocialMediaAdolescent2022], we have next to no idea of how the wider adoption of social media platforms relates to psychological well-being across the world.
 
-To better understand the plausible range of associations, we linked data tracking Facebook's global adoption with three indicators of global well-being.
+To better understand the plausible range of associations, we linked data tracking Facebook's global adoption with three indicators of well-being.
 We examined 72 countries' per capita daily active Facebook users (DAU) in two age brackets (13-34 and 35+ years) as predictors of life satisfaction (LS), negative (NE), and positive psychological experiences (PE) at the level of years spanning 2008 to 2019.
 The well-being data represented 946,798 individuals' responses from the nationally representative Gallup World Poll Survey [@gallupHowDoesGallup2014].
-We joined these unique datasets to conduct a descriptive study to answer three basic yet important questions: First, to what extent did Facebook adoption predict well-being?
+We joined these unique datasets to conduct a descriptive study to answer three basic yet important questions: First, to what extent is Facebook adoption associated with well-being?
 Second, do these associations differ by age or sex.
@@
 
+To answer our first question of how Facebook adoption relates to well-being, we specified a multilevel linear meta-regression model of each well-being outcome on time, sex, age, and DAU (both within- and between-country-centered, see SI).
+We included all interactions between sex, age, and time, and sex, age, and DAU (within-country-centered), and allowed all parameters to vary randomly across countries.
+We first examined whether the relative standing of countries on their average Facebook adoption predicted well-being (the model's between-country associations).
+We found that countries with greater average DAU had somewhat higher levels of life satisfaction and positive experiences, and lower levels of negative experiences than countries with lower DAU (Table 1).
+However, there are large and important differences between countries in factors that might underlie differences in both social media adoption and well-being, such as socioeconomic conditions.
+While descriptively informative, these associations are likely to indicate between-country confounding factors.
+
 ```{r fig-data, fig.pos = "H"}
@@
   ) +
-  theme(text = element_text(size = 5))
+  theme(
+    strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
+    text = element_text(size = 5)
+    )
 
@@
   ) +
-  theme(legend.position = "none") +
-  theme(text = element_text(size = 5))
+  theme(
+    strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
+    strip.text.y = element_text(margin = margin(0,2,0,2, "pt")),
+    legend.position = "none",
+    text = element_text(size = 5)
+  )
 
@@
 
-To answer our first question of how Facebook adoption relates to well-being, we specified a multilevel linear meta-regression model of each well-being outcome on time, sex, age, and DAU (both within- and between-country-centered, see SI).
-We included all interactions between sex, age, and time, and sex, age, and DAU (within-country-centered), and allowed all parameters to vary randomly across countries.
-We first examined whether the relative standing of countries on their average Facebook adoption predicted well-being (the model's between-country associations).
-We found that countries with greater average DAU had somewhat higher levels of life satisfaction and positive experiences, and lower levels of negative experiences than countries with lower DAU (Table 1).
-However, there are large and important differences between countries in factors that might underlie differences in both social media adoption and well-being, such as socioeconomic conditions.
-As such, while descriptively informative, these associations are likely to indicate between-country confounding factors.
+Variations in such confounding factors are likely to be significantly smaller within countries over time.
+We therefore next focused on the model's within-country associations, which measure the extent to which Facebook adoption in a given country predicted well-being in that country adjusting for general linear temporal trends in the well-being outcome.
+On average across age, and sex, we found that years with greater than the country's average DAU were associated with greater levels of life satisfaction and positive experiences, and lower levels of negative experiences (Table 1), although the first association's 95%CI contained zero.
+For the average country in our sample, Facebook adoption positively predicted well-being.
+The magnitudes of these associations were small; a one-percent increase in DAU predicted a `r tab_world[3,4]` increase in positive experiences for the average country.
+While these associations indicate relations within countries and adjust for confounders that vary linearly with time by including time as a predictor, they are still susceptible to confounders and do not indicate causal relations.
+Rather, this association describes that, all else being equal, years with greater Facebook adoption tended to be those with greater levels of well-being.
+
+```{r demographics}
+coefs %>% 
+  filter(
+    str_detect(Hypothesis, " by "), 
+    name == "world"
+  ) %>% 
+  select(
+    Predictor = predictor, Outcome = outcome, Hypothesis, result
+  ) %>% 
+  pivot_wider(names_from = Outcome, values_from = result)
+coefs %>% 
+  filter(
+    Hypothesis %in% c("13-34", "35+", "Female", "Male"),
+    name == "world"
+  ) %>% 
+  select(
+    Predictor = predictor, Outcome = outcome, Hypothesis, result
+  ) %>% 
+  pivot_wider(names_from = Outcome, values_from = result)
+
+tab_demo <- coefs %>% 
+  filter(
+    str_detect(Hypothesis, "_"),
+    name == "world"
+  ) %>% 
+  select(
+    Predictor = predictor, Outcome = outcome, Hypothesis, result
+  ) %>% 
+  pivot_wider(names_from = Outcome, values_from = result)
+tab_demo
+```
+
+We then turned to our second question and assessed whether within-country associations linking Facebook adoption to well-being differed between age and sex.
+Differences in the associations were greater between the younger and older demographics than they were between females and males (Figure 2, Average).
+DAU predicted life satisfaction more positively in the younger age bracket, but these estimates' CIs did not exclude zero.
+DAU predicted negative experiences negatively only in the younger age group.
+These differences were less pronounced for positive experiences.
+These results show that Facebook adoption was, for the average nation in our sample, more positively predictive of well-being for individuals below 35, and that differences between males and females were generally smaller than those between age groups.
+Importantly, they did not indicate that the well-being of younger individuals is particularly linked to social media adoption.
+
+```{r}
+# Can we show regions in the forest plot as secondary axis? 
+# Table of percentages of countries with credible associations
+tmp <- coefs %>% 
+  filter(name == "country", Hypothesis == "Average") %>% 
+  group_by(predictor, outcome, Star, direction=sign(Estimate)) %>% 
+  count() %>% 
+  group_by(predictor, outcome) %>% 
+  # mutate(n = percent(n / sum(n), 1)) %>% 
+  mutate(x = interaction(Star, direction)) %>% 
+  select(-Star, -direction) %>% 
+  pivot_wider(names_from=x, values_from=n) %>% 
+  replace_na(list(`.-1` = 0, `.1` = 0, `*.1` = 0, `*.-1` = 0))
+tmp
+coefs %>% 
+  filter(predictor == "dau", name == "country", Hypothesis == "Average") %>% 
+  filter(Star=="*") %>% 
+  arrange(outcome, country) %>% 
+  select(outcome, country, Estimate:CI.Upper)
+```
+
+However, while informative aggregates, these results do not describe associations between Facebook adoption and well-being for any individual country, but rather their averages.
+To answer our third question, we computed country-specific estimates for each sex and age group (Figure 2).
+For life satisfaction, `r tmp[1, 5]` countries had credibly positive average associations.
+For negative experiences, `r tmp[2, 6]` countries had credibly negative average association, and `r tmp[3, 5]` countries had a credibly positive average association between DAU and positive experiences.
+There were no credible (at the 95% level) country-level negative associations between DAU and life-satisfaction.
+Although many country-level estimates were uncertain, these results aligned with the general pattern of positive associations between Facebook adoption and country-level well-being.
+
+We found that, overall, Facebook adoption positively predicted well-being.
+This association held when comparing countries to other countries and to themselves over time.
+While these descriptive results do not speak to causal effects, they align with other recent findings suggesting that technology has not become increasingly harmful over time [@vuorreThereNoEvidence2021], and that the increased adoption of Internet technologies is not, overall, associated with widespread psychological harms [@vuorreGlobalWellbeingMental2022].
+That said, these conclusions are qualified because our focus on daily active users could miss those who use Facebook less regularly.
+To test this possibility, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor.
+Those results were substantively the same (see online supplement).
 
@@
     text = element_text(size = 5),
+    strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
     axis.text.y = element_text(size = rel(0.9)),
@@
 ```
-
-Variations in such confounding factors are likely to be significantly smaller within countries over time.
-We therefore next focused on the model's within-country associations, which measure the extent to which Facebook adoption in a given country predicted well-being in that country adjusting for general linear temporal trends in the well-being outcome.
-On average across countries, age, and sex, we found that years with greater than the average country's average DAU were associated with greater levels of life satisfaction and positive experiences, and lower levels of negative experiences (Table 1).
-For the average country in our sample, Facebook adoption positively predicted well-being.
-While these associations indicate relations within countries and adjust for confounders that vary linearly with time, by including time as a predictor, they are still susceptible to confounders and do not indicate causal relations.
-Rather, this association describes the fact that, all else being equal, years with greater Facebook adoption tended to be those with greater levels of well-being.
-
-```{r demographics}
-coefs %>% 
-  filter(
-    str_detect(Hypothesis, " by "), 
-    name == "world"
-  ) %>% 
-  select(
-    Predictor = predictor, Outcome = outcome, Hypothesis, result
-  ) %>% 
-  pivot_wider(names_from = Outcome, values_from = result)
-coefs %>% 
-  filter(
-    Hypothesis %in% c("13-34", "35+", "Female", "Male"),
-    name == "world"
-  ) %>% 
-  select(
-    Predictor = predictor, Outcome = outcome, Hypothesis, result
-  ) %>% 
-  pivot_wider(names_from = Outcome, values_from = result)
-
-tab_demo <- coefs %>% 
-  filter(
-    str_detect(Hypothesis, "_"),
-    name == "world"
-  ) %>% 
-  select(
-    Predictor = predictor, Outcome = outcome, Hypothesis, result
-  ) %>% 
-  pivot_wider(names_from = Outcome, values_from = result)
-tab_demo
-```
-
-We then turned to our second question and assessed whether within-country associations linking Facebook adoption to well-being differed between the demographic groups.
-Differences in the association linking Facebook adoption and well-being were greater between the younger and older demographics than they were between females and males (Figure 2, Average).
-DAU predicted life satisfaction more positively in the younger age bracket, but these estimates' CIs did not exclude zero.
-DAU predicted negative experiences negatively in the younger age group, but positively for older males.
-These differences were less pronounced for positive experiences, which were positively associated with DAU only in the 13-34 year old male group.
-These results show that Facebook adoption was, for the average nation in our sample, more positively predictive of well-being for individuals below 35, and that differences between males and females were generally smaller than those between age groups.
-
-```{r}
-# Can we show regions in the forest plot as secondary axis? 
-# Table of percentages of countries with credible associations
-tmp <- coefs %>% 
-  filter(name == "country", Hypothesis == "Average") %>% 
-  group_by(predictor, outcome, Star, direction=sign(Estimate)) %>% 
-  count() %>% 
-  group_by(predictor, outcome) %>% 
-  # mutate(n = percent(n / sum(n), 1)) %>% 
-  mutate(x = interaction(Star, direction)) %>% 
-  select(-Star, -direction) %>% 
-  pivot_wider(names_from=x, values_from=n) %>% 
-  replace_na(list(`.-1` = 0, `.1` = 0, `*.1` = 0, `*.-1` = 0))
-tmp
-coefs %>% 
-  filter(predictor == "dau", name == "country", Hypothesis == "Average") %>% 
-  filter(Star=="*") %>% 
-  arrange(outcome, country) %>% 
-  select(outcome, country, Estimate:CI.Upper)
-```
-
-However, while informative aggregates, these results do not describe associations between Facebook adoption and well-being for any individual country, but rather their averages.
-To answer our third question, we computed country-specific estimates for each sex and age group (Figure 2).
-On average, for life satisfaction, `r tmp[1, 5]` countries credibly positive associations.
-For negative experiences, `r tmp[2, 6]` countries had a credibly negative association, and `r tmp[3, 5]` countries had a credibly positive association between DAU and positive experiences.
-There were no credible (at the 95% level) country-level negative associations between DAU and life-satisfaction.
-Although many country-level estimates were uncertain, these results aligned with the general pattern of positive associations between Facebook adoption and country-level well-being.
-
-```{r fig-ce-prepare}
-#| eval: false
-# Create a predictor table with evenly spaced mau_cw values for each country
-newx_country <- fits$data[[1]] %>% 
-  group_by(country, age, sex, mau_cb) %>% 
-  filter(mau_cw %in% c(min(mau_cw), max(mau_cw))) %>% 
-  select(country, age, sex, mau_cb, mau_cw) %>% 
-  # For above groupings, create a sequence of dau_cws from min to max
-  group_modify(
-    ~tibble(mau_cw = seq(min(.$mau_cw), max(.$mau_cw), length = 31))
-  ) %>% 
-  ungroup() %>% 
-  mutate(year = 0, se = 0)
-
-newx_world <- fits$data[[1]] %>% 
-  group_by(age, sex) %>% 
-  filter(mau_cw %in% c(min(mau_cw), max(mau_cw))) %>% 
-  select(age, sex, mau_cw) %>% 
-  # For above groupings, create a sequence of mau_cws from min to max
-  group_modify(
-    ~tibble(mau_cw = seq(min(.$mau_cw), max(.$mau_cw), length = 31))
-  ) %>% 
-  ungroup() %>% 
-  mutate(mau_cb = 0, year = 0, se = 0)
-
-newy <- fits %>% 
-  mutate(
-    country = map(
-      mau, 
-      ~bind_cols(newx_country, fitted(.x, newx_country))
-    ),
-    world = map(
-      mau, 
-      ~bind_cols(newx_world, fitted(.x, newx_world, re_formula = NA))
-    )
-  ) %>% 
-  select(outcome, country, world)
-```
-
-```{r fig-ce}
-#| eval: false
-#| include: true
-
-newy %>% 
-  pivot_longer(c(country, world)) %>% 
-  unnest(value) %>% 
-  ungroup() %>% 
-  mutate(country = if_else(name == "world", "World", country)) %>% 
-  ggplot(
-    aes(mau_cw, Estimate, group = interaction(country, sex), col = sex, fill = sex)
-  ) +
-  scale_color_brewer(
-    "Age", 
-    palette = "Dark2", 
-    aesthetics = c("color", "fill")
-  ) +
-  scale_y_continuous(
-    "Estimated outcome",
-    breaks = extended_breaks()
-  ) +
-  scale_x_continuous(
-    "Country-mean deviated monthly FB users",
-    breaks = extended_breaks(),
-    labels = ~percent(.)
-  ) +
-  scale_size_manual(values = c(.2, .4)) +
-  geom_ribbon(
-    data = . %>% filter(name == "world"),
-    aes(ymin = Q2.5, ymax = Q97.5),
-    alpha = .2, col = NA
-  ) +
-  geom_line(aes(size = name)) +
-  facet_grid(
-    age~outcome, scales = "free_y",
-    labeller = as_labeller(~str_replace(., "_", " "))
-  ) +
-  theme(legend.position = "none")
-```
-
-We found that, overall, Facebook adoption positively predicted well-being.
-This association held when comparing countries to other countries and to themselves over time.
-While these descriptive results do not speak to causal effects, they align with other recent findings suggesting that technology has not become increasingly harmful over time [@vuorreThereNoEvidence2021], and that increased adoption of general internet technologies are not, overall, associated with psychological harms [@vuorreGlobalWellbeingMental2022].
-That said, these conclusions are qualified because our focus on daily active users could miss those who use Facebook less regularly.
-To test this possibility, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor.
-Those results were substantively the same (see online supplement).
 
@@
 Both datasets (Facebook and Gallup) are proprietary and we therefore could not share them with this manuscript.
-The analytic code, along with synthetic datasets, is available at (LINK).
-Researchers can contact Facebook (ccobb@fb.com) to access our code, the Facebook data, and a synthetic version of the Gallup data for reproducing and extending our analyses.
+Our analytic code, along with synthetic datasets, is available at (LINK).
+Researchers can contact Facebook (ccobb@fb.com) to reproduce our analyses with the actual Facebook adoption dataset.
 The Gallup data are available online to subscribing institutions.
@@
 We report analyses based on DAU in the main manuscript, and MAU in the online supplement.
-DAU and MAU estimates are calculated separately for individuals aged 13-34 and 35+.
+Facebook calculates DAU and MAU estimates separately for individuals aged 13-34 and 35+.
 User age is determined based on Facebook profile information, which can be inaccurate (e.g.
-young individuals report an older age.) Accordingly, 0.008% of total MAU were trimmed to exclude accounts with unrealistic on non-reported age.
+young users reporting an older age.) Accordingly, Facebook has trimmed 0.008% of total MAU to exclude accounts with unrealistic or non-reported ages.
 
@@
 Although accurately captured, these numbers are not perfect indicators of actual user numbers because of possible duplicate and false accounts.
-FB estimates those accounts to count for 11% and 5% of global MAUs, and that the former may be more likely in developing regions.
+Facebook estimates those accounts to account for 11% and 5% of global MAUs, respectively, and that the former may be more likely in developing regions.
 Because internal criteria and methodology for determining duplicate and false accounts can change over time, estimates of MAU and DAU can also change.
@@
 \begin{aligned} 
-y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i), \\
+y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i^2), \\
 \mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \\
@@
 Where $y_i$ is the outcome (e.g.
-life satisfaction) on row $i$, $v_i$ its sampling variance, $\alpha$ are the population-level coefficients, $\beta_{0, \dots, 11\text{country}[i]}$ are the country-specific coefficients for the country indicated on row $i$, $\text{DAU}^{\text{CW}}_i$ the within-country centered year-aggregated daily (or monthly) active Facebook users, and $\text{DAU}^{\text{CB}}_i$ the between-country centered DAU (or MAU).
+life satisfaction) on row $i$, $v_i$ its standard error, $\pmb{\alpha}$ are the population-level coefficients, $\beta_{0, \dots, 11\text{country}[i]}$ are the country-specific coefficients for the country indicated on row $i$, $\text{DAU}^{\text{CW}}_i$ the within-country centered year-aggregated daily (or monthly) active Facebook users, and $\text{DAU}^{\text{CB}}_i$ the between-country centered DAU (or MAU).
 

### 2022-09-16 ms.Rmd
Commit synthetic and population data

@@
 
-output: 
-  rticles::pnas_article:
-    keep_tex: false
+output: rticles::pnas_article
 ---
@@
 # Facebook -- this data only exists on FORT
-d_fb <- read_csv("data/fb.csv")
+d_fb <- read_csv("data-raw/fb.csv")
 # If you are not conducting these analyses on FORT, the above data is not 
@@
 # Gallup
-d_gwp <- read_rds("data/gwp.rds") 
+d_gwp <- read_rds("data-raw/gwp.rds") 
 # d_gwp <- read_rds("data/gwp-SYNTHETIC.rds") # If real Gallup data not available

### 2022-09-16 ms.Rmd
Edit title

@@
 ---
-title: Estimating the association between Facebook adoption and well-being
+title: Estimating the association between Facebook adoption and well-being in 72 countries
 
@@
 To test this possibility, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor.
-Those results were substantively the same (see online supplement).
+Those results were substantively the same (see online analysis supplement; <https://doi.org/10.5281/zenodo.7086277>).
 
@@
 Both datasets (Facebook and Gallup) are proprietary and we therefore could not share them with this manuscript.
-Our analytic code, along with synthetic datasets, is available at (LINK).
+Our analytic code, along with synthetic datasets and an online analysis supplement, is available at <https://doi.org/10.5281/zenodo.7086277>.
 Researchers can contact Facebook (ccobb@fb.com) to reproduce our analyses with the actual Facebook adoption dataset.

### 2022-10-20 ms.Rmd
Submitted

@@
 title: Estimating the association between Facebook adoption and well-being in 72 countries
-
-# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
+shorttitle: Facebook and well-being
+leftheader: Facebook and well-being
 author: 
   - name: Matti Vuorre
-    affiliation: a
+    affiliation: 1
+    address: Oxford Internet Institute, University of Oxford
+    email: matti.vuorre@oii.ox.ac.uk
+    role:
+      - Design
+      - Administration
+      - Analysis
+      - Visualization
+      - Writing
   - name: Andrew K. Przybylski
-    affiliation: a,1
-address:
-  - code: a
-    address: Oxford Internet Institute, University of Oxford, 1 St Giles, Oxford OX1 3JS, United Kingdom
+    affiliation: 1
+    corresponding: yes
+    address: Oxford Internet Institute, University of Oxford
+    email: andy.przybylski@oii.ox.ac.uk
+    role:
+      - Design
+      - Administration
+      - Funding
+      - Resources
+      - Supervision
+      - Visualization
+      - Writing
 
-corresponding_author:
-  code: 1
-  text: "To whom correspondence should be addressed. E-mail: andy.przybylski@oii.ox.ac.uk"
+affiliation:
+  - id: 1
+    institution: Oxford Internet Institute, University of Oxford
 
-# For footer text
-lead_author_surname: Vuorre
+authornote: |
+  \noindent \textbf{This manuscript is not yet peer-reviewed.}
 
-author_contributions: |
-  The authors made the following contributions.
-Matti Vuorre: Design, Administration, Analysis, Visualization, Writing; Andrew K.
-Przybylski: Design, Administration, Funding, Resources, Super- vision, Visualization, Writing.
+  This research was supported by the Huo Family Foundation and Economic and Social Research Council Grant ES/T008709/1.
 
-## Remove this if not required
-conflict_of_interest: |
-  The authors declare no conflicts of interest.
+  This study and methodology was reviewed and approved by the Oxford Internet Institute's Departmental Research Ethics Committee (SSH_OII_CIA_21_084). The authors declare no conflicts of interest.
 
 abstract: |
-  Social media's potential effects on well-being have received considerable research interest, but much of past work is hampered by an exclusive focus on demographics in the Global North and inaccurate self-reports of social media engagement.
+  \textbf{Abstract} Social media's potential effects on well-being have received considerable research interest, but much of past work is hampered by an exclusive focus on demographics in the Global North and inaccurate self-reports of social media engagement.
 We describe associations linking 72 countries' Facebook adoption to the well-being of 946,798 individuals from 2008 to 2019.
-We found no associations suggesting that the global penetration of social media has caused widespread psychological harm: Facebook adoption predicted life satisfaction and positive experiences positively, and negative experiences negatively, both between countries and within countries but over time, and the associations were small.
-Facebook adoption was more positively associated with well-being for younger individuals, but country-specific results were mixed.
-In order to move beyond studying aggregates and to better understand social media's causal effects, we need more transparent collaborative research between independent scientists and the technology industry.
+We found no evidence suggesting that the global penetration of social media is associated with widespread psychological harm: Facebook adoption predicted life satisfaction and positive experiences positively, and negative experiences negatively, both between countries and within countries but over time.
+The observed associations were small.
+Facebook adoption predicted well-being more positively for younger individuals, but country-specific results were mixed.
+To move beyond studying aggregates and to better understand social media's roles in people's lives, and their potential causal effects, we need more transparent collaborative research between independent scientists and the technology industry.
+\linebreak[4]
 
-significance: |
-  Billions of individuals across the globe use social media on a regular basis.
+  \textbf{Statement of relevance} Billions of individuals across the globe use social media on a regular basis.
 The widespread adoption of social media---most prominently Facebook---has fundamentally shifted how humans conduct their lives.
@@
 
-# acknowledgements: |
-#   Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.
-
-keywords:
-  - well-being
-  - social media
-
-## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
-pnas_type: pnasresearcharticle
-
-bibliography: references.bib
-csl: pnas.csl
-
-## change to true to add optional line numbering
-lineno: true
-
-output: rticles::pnas_article
+keywords: well-being, social media
+wordcount: "`r wordcountaddin:::word_count(filename = 'ms.Rmd')`"
+bibliography: "references.bib"
+floatsintext: yes
+linenumbers: yes
+draft: no
+mask: yes
+figurelist: no
+tablelist: no
+footnotelist: no
+header-includes:
+  - |
+    \setlength{\parskip}{0pt}
+    \setlength\parindent{24pt}
+csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass: apa7
+classoption: doc
+output: 
+  papaja::apa6_pdf:
+    number_sections: false
+    keep_tex: false
+  papaja::apa6_docx: 
+    number_sections: false
+always_allow_html: true
 ---
-
-\raggedbottom
 
@@
   theme_linedraw(
-    base_size = 8
+    base_size = 10
   ) +
@@
 )
+
+# Function to replace extreme percentages
+percent2 <- function(x, accuracy = .1) {
+  x <- percent(x, accuracy = accuracy)
+  x <- if_else(x == "100.0%", ">99.9%", x)
+  x <- if_else(x == "0.0%", "<0.1%", x)
+  x
+}
 ```
@@
   )
+
+  # Summarise hypotheses with pd
+  hsum <- function(fit, hypothesis) {
+    h1 <- hypothesis(fit, hypothesis)
+    out1 <- describe_posterior(
+      h1$samples, 
+      centrality = "mean", 
+      test = "pd"
+    ) %>% 
+      mutate(
+        Hypothesis = h1$hypothesis$Hypothesis, 
+        country = "World",
+        .before = 1
+      ) %>% 
+      select(-CI, -Parameter) %>% 
+      tibble()
+    h2 <- hypothesis(fit, hypothesis, scope = "coef", group = "country")
+    out2 <- describe_posterior(
+      h2$samples, 
+      centrality = "mean", 
+      test = "pd"
+    ) %>% 
+      mutate(
+        Hypothesis = h2$hypothesis$Hypothesis, 
+        country = h2$hypothesis$Group, 
+        .before = 1
+      ) %>% 
+      select(-CI, -Parameter) %>% 
+      tibble
+    bind_rows(out1, out2)
+  }
+
   coefs <- fits %>% 
@@
     mutate(
-      world = map2(
+      coefs = map2(
         fit, h,
-        ~hypothesis(.x, .y) %>% 
-          .[["hypothesis"]] %>%
-          tibble()
-      ),
-      country = map2(
-        fit, h,
-        ~hypothesis(.x, .y, scope = "coef", group = "country") %>%
-          .[["hypothesis"]] %>%
-          tibble()
+        ~hsum(.x, .y)
       )
     ) %>% 
-    select(-fit, -h)
-
-  # Both predictor and outcome are 0-1, so scale can be interpreted as % change as a function of % change
-
-  coefs <- coefs %>% 
-    pivot_longer(c(world, country)) %>% 
-    unnest(value) %>% 
-    mutate(
-      country = if_else(name == "country", as.character(Group), "World")
-    ) %>% 
+    select(-fit, -h) %>% 
+    unnest(coefs) %>% 
     # Between country contrast not country-specific!
-    filter(!(Hypothesis == "Between-country" & country != "World")) %>% 
-    # Neatly formatted result string
-    mutate(
-      across(c(Estimate, CI.Lower, CI.Upper), list("str" = ~number(., .01))),
-      result = str_glue("{Estimate_str}% [{CI.Lower_str}, {CI.Upper_str}]")
-    )
+    filter(!(Hypothesis == "Between-country" & country != "World"))
 
@@
 To better understand the plausible range of associations, we linked data tracking Facebook's global adoption with three indicators of well-being.
-We examined 72 countries' per capita daily active Facebook users (DAU) in two age brackets (13-34 and 35+ years) as predictors of life satisfaction (LS), negative (NE), and positive psychological experiences (PE) at the level of years spanning 2008 to 2019.
+We examined 72 countries' per capita active Facebook users in two age brackets (13-34 and 35+ years) as predictors of life satisfaction (LS), negative (NE), and positive psychological experiences (PE) at the level of years spanning 2008 to 2019.
 The well-being data represented 946,798 individuals' responses from the nationally representative Gallup World Poll Survey [@gallupHowDoesGallup2014].
@@
 And finally, how might these associations have differed between countries?
+In addition, we were interested in whether the intensity of use might make a difference, and therefore conducted our analyses separately for daily active users and monthly active users.
 
-```{r tab-world}
-#| echo: false
-#| include: true
-
-# Average within- and between-country associations
-tab_world <- coefs %>% 
-  filter(
-    name == "world",
-    Hypothesis %in% c("Average", "Between-country")
-  ) %>% 
-  mutate(
-    outcome = case_when(
-      outcome == "Life_satisfaction" ~ "LS",
-      outcome == "Negative_experiences" ~ "NE",
-      outcome == "Positive_experiences" ~ "PE"
-    )
-  ) %>% 
-  select(
-    predictor, Outcome = outcome, Hypothesis, result
-  ) %>% 
-  pivot_wider(names_from = Hypothesis, values_from = result) %>% 
-  rename(
-    `Within country` = Average,
-    `Between country` = `Between-country`
-  ) %>% 
-  select(predictor, Outcome, `Between country`, `Within country`) %>% 
-  arrange(predictor, Outcome)
-
-tab_world %>% 
-  filter(predictor == "dau") %>% 
-  select(-predictor) %>% 
-  mutate(
-    across(
-      ends_with("country"), 
-      ~if_else(str_starts(., "-"), ., paste0("\\phantom{-}", .))
-    )
-  ) %>% 
-  apa_table(
-    caption = "Average Facebook DAU and well-being associations",
-    font_size = "small",
-    note = "LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences. Numbers indicate posterior means and 95\\%CIs.",
-    span_text_columns = FALSE,
-    escape = FALSE,
-    placement = "htb",
-    align = 'llll'
-  )
-```
-
-```{r}
-# How many people in GWP data
-d_gwp %>% 
-  group_by(outcome) %>% 
-  summarise(n = sum(n)) %>% 
-  pull(n) %>% max %>% number
-
-# Percentages of countries where DAU was over 25% by year
-tmp <- d_fb %>% 
-  group_by(year, age) %>% 
-  summarise(median_dau = percent(median(dau))) %>% 
-  pivot_wider(names_from = age, values_from = median_dau)
-tmp
-```
-
-Facebook adoption increased markedly from 2008 when the median per capita DAU across these 72 countries was `r tmp[1,2]` (ages 13-34) and `r tmp[1,3]`% (35+), to `r tmp[12,2]` (13-34) and `r tmp[12,3]` (35+; Figure 1A) in 2019.
-During this period Facebook adoption by younger individuals plateaued before saturation in many countries, but not for older individuals.
-At the same time, we did not observe correspondingly large and uniform changes across measures of well-being (Figure 1B) [@vuorreGlobalWellbeingMental2022].
-
-To answer our first question of how Facebook adoption relates to well-being, we specified a multilevel linear meta-regression model of each well-being outcome on time, sex, age, and DAU (both within- and between-country-centered, see SI).
-We included all interactions between sex, age, and time, and sex, age, and DAU (within-country-centered), and allowed all parameters to vary randomly across countries.
-We first examined whether the relative standing of countries on their average Facebook adoption predicted well-being (the model's between-country associations).
-We found that countries with greater average DAU had somewhat higher levels of life satisfaction and positive experiences, and lower levels of negative experiences than countries with lower DAU (Table 1).
-However, there are large and important differences between countries in factors that might underlie differences in both social media adoption and well-being, such as socioeconomic conditions.
-While descriptively informative, these associations are likely to indicate between-country confounding factors.
-
-```{r fig-data, fig.pos = "H"}
-#| include: true
-#| fig.height: 3.6
-#| fig.width: 3.5
-#| fig.cap: "A.
-72 countries' daily active Facebook users in two age brackets from 2008 to 2019.
-(Percentages may exceed 100\\% due to inaccurate estimation of either DAU or population size.) B.
-The same 72 countries' mean responses to three well-being scales in the Gallup World Poll from 2008 to 2019, separated by age category and sex.
-LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences."
-
-# Figure of all variables over time
-p_a <- d_fb %>% 
-  ggplot(aes(year, dau, group = country)) +
-  scale_y_continuous(
-    "Percentage of population", 
-    expand = expansion(.03),
-    breaks = extended_breaks(),
-    labels = ~percent(.)
-  ) +
-  scale_x_continuous(
-    "Year", 
-    breaks = seq(2008, 2018, by = 2), 
-    labels = ~str_replace(., "20", "'"),
-    expand = expansion(0.01)
-  ) +
-  geom_line(size = .125) +
-  # geom_smooth(group = 1, method = "gam", se = F) +
-  facet_wrap("age", nrow = 1) +
-  theme(
-    legend.position = "none",
-    axis.title.x = element_blank()
-  ) +
-  theme(
-    strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
-    text = element_text(size = 5)
-    )
-
-p_b <- d %>% 
-  # Exclude rows where FB data existed but not GWP data
-  drop_na(val) %>% 
-  # Actual lowest age in GWP
-  mutate(age = factor(age, labels = c("15-34", "35+"))) %>% 
-  mutate(
-    outcome = case_when(
-      outcome == "Life_satisfaction" ~ "LS",
-      outcome == "Negative_experiences" ~ "NE",
-      outcome == "Positive_experiences" ~ "PE"
-    )
-  ) %>% 
-  mutate(panel = str_glue("{age} ({sex})")) %>% 
-  ggplot(aes(year, val, group = country)) +
-  scale_color_brewer(palette = "Dark2") +
-  scale_y_continuous(
-    "Value", 
-    expand = expansion(.01),
-    breaks = extended_breaks(),
-    labels = ~percent(.)
-  ) +
-  scale_x_continuous(
-    "Year", 
-    breaks = seq(2008, 2018, by = 2),
-    labels = ~str_replace(., "20", "'")
-  ) +
-  geom_line(size = .1) +
-  facet_grid(
-    outcome~panel, 
-    scales = "free_y",
-    labeller = as_labeller(~str_replace(., "_", " "))
-  ) +
-  theme(
-    strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
-    strip.text.y = element_text(margin = margin(0,2,0,2, "pt")),
-    legend.position = "none",
-    text = element_text(size = 5)
-  )
-
-(p_a / p_b) +
-  plot_layout(heights = c(3, 7)) +
-  plot_annotation(tag_levels = "A")
-```
-
-Variations in such confounding factors are likely to be significantly smaller within countries over time.
-We therefore next focused on the model's within-country associations, which measure the extent to which Facebook adoption in a given country predicted well-being in that country adjusting for general linear temporal trends in the well-being outcome.
-On average across age, and sex, we found that years with greater than the country's average DAU were associated with greater levels of life satisfaction and positive experiences, and lower levels of negative experiences (Table 1), although the first association's 95%CI contained zero.
-For the average country in our sample, Facebook adoption positively predicted well-being.
-The magnitudes of these associations were small; a one-percent increase in DAU predicted a `r tab_world[3,4]` increase in positive experiences for the average country.
-While these associations indicate relations within countries and adjust for confounders that vary linearly with time by including time as a predictor, they are still susceptible to confounders and do not indicate causal relations.
-Rather, this association describes that, all else being equal, years with greater Facebook adoption tended to be those with greater levels of well-being.
-
-```{r demographics}
-coefs %>% 
-  filter(
-    str_detect(Hypothesis, " by "), 
-    name == "world"
-  ) %>% 
-  select(
-    Predictor = predictor, Outcome = outcome, Hypothesis, result
-  ) %>% 
-  pivot_wider(names_from = Outcome, values_from = result)
-coefs %>% 
-  filter(
-    Hypothesis %in% c("13-34", "35+", "Female", "Male"),
-    name == "world"
-  ) %>% 
-  select(
-    Predictor = predictor, Outcome = outcome, Hypothesis, result
-  ) %>% 
-  pivot_wider(names_from = Outcome, values_from = result)
-
-tab_demo <- coefs %>% 
-  filter(
-    str_detect(Hypothesis, "_"),
-    name == "world"
-  ) %>% 
-  select(
-    Predictor = predictor, Outcome = outcome, Hypothesis, result
-  ) %>% 
-  pivot_wider(names_from = Outcome, values_from = result)
-tab_demo
-```
-
-We then turned to our second question and assessed whether within-country associations linking Facebook adoption to well-being differed between age and sex.
-Differences in the associations were greater between the younger and older demographics than they were between females and males (Figure 2, Average).
-DAU predicted life satisfaction more positively in the younger age bracket, but these estimates' CIs did not exclude zero.
-DAU predicted negative experiences negatively only in the younger age group.
-These differences were less pronounced for positive experiences.
-These results show that Facebook adoption was, for the average nation in our sample, more positively predictive of well-being for individuals below 35, and that differences between males and females were generally smaller than those between age groups.
-Importantly, they did not indicate that the well-being of younger individuals is particularly linked to social media adoption.
-
-```{r}
-# Can we show regions in the forest plot as secondary axis? 
-# Table of percentages of countries with credible associations
-tmp <- coefs %>% 
-  filter(name == "country", Hypothesis == "Average") %>% 
-  group_by(predictor, outcome, Star, direction=sign(Estimate)) %>% 
-  count() %>% 
-  group_by(predictor, outcome) %>% 
-  # mutate(n = percent(n / sum(n), 1)) %>% 
-  mutate(x = interaction(Star, direction)) %>% 
-  select(-Star, -direction) %>% 
-  pivot_wider(names_from=x, values_from=n) %>% 
-  replace_na(list(`.-1` = 0, `.1` = 0, `*.1` = 0, `*.-1` = 0))
-tmp
-coefs %>% 
-  filter(predictor == "dau", name == "country", Hypothesis == "Average") %>% 
-  filter(Star=="*") %>% 
-  arrange(outcome, country) %>% 
-  select(outcome, country, Estimate:CI.Upper)
-```
-
-However, while informative aggregates, these results do not describe associations between Facebook adoption and well-being for any individual country, but rather their averages.
-To answer our third question, we computed country-specific estimates for each sex and age group (Figure 2).
-For life satisfaction, `r tmp[1, 5]` countries had credibly positive average associations.
-For negative experiences, `r tmp[2, 6]` countries had credibly negative average association, and `r tmp[3, 5]` countries had a credibly positive average association between DAU and positive experiences.
-There were no credible (at the 95% level) country-level negative associations between DAU and life-satisfaction.
-Although many country-level estimates were uncertain, these results aligned with the general pattern of positive associations between Facebook adoption and country-level well-being.
-
-We found that, overall, Facebook adoption positively predicted well-being.
-This association held when comparing countries to other countries and to themselves over time.
-While these descriptive results do not speak to causal effects, they align with other recent findings suggesting that technology has not become increasingly harmful over time [@vuorreThereNoEvidence2021], and that the increased adoption of Internet technologies is not, overall, associated with widespread psychological harms [@vuorreGlobalWellbeingMental2022].
-That said, these conclusions are qualified because our focus on daily active users could miss those who use Facebook less regularly.
-To test this possibility, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor.
-Those results were substantively the same (see online analysis supplement; <https://doi.org/10.5281/zenodo.7086277>).
-
-```{r fig-forest, fig.pos="H"}
-#| echo: false
-#| include: true
-#| fig.height: 4.2
-#| fig.width: 3.5
-#| fig.cap: "Forest plot of estimated associations between country-year level per-capita daily active Facebook users (DAU) and life satisfaction (LS), negative experiences (NE), and positive experiences (PE).
-Units indicate percentage change in outcome as function of percentage increase in within-country centered DAU.
-Filled points indicate estimates whose posterior 95\\%CI excluded zero.
-See the online supplementary materials for corresponding figure but with MAU as predictor."
-
-tmp <- coefs %>%   
-  filter(
-    # name != "world",
-    str_detect(Hypothesis, "_")
-  ) %>% 
-  separate(Hypothesis, c("Age", "Sex"), sep = "_") %>% 
-  mutate(
-    outcome = case_when(
-      outcome == "Life_satisfaction" ~ "LS",
-      outcome == "Negative_experiences" ~ "NE",
-      outcome == "Positive_experiences" ~ "PE"
-    )
-  ) %>% 
-  # mutate(outcome = str_glue("{outcome} ({Sex})")) %>% 
-  filter(predictor == "dau")
-
-tmp %>%
-  ggplot() +
-  aes(
-    x = Estimate, 
-    y = fct_rev(country), 
-    col = Age, 
-    fill = interaction(Age, Star, sep = " "), 
-    shape = Sex
-  ) +
-  scale_y_discrete(
-    "Country",
-    expand = expansion(.015),
-    labels = ~str_replace(., "World", "Average")
-  ) +
-  scale_x_continuous(
-    "Association with daily active Facebook users (95%CI)",
-    breaks = extended_breaks(7),
-    expand = expansion(.1)
-  ) +
-  scale_shape_manual(
-    values = c(21, 22)
-  ) +
-  scale_color_brewer(
-    "Age", palette = "Set1", aesthetics = c("color")
-  ) +
-  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
-  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
-  geom_linerangeh(
-    aes(xmin = CI.Lower, xmax = CI.Upper),
-    size = .15, position = position_dodge2v(.7), 
-    show.legend = FALSE
-  ) +
-  geom_point(
-    size = .65, stroke = .45,
-    position = position_dodge2v(.7)
-  ) +
-  facet_wrap(
-    "outcome", scales = "free_x", nrow = 1,
-    labeller = as_labeller(~str_replace(., "_", " "))
-  ) +
-  guides(
-    fill = "none",
-    color = guide_legend(override.aes = list(size = 1.5)),
-    shape = guide_legend(override.aes = list(size = 1.5))
-  ) +
-  theme(
-    text = element_text(size = 5),
-    strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
-    axis.text.y = element_text(size = rel(0.9)),
-    axis.title.y = element_blank(),
-    panel.grid.major.y = element_line(
-      size = .1, linetype = 2, color = "gray60"
-    ),
-    legend.position = "bottom", 
-    legend.box.margin = margin(-15, 0, -10, 0, "pt"),
-    legend.background = element_rect(fill = NA),
-    legend.key = element_rect(fill = NA),
-    legend.text = element_text(size = rel(0.9))
-  )
-```
-
-It is widely accepted that social media and the Internet more broadly have changed how humans socialize, organize, and seek leisure, but it is not obvious or necessary that their wide adoption has influenced well-being.
-In this study we used the best data available to describe how global Facebook adoption relates to well-being across 72 countries over a 12-year period.
-We found generally positive associations between Facebook adoption and well-being which were partially qualified by demographics and not uniform across countries.
-
-We did not find evidence that increased social media adoption is consistently negatively associated with well-being.
-Nevertheless, our analyses cannot and do not rule out that possibility because more fine-grained data needed to demonstrate this more conclusively either do not exist or are not available.
-If we are to move past description to prediction or intervention, independent scientists and online platforms will need to collaborate in new, transparent ways.
-As it stands now, only a handful of scientists working in the technology industry have the data required to advance this line of inquiry.
-If we are to understand and improve well-being in the digital age, this must change.
-
-# References
-
-::: {#refs}
-:::
-
-# Supporting information
+# Methods
 
@@
 Our analytic code, along with synthetic datasets and an online analysis supplement, is available at <https://doi.org/10.5281/zenodo.7086277>.
+This study was not preregistered.
 Researchers can contact Facebook (ccobb@fb.com) to reproduce our analyses with the actual Facebook adoption dataset.
@@
 Before analysing the data, we converted Facebook DAU and MAU to proportions of each country's and age group's yearly population sizes using population data from the United Nations Department of Economic and Social affairs (<https://population.un.org/wpp/Download/Standard/Population/>).
+No observations were removed for analyses.
 
 We examined the association between Facebook adoption and well-being through bayesian hierarchical regression models, estimated separately for DAU and MAU, and each of the three well-being outcomes.
-We regressed the outcome $y$ on time (decades, centered on 2014), within-country centered $x$ (DAU / MAU), age, sex, all the interactions except time by $x$, and the between-country centered DAU.
+We regressed the outcome $y$ on time (decades, centered on 2014), within-country centered DAU or MAU (in separate models), age, sex, all the interactions except time by DAU/MAU, and the between-country centered DAU/MAU.
 We allowed all coefficients to vary randomly across the 72 countries, except the between-country predictor.
-Because we aggregated the outcomes, we included to standard errors of the outcome in the model to account for the varying group sizes.
+Because we aggregated the outcomes, we included to standard errors of the outcome in the model to account for the varying group sizes and resulting uncertainties in the modelled data.
 Formally, we specified the model as
@@
 \begin{aligned} 
-y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i^2), \\
+y_i &\sim \text{Normal}(\mu_i, \sqrt{\sigma^{2} + \text{se}_i^2}), \\
 \mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \\
@@
 Where $y_i$ is the outcome (e.g.
-life satisfaction) on row $i$, $v_i$ its standard error, $\pmb{\alpha}$ are the population-level coefficients, $\beta_{0, \dots, 11\text{country}[i]}$ are the country-specific coefficients for the country indicated on row $i$, $\text{DAU}^{\text{CW}}_i$ the within-country centered year-aggregated daily (or monthly) active Facebook users, and $\text{DAU}^{\text{CB}}_i$ the between-country centered DAU (or MAU).
+life satisfaction) on row $i$, $\text{se}_i$ its standard error, $\pmb{\alpha}$ are the population-level coefficients, $\beta_{0, \dots, 11\text{country}[i]}$ are the country-specific coefficients for the country indicated on row $i$, $\text{DAU}^{\text{CW}}_i$ the within-country centered year-aggregated daily (or monthly) active Facebook users, and $\text{DAU}^{\text{CB}}_i$ the between-country centered DAU (or MAU).
 
-We conducted all data analyses with the R language for statistical computing [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan’s Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017].
+We conducted all data analyses with the R language for statistical computing [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan’s Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021].
 We used default noninformative priors, 4 HMC chains with 4,000 iterations and first 2,000 as warmup for 8,000 total iterations; we report all parameters with their posterior means and 95% credible intervals (posterior 2.5 and 97.5 percentiles; CI), and other posterior probabilities as indicated in text.
 
-<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
-\showmatmethods
-<!-- \showacknow -->
-\pnasbreak
+# Results
 
-\clearpage
+```{r fig-data}
+#| include: true
+#| fig.height: 4.4
+#| fig.width: 3.5
+#| fig.cap: "A.
+72 countries' daily (top) and monthly (bottom) active Facebook users in two age brackets from 2008 to 2019.
+(Percentages may exceed 100\\% due to inaccurate estimation of either DAU or population size.) B.
+The same 72 countries' mean responses to three well-being scales in the Gallup World Poll from 2008 to 2019, separated by age category and sex.
+LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences."
 
-# Online supplement to The association between Facebook adoption and well-being (Vuorre and Przybylski): Monthly active users
+# Figure of all variables over time
+p_a <- d_fb %>% 
+  pivot_longer(c(dau, mau)) %>% 
+  mutate(name = str_to_upper(name)) %>% 
+  ggplot(aes(year, value, group = country)) +
+  scale_y_continuous(
+    "Percentage of population", 
+    expand = expansion(.03),
+    breaks = extended_breaks(),
+    labels = ~percent(.)
+  ) +
+  scale_x_continuous(
+    "Year", 
+    breaks = seq(2008, 2018, by = 2), 
+    labels = ~str_replace(., "20", "'"),
+    expand = expansion(0.01)
+  ) +
+  geom_line(size = .125) +
+  # geom_smooth(group = 1, method = "gam", se = F) +
+  facet_grid(name~age) +
+  theme(
+    axis.title.x = element_blank()
+  )
 
-<!-- Prepend table & figure numbers with S and reset counters -->
-\setcounter{page}{1}
-\setcounter{table}{0}
-\setcounter{figure}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
+p_b <- d %>% 
+  # Exclude rows where FB data existed but not GWP data
+  drop_na(val) %>% 
+  # Actual lowest age in GWP
+  mutate(age = factor(age, labels = c("15-34", "35+"))) %>% 
+  mutate(
+    outcome = case_when(
+      outcome == "Life_satisfaction" ~ "LS",
+      outcome == "Negative_experiences" ~ "NE",
+      outcome == "Positive_experiences" ~ "PE"
+    )
+  ) %>% 
+  mutate(panel = str_glue("{age} ({sex})")) %>% 
+  ggplot(aes(year, val, group = country)) +
+  scale_color_brewer(palette = "Dark2") +
+  scale_y_continuous(
+    "Value", 
+    expand = expansion(.01),
+    breaks = extended_breaks(),
+    labels = ~percent(.)
+  ) +
+  scale_x_continuous(
+    "Year", 
+    breaks = seq(2008, 2018, by = 2),
+    labels = ~str_replace(., "20", "'")
+  ) +
+  geom_line(size = .1) +
+  facet_grid(
+    outcome~panel, 
+    scales = "free_y",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  )
 
-In the main document, we analysed associations between well-being and daily active Facebook users (DAU). Here, we repeat those analyses but use monthly active users (MAU) as the predictor
-
-```{r fig-data-mau, fig.pos="H"}
-#| include: true
-#| fig.height: 1.4
-#| fig.width: 3.5
-#| fig.cap: "72 countries' monthly active Facebook users in two age brackets from 2008 to 2019. (Percentages may exceed 100\\% due to inaccurate estimation of either DAU or population size.) "
-p_a + aes(y = mau)
+((p_a / p_b) &
+    theme(
+      strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
+      strip.text.y = element_text(margin = margin(0,2,0,2, "pt")),
+      text = element_text(size = 5)
+    )) +
+  plot_layout(heights = c(4, 6)) +
+  plot_annotation(tag_levels = "A")
 ```
 
-Figure S1 shows that the trends of Facebook adoption observed for DAU for mostly similar for MAU, but the overall rates were somewhat greater.
-We estimated the same model as in the main analyses; the key association parameters are shown in Table S1.
-Overall, the results were qualitatively similar, but the associations with MAU tended to be smaller.
-In addition the within-country associations between life satisfaction and negative experiences and MAU were no longer credible at the 95% level.
+```{r}
+# How many people in GWP data
+d_gwp %>% 
+  group_by(outcome) %>% 
+  summarise(n = sum(n)) %>% 
+  pull(n) %>% max %>% number
 
-```{r tab-world-mau}
+# Percentages of countries where DAU was over 25% by year
+tmp <- d_fb %>% 
+  pivot_longer(dau:mau) %>% 
+  group_by(year, name, age) %>% 
+  summarise(m = percent(mean(value))) %>% 
+  pivot_wider(names_from = year, values_from = m)
+tmp
+```
+
+Facebook adoption increased markedly from 2008, when the mean per capita DAU across these 72 countries was `r tmp[1,3]` (ages 13-34) and `r tmp[2,3]` (35+), to `r tmp[1,14]` (13-34) and `r tmp[2,14]` (35+; Figure 1A) in 2019.
+The mean MAUs in 2019 were greater at `r tmp[3, 14]` (13-34) and `r tmp[4, 14]` (35+).
+During this period Facebook adoption by younger individuals reached near 100% in many countries, but not for older individuals.
+At the same time, we did not observe correspondingly large and uniform changes across measures of well-being; life satisfaction had remained relatively stable, whereas both negative and positive experiences had slightly increased (Figure 1B) [@vuorreGlobalWellbeingMental2022].
+
+We then focused on our first question: How Facebook adoption relates to well-being in the average country and demographic.
+We first examined whether and how the relative standing of countries on their average Facebook adoption predicted well-being (between-country associations, $\alpha_{12}$).
+We found that countries with greater average daily active Facebook users (DAU) had higher levels of life satisfaction and positive experiences, and lower levels of negative experiences, than countries with lower DAU (Table 1; Between countries).
+However, there are large and important differences between countries in factors that might underlie differences in both social media adoption and well-being, such as socioeconomic conditions [@sprukInstitutionalOriginsSubjective2016].
+While descriptively informative, these associations are therefore likely to indicate between-country confounding factors.
+
+```{r tab-world}
+#| echo: false
 #| include: true
+
+# Average within- and between-country associations
+tab_world <- coefs %>% 
+  filter(
+    country == "World",
+    Hypothesis %in% c("Average", "Between-country")
+  ) %>% 
+  mutate(
+    outcome = case_when(
+      outcome == "Life_satisfaction" ~ "LS",
+      outcome == "Negative_experiences" ~ "NE",
+      outcome == "Positive_experiences" ~ "PE"
+    )
+  ) %>% 
+  mutate(
+    across(c(Mean, CI_low, CI_high), list("str" = ~number(., .01))),
+    result = str_glue(
+      "{Mean_str} [{CI_low_str}, {CI_high_str}] ({percent2(pd)})"
+    )
+  ) %>% 
+  select(
+    predictor, Outcome = outcome, Hypothesis, result
+  ) %>% 
+  pivot_wider(names_from = Hypothesis, values_from = result) %>% 
+  rename(
+    `Within-country` = Average,
+    `Between countries` = `Between-country`
+  ) %>% 
+  select(predictor, Outcome, `Between countries`, `Within-country`) %>% 
+  arrange(predictor, Outcome)
+
 tab_world %>% 
-  filter(predictor == "mau") %>% 
-  select(-predictor) %>% 
+  mutate(
+    Predictor = str_to_upper(predictor), 
+    Predictor = if_else(1:n() %in% c(1, 4), Predictor, ""),
+    .keep = "unused", .before = 1
+  ) %>% 
+  rename(X = Predictor, Y = Outcome) %>% 
   mutate(
@@
       ~if_else(str_starts(., "-"), ., paste0("\\phantom{-}", .))
+    ),
+    across(
+      ends_with("country"),
+      ~str_replace_all(., "%", "\\\\%")
     )
@@
   apa_table(
-    caption = "Average Facebook MAU and well-being associations",
-    font_size = "small",
-    note = "LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences. Numbers indicate posterior means and 95\\%CIs.",
+    caption = "Average Facebook adoption and well-being associations",
+    font_size = "scriptsize",
+    note = "LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences. Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction).",
     span_text_columns = FALSE,
     escape = FALSE,
+    midrules = 3,
     placement = "htb",
@@
 
-Overall, the average results across demographics mirrored those with DAU (Figure S2).
-However, many of the country-specific associations differed (individual countries in Figure S2).
-In sum, these results suggest that for associations at the level of countries, the aggregate intensity of use (monthly or daily) did not play a large role.
+Variations in such confounding factors are likely to be significantly smaller within countries but over time in a 12-year period.
+We therefore next focused on the model's within-country associations.
+They measure the extent to which Facebook adoption in a given country predicted well-being in that country, adjusting for temporal trends in the country's well-being outcome ($\alpha_4$).
+For the average country and across age and sex, we found that within-country increases in DAU predicted greater levels of life satisfaction and positive experiences, and lower levels of negative experiences, although only the latter association's 95%CI excluded zero (Table 1; Within-country).
 
-```{r fig-forest-mau, fig.pos="H"}
+However, these results are qualified because a focus on daily active users could miss those who use Facebook less regularly.
+To test this possibility, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor.
+Both the between- and within-country associations linking MAU and well-being were very similar to those linking DAU and well-being, although in general of smaller magnitude, and the within-country link between MAU and negative experiences was not credibly different from zero.
+
+```{r}
+tmp <- fits %>% 
+  select(outcome, predictor, fit) %>% 
+  mutate(
+    out = map(
+      fit,
+      ~describe_posterior(
+        .x, 
+        rope_range = c(-.01, .01), 
+        rope_ci = 1,
+        parameters = c("_cw$")
+      )
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out)
+tmp <- tmp %>% 
+  select(predictor, outcome, ROPE_Percentage) %>% 
+  mutate(x = percent2(1 - ROPE_Percentage), .keep = "unused") %>% 
+  pivot_wider(names_from = outcome, values_from = x)
+tmp
+```
+
+In addition to simple sign tests, we quantified evidence for the associations to be greater in magnitude to a 0.01% change as a function of 1% increase in MAU/DAU [@kruschkeBayesianNewStatistics2017].
+DAU predicted negative and positive experiences in excess of 0.01% with `r tmp[1,3]` and `r tmp[1, 4]` probability, respectively, and MAU predicted positive experiences in excess of 0.01% with `r tmp[2,4]` probability.
+In sum, then, for the average country in our sample, Facebook adoption positively predicted well-being.
+Nevertheless, our certainties in the directions of these associations were not great, and the magnitudes of these associations were small: A one-percent increase in DAU predicted a `r tab_world[3,4]` increase in positive experiences for the average country.
+While these associations indicate relations within countries and adjust for confounders that vary linearly with time by including time as a predictor, they are still susceptible to confounders and do not indicate causal relations.
+Rather, this association describes that all else being equal, years with greater Facebook adoption tended to be those with greater levels of well-being.
+
+```{r demographics}
+# Differences between ages
+age <- coefs %>% 
+  filter(
+    Hypothesis == "X by age",
+    country == "World"
+  ) %>% 
+  mutate(result = str_glue("{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .02)}] ({percent2(pd)})")) %>% 
+  select(
+    Predictor = predictor, Outcome = outcome, result
+  ) %>% 
+  pivot_wider(names_from = Outcome, values_from = result)
+
+# And sexes
+sex <- coefs %>% 
+  filter(
+    Hypothesis == "X by sex",
+    country == "World"
+  ) %>% 
+  mutate(result = str_glue("{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .02)}] ({percent2(pd)})")) %>% 
+  select(
+    Predictor = predictor, Outcome = outcome, result
+  ) %>% 
+  pivot_wider(names_from = Outcome, values_from = result)
+
+age
+sex
+```
+
+We then turned to our second question and assessed whether within-country associations linking Facebook adoption to well-being differed between age and sex.
+DAU predicted negative experiences more negatively, and MAU positive experiences more positively, for the younger age group than for the older (`r age[1, 3]`, `r age[2, 4]`).
+Other average age differences were not credibly different from zero at the 95% level.
+The association between DAU and MAU and well-being was more positive for males than it was for females, across all well-being measures, but the differences were not credibly different from zero.
+We display the average age- and sex-specific associations in the bottom row of Figure 2.
+Overall, these results indicated that the association between Facebook adoption and well-being was more positive for younger individuals, particularly for negative and positive experiences, and that sex-based differences were much smaller in magnitude and not credibly different from zero.
+
+```{r fig-forest}
 #| echo: false
 #| include: true
-#| fig.height: 4.2
-#| fig.width: 3.5
-#| fig.cap: "Forest plot of estimated associations between country-year level per-capita monthly active Facebook users (MAU) and life satisfaction (LS), negative experiences (NE), and positive experiences (PE).
-Units indicate percentage change in outcome as function of percentage increase in within-country centered MAU.
-Filled points indicate estimates whose posterior 95\\%CI excluded zero."
-
+#| fig.height: 5.4
+#| fig.width: 7
+#| out.width: "\\textwidth" 
+#| fig.env: "figure*"
+#| fig.cap: "Within-country associations between daily (left; DAU) and monthly (right; MAU) active Facebook users and life satisfaction (LS), negative experiences (NE), and positive experiences (PE).
+Units indicate percentage change in outcome as function of percentage increase in within-country centered DAU or MAU.
+Filled points indicate estimates whose 95\\%CI excludes zero."
 tmp <- coefs %>%   
   filter(
-    # name != "world",
     str_detect(Hypothesis, "_")
@@
       outcome == "Positive_experiences" ~ "PE"
+    ),
+    predictor = if_else(
+      predictor == "dau",
+      "Daily active users",
+      "Monthly active users"
       )
   ) %>% 
-  # mutate(outcome = str_glue("{outcome} ({Sex})")) %>% 
-  filter(predictor == "mau")
+  mutate(cred = pd >= .975)
 
@@
   aes(
-    x = Estimate, 
+    x = Mean, 
     y = fct_rev(country), 
     col = Age, 
-    fill = interaction(Age, Star, sep = " "), 
+    fill = interaction(Age, cred, sep = " "), 
     shape = Sex
@@
   scale_x_continuous(
-    "Association with monthly active Facebook users (95%CI)",
+    str_glue(
+      "Association with per capita Facebook users (95%CI)")
+    ,
     breaks = extended_breaks(7),
@@
   geom_linerangeh(
-    aes(xmin = CI.Lower, xmax = CI.Upper),
+    aes(xmin = CI_low, xmax = CI_high),
     size = .15, position = position_dodge2v(.7), 
@@
   ) +
-  facet_wrap(
-    "outcome", scales = "free_x", nrow = 1,
+  facet_nested(
+    ~ predictor + outcome, scales = "free_x",
     labeller = as_labeller(~str_replace(., "_", " "))
@@
   theme(
-    text = element_text(size = 5),
-    strip.text.x = element_text(margin = margin(2,0,2,0, "pt")),
-    axis.text.y = element_text(size = rel(0.9)),
+    text = element_text(size = 7),
+    axis.text.y = element_text(size = rel(0.8), vjust = 0.35),
+    axis.text.x = element_text(size = rel(0.9)),
     axis.title.y = element_blank(),
-    panel.grid.major.y = element_line(
+    panel.grid.major = element_line(
       size = .1, linetype = 2, color = "gray60"
@@
     legend.position = "bottom", 
-    legend.box.margin = margin(-15, 0, -10, 0, "pt"),
-    legend.background = element_rect(fill = NA),
-    legend.key = element_rect(fill = NA),
-    legend.text = element_text(size = rel(0.9))
+    legend.title = element_blank(),
+    legend.box.margin = margin(-10, 0, -5, 0, "pt")
   )
 ```
+
+```{r}
+# Table of percentages of countries with credible associations
+tmp <- coefs %>% 
+  filter(country != "World", Hypothesis == "Average") %>% 
+  group_by(
+    predictor, 
+    outcome, 
+    cred = pd > .975, 
+    direction = sign(Mean)
+  ) %>% 
+  count() %>% 
+  group_by(predictor, outcome) %>% 
+  # mutate(n = percent(n / sum(n), 1)) %>% 
+  mutate(x = interaction(cred, direction)) %>% 
+  select(-cred, -direction) %>% 
+  pivot_wider(names_from=x, values_from=n) %>% 
+  replace_na(list(`FALSE.-1` = 0, `FALSE.1` = 0, `TRUE.1` = 0, `TRUE.-1` = 0))
+tmp
+```
+
+However, while informative aggregates, these results do not describe associations between Facebook adoption and well-being for any individual country, but rather for the average country in this sample of 72 countries.
+To answer our third question, we computed country-specific estimates for each sex and age group (Figure 2).
+For life satisfaction, `r tmp[1, 5]` countries had credibly positive, and `r tmp[1, 6]` negative average associations with DAU.
+For negative experiences, `r tmp[2, 5]` countries had credibly positive and `r tmp[2, 6]` had negative average association.
+`r tmp[3, 5]` countries had a credibly positive average association but `r tmp[3, 6]` had a negative association, between DAU and positive experiences.
+The corresponding results but with MAU as the predictor were very similar.
+Although the country-level estimates were generally associated with large uncertainty, these results aligned with the general pattern of positive or inconclusive, rather than negative, associations between Facebook adoption and country-level well-being.
+
+# Discussion
+
+It is widely accepted that social media and the internet more broadly have changed how humans socialize, organize, and seek leisure, but it is not obvious or necessary that their wide adoption has influenced psychological well-being.
+In this study we used the best data available to describe how two measures of Facebook adoption relate to three well-being outcomes across 72 countries over a 12-year period.
+We found generally positive associations between Facebook adoption and well-being which were partially qualified by demographics and not uniform across countries.
+We did not find evidence that increased social media adoption is consistently negatively associated with well-being.
+
+Overall, per capita active Facebook users predicted positive experiences positively, and negative experiences negatively.
+These associations held when comparing countries to other countries and to themselves over time.
+Associations between Facebook adoption and life satisfaction were less certain within-countries, but strong when comparing countries to each other.
+While these descriptive results do not speak to causal effects, they align with other recent findings suggesting that technology use has not become increasingly associated with negative psychological outcomes over time [@vuorreThereNoEvidence2021], and that the increased adoption of internet technologies in general is not, overall, associated with widespread psychological harms [@vuorreGlobalWellbeingMental2022].
+We also found that Facebook adoption predicted young demographics' positive well-being more strongly than it did older demographics', and that, although males' associations were generally slightly more positive, the sex differences in this dataset were very small and not credibly different from zero.
+These demography-based differences, and lack therein, were notable in light of previous literature that has reported young girls to be more at-risk of screen- and technology-based effects than young males [e.g.
+@kellySocialMediaUse2018; but see @kreskiSocialMediaUse2021].
+We also compared results between analyses focusing on more intensive Facebook use to less intensive use (DAU and MAU, respectively), but the results were, by and large, in agreement.
+
+In this study, we aimed to most accurately describe how nation-level trends in well-being are associated with Facebook adoption.
+As such, these data are aggregated and there are likely to be large differences within countries in the degree of social media adoption and well-being that we could not address.
+Our analyses also necessarily gloss over dimensions known to moderate associations between social media use and well-being, such as whether the use is active vs.
+passive, or whether the purpose of use is goal-directed or mere procrastination [@dienlinImpactDigitalTechnology2020; @verduynSocialNetworkSites2017].
+In addition, our descriptive analyses cannot and do not rule out the possibility of causal effects, either negative or positive, between social media use and well-being.
+More fine-grained data needed to demonstrate causal relations, or lack thereof, more conclusively either do not exist or are not available to independent scientists.
+We also did not make attempts at finding a representative sample of nations to study, but rather used data from countries that Facebook determined to have the most accurate data about adoption and demographics.
+It is therefore possible that these results would not generalize beyond the sample of 72 nations studied.
+
+If we are to move past description, the goal of this study, to prediction or intervention, independent scientists and online platforms will need to collaborate in new, transparent ways.
+As it stands now, only a handful of scientists working in the technology industry have the data required to advance this line of inquiry.
+If we are to understand and improve well-being in the digital age, this must change.
+
+# References
+
+::: {#refs}
+:::

### 2022-11-04 ms.Rmd
Prepare for submission

@@
 abstract: |
-  \textbf{Abstract} Social media's potential effects on well-being have received considerable research interest, but much of past work is hampered by an exclusive focus on demographics in the Global North and inaccurate self-reports of social media engagement.
+  Social media's potential effects on well-being have received considerable research interest, but much of past work is hampered by an exclusive focus on demographics in the Global North and inaccurate self-reports of social media engagement.
 We describe associations linking 72 countries' Facebook adoption to the well-being of 946,798 individuals from 2008 to 2019.
@@
 To move beyond studying aggregates and to better understand social media's roles in people's lives, and their potential causal effects, we need more transparent collaborative research between independent scientists and the technology industry.
-\linebreak[4]
-
-  \textbf{Statement of relevance} Billions of individuals across the globe use social media on a regular basis.
-The widespread adoption of social media---most prominently Facebook---has fundamentally shifted how humans conduct their lives.
-Consequently, researchers, healthcare professionals, and policy makers have repeatedly raised alarms that the spread of social media may be negatively affecting individuals', particularly young ones', mental health and well-being on a global scale.
-We examined the plausibility of this idea by associating 72 nations' yearly Facebook adoption rates to the well-being of 946,798 individuals from 2008 to 2019.
-Overall, we found that increased rates of daily and monthly active Facebook users slightly predicted greater levels of well-being, when comparing countries to other countries, or countries to themselves but over time.
-These findings should guide debate surrounding social media towards more empirical foundations: The importance of this topic requires that independent scientists gain access to more detailed data from the technology industry in order to better determine how, when, and why modern online platforms might be affecting their users.
 
@@
 draft: no
-mask: yes
+mask: no
 figurelist: no
@@
 library(ggh4x)
-library(brms)
 library(kableExtra)
@@
 library(bayestestR)
+library(brms)
 library(tidyverse)
@@
 
+# Global burden of disease
+d_gbd <- read_rds("data/gbd.rds")
+
 # Population estimates
@@
 # Merge
-d <- left_join(d_gwp, d_fb) %>% 
-  mutate(age = factor(age, levels = c("13-34", "35+")))
+oo <- c(
+  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
+  "Anxiety", "Depression", "Selfharm"
+  )
+d <- left_join(
+  bind_rows(d_gwp, d_gbd), 
+  d_fb
+) %>% 
+  mutate(
+    age = factor(age, levels = c("13-34", "35+")),
+    outcome = factor(outcome, levels = oo)
+  )
 ```
@@
 
-# Prepare data
-dm <- d %>% 
-  # Centering predictors
+# Create centered predictors
+# Outcomes can have different countries / years, do by country
+d <- d %>% 
   # Grand mean centering so both components are zero-centered
-  mutate(across(c(dau, mau), ~. - mean(., na.rm = TRUE))) %>% 
-  group_by(country) %>%
+  group_by(outcome) %>% 
+  mutate(
+    across(
+      c(dau, mau), 
+      .fns = list(c = ~. - mean(., na.rm = TRUE))
+    )
+  ) %>% 
+  # Outcomes may have different data so do by outcome
+  group_by(outcome, country) %>%
   mutate(
     # Between
-    dau_cb = mean(dau, na.rm = TRUE),
-    mau_cb = mean(mau, na.rm = TRUE),
+    dau_cb = mean(dau_c, na.rm = TRUE),
+    mau_cb = mean(mau_c, na.rm = TRUE),
     # Within
-    dau_cw = dau - dau_cb, 
-    mau_cw = mau - mau_cb
+    dau_cw = dau_c - dau_cb, 
+    mau_cw = mau_c - mau_cb
   ) %>% 
-  ungroup() %>% 
-  # Center year so that intercepts are at 2014
-  mutate(year = year - 2014) %>% 
-  # Remove rows where predictor existed but outcome didn't
-  drop_na(val)
+  ungroup()
+
+d <- d %>% 
+  mutate(sex = factor(sex), age = factor(age))
 
@@
 )
-fits <- dm %>% 
+fits <- d %>% 
   select(outcome, year, country, sex, age, contains("_c"), val, se) %>% 
@@
         ..1,
-        cores = 4, chains = 4,
+        cores = 4,
         backend = "rstan",
         control = list(adapt_delta = .95),
-        iter = 3000,
-        data = ..2,
+        iter = 4000,
+        # Center year on 2014
+        data = mutate(..2, year = year - 2014),
         file = str_glue("models/brm-{..3}-{..4}")
@@
   )
+```
+
+```{r diagnostics}
+if (length(list.files("diagnostics")) == 0) {
+  rhats <- fits %>% 
+    mutate(
+      out = map(
+        fit, 
+        ~describe_posterior(
+          .x, 
+          ci_method = "eti", 
+          test = NULL, 
+          effects = "all",
+          parameters = "^cor_|^sd_|^b_"
+        ) %>% 
+          as_tibble() %>% 
+          select(Parameter, Rhat, ESS)
+      )
+    ) %>% 
+    select(-fit, -data, -model) %>% 
+    unnest(out)
+
+  # Show a table of bad rhats
+  rhats %>%
+    filter(!near(Rhat, 1, tol = .01)) %>% 
+    arrange(desc(Rhat))
+
+  # Draw a scatterplot of parameters with 9 worst rhats
+  # Create a tabset of this in HTML output
+  rhats_sum <- rhats %>% 
+    group_by(outcome, predictor) %>% 
+    arrange(outcome, predictor, desc(abs(Rhat))) %>% 
+    slice(1:9) %>% 
+    summarise(v = list(str_c(Parameter))) %>% 
+    ungroup() %>% 
+    right_join(select(fits, -data, -model))
+
+  dir.create("diagnostics", FALSE)
+  for (i in 1:nrow(rhats_sum)) {
+    x <- slice(rhats_sum, i)
+    path <- str_glue("diagnostics/{x$outcome}-{x$predictor}.png")
+    png(path, width = 1200, height = 1200, units = "px", res = 120)
+    pairs(x = x$fit[[1]]$fit, pars = x$v[[1]])
+    dev.off()
+
+  }
+}
 ```
@@
 In addition, we were interested in whether the intensity of use might make a difference, and therefore conducted our analyses separately for daily active users and monthly active users.
+As a supplementary analysis, we replicated and present these analyses on meta-analytic mental health outcomes in an appendix.
 
@@
 Both datasets (Facebook and Gallup) are proprietary and we therefore could not share them with this manuscript.
-Our analytic code, along with synthetic datasets and an online analysis supplement, is available at <https://doi.org/10.5281/zenodo.7086277>.
+Our analytic code, along with synthetic datasets, is available at <https://doi.org/10.5281/zenodo.7086277> [@vuorreEstimatingAssociationFacebook2022a].
 This study was not preregistered.
 Researchers can contact Facebook (ccobb@fb.com) to reproduce our analyses with the actual Facebook adoption dataset.
-The Gallup data are available online to subscribing institutions.
+The Gallup well-being data are available online to subscribing institutions.
 
@@
 
-```{r}
-# Text list of countries
-countries <- sort(unique(d_fb$country))
-countries[length(countries)] <- paste("and", countries[length(countries)])
-countries <- str_c(countries, collapse = ", ")
-```
-
-We studied two metrics of Facebook adoption, daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (see Figure 2).
+We studied two metrics of Facebook adoption, daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (see Figure \@ref(fig:fig-forest)).
 FB estimates yearly DAU & MAU with their corresponding means from June 1 to August 31, and rounds values greater than 10,000,000 to three significant digits, and values less than 10,000,000 to the nearest 10,000.
@@
 
-The NE items are responses to "Did you experience the following feelings during a lot of the day yesterday?" for physical pain, worry, sadness, stress, and anger?
+The NE items are responses to "Did you experience the following feelings during a lot of the day yesterday?" for "physical pain", "worry", "sadness", "stress", and "anger".
 For analyses we used the means of these scales.
@@
 p_b <- d %>% 
+  # GWP only
+  filter(outcome %in% oo[1:3]) %>% 
   # Exclude rows where FB data existed but not GWP data
@@
       strip.text.y = element_text(margin = margin(0,2,0,2, "pt")),
-      text = element_text(size = 5)
+      text = element_text(size = 7)
     )) +
@@
 
-Facebook adoption increased markedly from 2008, when the mean per capita DAU across these 72 countries was `r tmp[1,3]` (ages 13-34) and `r tmp[2,3]` (35+), to `r tmp[1,14]` (13-34) and `r tmp[2,14]` (35+; Figure 1A) in 2019.
+Facebook adoption increased markedly from 2008, when the mean per capita DAU across these 72 countries was `r tmp[1,3]` (ages 13-34) and `r tmp[2,3]` (35+), to `r tmp[1,14]` (13-34) and `r tmp[2,14]` (35+; Figure \@ref(fig:fig-data)A) in 2019.
 The mean MAUs in 2019 were greater at `r tmp[3, 14]` (13-34) and `r tmp[4, 14]` (35+).
 During this period Facebook adoption by younger individuals reached near 100% in many countries, but not for older individuals.
-At the same time, we did not observe correspondingly large and uniform changes across measures of well-being; life satisfaction had remained relatively stable, whereas both negative and positive experiences had slightly increased (Figure 1B) [@vuorreGlobalWellbeingMental2022].
+At the same time, we did not observe correspondingly large and uniform changes across measures of well-being; life satisfaction had remained relatively stable, whereas both negative and positive experiences had slightly increased (Figure \@ref(fig:fig-data)B) [@vuorreGlobalWellbeingMental2022].
 
@@
 We first examined whether and how the relative standing of countries on their average Facebook adoption predicted well-being (between-country associations, $\alpha_{12}$).
-We found that countries with greater average daily active Facebook users (DAU) had higher levels of life satisfaction and positive experiences, and lower levels of negative experiences, than countries with lower DAU (Table 1; Between countries).
+We found that countries with greater average daily active Facebook users (DAU) had higher levels of life satisfaction and positive experiences, and lower levels of negative experiences, than countries with lower DAU (Table \@ref(tab:tab-world)); Between countries).
 However, there are large and important differences between countries in factors that might underlie differences in both social media adoption and well-being, such as socioeconomic conditions [@sprukInstitutionalOriginsSubjective2016].
@@
       outcome == "Negative_experiences" ~ "NE",
-      outcome == "Positive_experiences" ~ "PE"
+      outcome == "Positive_experiences" ~ "PE",
+      TRUE ~ outcome
     )
@@
 tab_world %>% 
+  filter(Outcome %in% c("LS", "NE", "PE")) %>% 
   mutate(
@@
 Variations in such confounding factors are likely to be significantly smaller within countries but over time in a 12-year period.
-We therefore next focused on the model's within-country associations.
-They measure the extent to which Facebook adoption in a given country predicted well-being in that country, adjusting for temporal trends in the country's well-being outcome ($\alpha_4$).
-For the average country and across age and sex, we found that within-country increases in DAU predicted greater levels of life satisfaction and positive experiences, and lower levels of negative experiences, although only the latter association's 95%CI excluded zero (Table 1; Within-country).
+We therefore next focused on the model's within-country associations ($\alpha_4$).
+They measure the extent to which Facebook adoption in a given country predicted well-being in that country, adjusting for temporal trends in the country's well-being outcome.
+For the average country and across age and sex, we found that within-country increases in DAU predicted greater levels of life satisfaction and positive experiences, and lower levels of negative experiences, although only the latter association's 95%CI excluded zero (Table \@ref(tab:tab-world); Within-country).
 
@@
 tmp <- fits %>% 
+  filter(outcome %in% oo[1:3]) %>% 
   select(outcome, predictor, fit) %>% 
@@
 
-In addition to simple sign tests, we quantified evidence for the associations to be greater in magnitude to a 0.01% change as a function of 1% increase in MAU/DAU [@kruschkeBayesianNewStatistics2017].
+In addition to sign tests, we quantified evidence for the associations to be greater in magnitude to a 0.01% change as a function of 1% increase in MAU/DAU [@kruschkeBayesianNewStatistics2017].
 DAU predicted negative and positive experiences in excess of 0.01% with `r tmp[1,3]` and `r tmp[1, 4]` probability, respectively, and MAU predicted positive experiences in excess of 0.01% with `r tmp[2,4]` probability.
@@
   filter(
+    outcome %in% oo[1:3],
     Hypothesis == "X by age",
@@
   filter(
+    outcome %in% oo[1:3],
     Hypothesis == "X by sex",
@@
 The association between DAU and MAU and well-being was more positive for males than it was for females, across all well-being measures, but the differences were not credibly different from zero.
-We display the average age- and sex-specific associations in the bottom row of Figure 2.
+We display the average age- and sex-specific associations in the bottom row of Figure \@ref(fig:fig-forest).
 Overall, these results indicated that the association between Facebook adoption and well-being was more positive for younger individuals, particularly for negative and positive experiences, and that sex-based differences were much smaller in magnitude and not credibly different from zero.
@@
 #| include: true
-#| fig.height: 5.4
+#| fig.height: 9
 #| fig.width: 7
@@
   filter(
+    outcome %in% oo[1:3],
     str_detect(Hypothesis, "_")
@@
   mutate(
-    outcome = case_when(
-      outcome == "Life_satisfaction" ~ "LS",
-      outcome == "Negative_experiences" ~ "NE",
-      outcome == "Positive_experiences" ~ "PE"
-    ),
+    # outcome = case_when(
+    #   outcome == "Life_satisfaction" ~ "LS",
+    #   outcome == "Negative_experiences" ~ "NE",
+    #   outcome == "Positive_experiences" ~ "PE"
+    # ),
     predictor = if_else(
@@
   theme(
-    text = element_text(size = 7),
-    axis.text.y = element_text(size = rel(0.8), vjust = 0.35),
-    axis.text.x = element_text(size = rel(0.9)),
+    text = element_text(size = 9),
+    axis.text.y = element_text(size = rel(0.9), vjust = 0.35),
+    axis.text.x = element_text(size = rel(0.8)),
     axis.title.y = element_blank(),
@@
 tmp <- coefs %>% 
-  filter(country != "World", Hypothesis == "Average") %>% 
+  filter(
+    outcome %in% oo[1:3],
+    country != "World", 
+    Hypothesis == "Average"
+    ) %>% 
   group_by(
@@
 However, while informative aggregates, these results do not describe associations between Facebook adoption and well-being for any individual country, but rather for the average country in this sample of 72 countries.
-To answer our third question, we computed country-specific estimates for each sex and age group (Figure 2).
+To answer our third question, we computed country-specific estimates for each sex and age group (Figure \@ref(fig:fig-forest)).
 For life satisfaction, `r tmp[1, 5]` countries had credibly positive, and `r tmp[1, 6]` negative average associations with DAU.
@@
 It is widely accepted that social media and the internet more broadly have changed how humans socialize, organize, and seek leisure, but it is not obvious or necessary that their wide adoption has influenced psychological well-being.
-In this study we used the best data available to describe how two measures of Facebook adoption relate to three well-being outcomes across 72 countries over a 12-year period.
+In this descriptive study we used the broadest data available to describe how two measures of Facebook adoption relate to three well-being outcomes across 72 countries over a 12-year period.
 We found generally positive associations between Facebook adoption and well-being which were partially qualified by demographics and not uniform across countries.
@@
 Overall, per capita active Facebook users predicted positive experiences positively, and negative experiences negatively.
-These associations held when comparing countries to other countries and to themselves over time.
+These associations held when comparing countries to other countries as well as countries to themselves over time.
 Associations between Facebook adoption and life satisfaction were less certain within-countries, but strong when comparing countries to each other.
@@
 @kellySocialMediaUse2018; but see @kreskiSocialMediaUse2021].
-We also compared results between analyses focusing on more intensive Facebook use to less intensive use (DAU and MAU, respectively), but the results were, by and large, in agreement.
 
-In this study, we aimed to most accurately describe how nation-level trends in well-being are associated with Facebook adoption.
+We also conducted these analyses using two different metrics of Facebook adoption: Daily active users and monthly active users.
+It was important to study both, as they indicate different types of engagement with the platform, and it is possible that meaningful associations might emerge only for more intense types of engagement (daily active users).
+We found that the results were, by and large, in agreement.
+In addition, in Appendix A we studied Facebook adoption in relation to meta-analytic estimates of country-level rates of anxiety, depression, and self-harm [@vosGlobalBurden3692020].
+Those results did not indicate strong evidence either for or against associations.
+Instead, they reinforce the position that better data, on both Facebook adoption and global mental health, are urgently needed to better understand how they might relate.
+
+In this study, we aimed to accurately describe how nation-level trends in well-being are associated with Facebook adoption.
 As such, these data are aggregated and there are likely to be large differences within countries in the degree of social media adoption and well-being that we could not address.
-Our analyses also necessarily gloss over dimensions known to moderate associations between social media use and well-being, such as whether the use is active vs.
-passive, or whether the purpose of use is goal-directed or mere procrastination [@dienlinImpactDigitalTechnology2020; @verduynSocialNetworkSites2017].
+Our analyses also cannot address qualitative dimensions of engagement thought to moderate associations between social media use and well-being, such as whether the use is active or passive, or whether user motivations are goal-directed or mere procrastination [@dienlinImpactDigitalTechnology2020; @verduynSocialNetworkSites2017].
 In addition, our descriptive analyses cannot and do not rule out the possibility of causal effects, either negative or positive, between social media use and well-being.
 More fine-grained data needed to demonstrate causal relations, or lack thereof, more conclusively either do not exist or are not available to independent scientists.
-We also did not make attempts at finding a representative sample of nations to study, but rather used data from countries that Facebook determined to have the most accurate data about adoption and demographics.
+We also did not make attempts at finding a socially or geographically representative sample of nations to study, but rather used data from countries that Facebook determined to have the most accurate data about adoption and demographics.
 It is therefore possible that these results would not generalize beyond the sample of 72 nations studied.
@@
 :::
+
+\clearpage
+\onecolumn
+
+# Appendix A: Meta-analytic mental health outcomes
+
+<!-- Prepend table & figure numbers with S and reset counters -->
+\setcounter{page}{1}
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
+The main focus of this study was on well-being, as operationalized in the three Gallup World Poll measures.
+In addition, we replicated the analyses in this supplement, but used meta-analytic rates (per 100,000 individuals) of anxiety disorders (ICD10 F40-F44.9, F93-F93.2), depressive disorders (ICD10 F32-F33.9, F34.1), and self-harm (ICD10 X60-X64.9, X66-X84.9, Y87.0), as estimated by the Global Burden of Disease 2019 (GBD) study [@jamesGlobalRegionalNational2018; @vosGlobalBurden3692020] as the outcomes.
+The prevalence rate estimates are based on meta-analyses of 19,773 data sources with varying coverage for individual countries; for methodological details, see [@vosGlobalBurden3692020] and especially Appendix 1 therein.
+The prevalence rates are estimated for females and males in 5-year age groups, but we aggregated these to match the age groups in the Facebook data set.
+
+The GBD estimates are not observed data, but instead reflect the meta-analytic methods of the GBD 2019 study.
+We have compared the GBD estimates to the CDC's estimates of self-harm in the United States [@u.s.centersfordiseasecontrolandpreventionWISQARSFatalInjury2022], and found that they are likely to deviate in systematic ways from other authoritative information sources.
+Nevertheless because the GBD provides the most comprehensive dataset of global mental health, studying these estimates can be informative.
+We analysed the data as above.
+
+We have reported elsewhere, using a superset of the current countries, that rates of anxiety had increased, and rates of depression and self-harm had decreased, for the average country [@vuorreGlobalWellbeingMental2022].
+To answer our first research question, Table \@ref(tab:gbd1) reports the within- and between-country associations linking the three mental health outcomes with daily and monthly active Facebook users.
+These data did not indicate strong support for or against the idea that countries' Facebook adoption was associated with those countries' levels of mental health problems, as reflected in the parameters' wide posterior uncertainty intervals (Within-country associations in Table \@ref(tab:gbd1)).
+Similarly, none of the between-country associations' credibility intervals excluded zero, but instead indicated great uncertainty about the parameters (Between-country associations in Table \@ref(tab:gbd1)).
+
+```{r gbd1}
+#| include: !expr knitr::is_latex_output()
+tab_world %>% 
+  filter(Outcome %in% oo[4:6]) %>% 
+  mutate(
+    Predictor = str_to_upper(predictor), 
+    Predictor = if_else(1:n() %in% c(1, 4), Predictor, ""),
+    .keep = "unused", .before = 1
+  ) %>% 
+  rename(X = Predictor, Y = Outcome) %>% 
+  mutate(
+    across(
+      ends_with("country"), 
+      ~if_else(str_starts(., "-"), ., paste0("\\phantom{-}", .))
+    ),
+    across(
+      ends_with("country"),
+      ~str_replace_all(., "%", "\\\\%")
+    )
+  ) %>% 
+  apa_table(
+    caption = "Average Facebook adoption and mental health associations",
+    font_size = "scriptsize",
+    note = "Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction).",
+    span_text_columns = FALSE,
+    escape = FALSE,
+    midrules = 3,
+    placement = "htb",
+    align = 'llll'
+  )
+```
+
+```{r demographics-gbd}
+# Differences between ages
+age <- coefs %>% 
+  filter(
+    outcome %in% oo[4:6],
+    Hypothesis == "X by age",
+    country == "World"
+  ) %>% 
+  mutate(result = str_glue("{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .02)}] ({percent2(pd)})")) %>% 
+  select(
+    Predictor = predictor, Outcome = outcome, result
+  ) %>% 
+  pivot_wider(names_from = Outcome, values_from = result)
+
+# And sexes
+sex <- coefs %>% 
+  filter(
+    outcome %in% oo[4:6],
+    Hypothesis == "X by sex",
+    country == "World"
+  ) %>% 
+  mutate(result = str_glue("{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .02)}] ({percent2(pd)})")) %>% 
+  select(
+    Predictor = predictor, Outcome = outcome, result
+  ) %>% 
+  pivot_wider(names_from = Outcome, values_from = result)
+
+age
+sex
+```
+
+We then examined whether there might have been differences in the associations between the demographic groups, or between countries.
+We did not find differences between either sex or age groups in the associations linking Facebook adoption to either anxiety, depression, or self-harm (all posterior probabilities of direction were smaller than 83%.) In a similar vein, any differences between countries were very small (Figure \@ref(fig:gbd2)).
+
+```{r gbd2}
+#| echo: false
+#| include: true
+#| fig.height: 5.4
+#| fig.width: 7
+#| out.width: "\\textwidth" 
+#| fig.env: "figure*"
+#| fig.cap: "Within-country associations between daily (left; DAU) and monthly (right; MAU) active Facebook users and three mental health outcomes.
+Units indicate change in outcome rate (per 100k individuals) as function of percentage increase in within-country centered DAU or MAU.
+Filled points indicate estimates whose 95\\%CI excludes zero."
+tmp <- coefs %>%   
+  filter(
+    outcome %in% oo[4:6],
+    str_detect(Hypothesis, "_")
+  ) %>% 
+  separate(Hypothesis, c("Age", "Sex"), sep = "_") %>% 
+  mutate(
+    predictor = if_else(
+      predictor == "dau",
+      "Daily active users",
+      "Monthly active users"
+      )
+  ) %>% 
+  mutate(cred = pd >= .975)
+
+tmp %>%
+  ggplot() +
+  aes(
+    x = Mean, 
+    y = fct_rev(country), 
+    col = Age, 
+    fill = interaction(Age, cred, sep = " "), 
+    shape = Sex
+  ) +
+  scale_y_discrete(
+    "Country",
+    expand = expansion(.015),
+    labels = ~str_replace(., "World", "Average")
+  ) +
+  scale_x_continuous(
+    str_glue(
+      "Association with per capita Facebook users (95%CI)")
+    ,
+    breaks = extended_breaks(7),
+    expand = expansion(.1)
+  ) +
+  scale_shape_manual(
+    values = c(21, 22)
+  ) +
+  scale_color_brewer(
+    "Age", palette = "Set1", aesthetics = c("color")
+  ) +
+  scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
+  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
+  geom_linerangeh(
+    aes(xmin = CI_low, xmax = CI_high),
+    size = .15, position = position_dodge2v(.7), 
+    show.legend = FALSE
+  ) +
+  geom_point(
+    size = .65, stroke = .45,
+    position = position_dodge2v(.7)
+  ) +
+  facet_nested(
+    ~ predictor + outcome, scales = "free_x",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  guides(
+    fill = "none",
+    color = guide_legend(override.aes = list(size = 1.5)),
+    shape = guide_legend(override.aes = list(size = 1.5))
+  ) +
+  theme(
+    text = element_text(size = 9),
+    axis.text.y = element_text(size = rel(0.8), vjust = 0.35),
+    axis.text.x = element_text(size = rel(0.9)),
+    axis.title.y = element_blank(),
+    panel.grid.major = element_line(
+      size = .1, linetype = 2, color = "gray60"
+    ),
+    legend.position = "bottom", 
+    legend.title = element_blank(),
+    legend.box.margin = margin(-10, 0, -5, 0, "pt")
+  )
+```
+
+In summary, we extended our main analyses concerning the relationships between country-level Facebook adoption and well-being to the domain of mental health, using openly available meta-analytical estimates of anxiety, depression, and self-harm.
+Across the six models examining two facets of Facebook adoption and meta-regression estimates of three mental health outcomes, we did not find any associations that were credibly different from zero, or any differences in those associations between demographic groups or countries.
+However, these results are likely to reflect the invariance in the mental health outcomes combined with the relatively high correlations between the Facebook adoption metrics and time.
+Therefore, in order to better understand how Facebook adoption might relate to mental health, more detailed data on both Facebook adoption and mental health is urgently required.

### 2022-11-09 data-prepare.Rmd
Commit synthetic and population data

@@
 
+## GBD
+
+```{r}
+# Load data files and merge to one table
+gbd <- list.files(
+  here("data-raw/GBD/"),
+  pattern = ".zip", full.names = TRUE, recursive = TRUE
+) %>%
+  read_csv()
+
+# First step is to clean names and remove unnecessary variables
+gbd <- clean_names(gbd)
+# distinct(gbd, measure, metric)
+gbd <- select(gbd, -measure, -metric)
+
+# Clean cause names
+# distinct(gbd, cause)
+gbd <- gbd %>%
+  mutate(
+    cause = case_when(
+      cause == "Anxiety disorders" ~ "Anxiety",
+      cause == "Depressive disorders" ~ "Depression",
+      cause == "Self-harm" ~ "Selfharm"
+    )
+  )
+
+# Harmonise variable names with other datasets
+gbd <- gbd %>%
+  rename(country = location, outcome = cause)
+
+# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
+gbd <- gbd %>%
+  mutate(se = (upper - lower) / (1.96 * 2)) %>%
+  select(-c(upper, lower))
+
+# Harmonise old names and replace only if harmonised name found
+gbd <- gbd %>%
+  mutate(
+    country_harmonised = countryname(
+      country,
+      destination = "cldr.short.en"
+    )
+  ) %>%
+  # This picks the harmonised name if exists, otherwise original name
+  mutate(country = coalesce(country_harmonised, country)) %>%
+  select(-country_harmonised)
+
+# Include only FB years and countries
+gbd <- gbd %>% 
+  filter(country %in% fb_countries) %>% 
+  filter(between(year, 2008, 2019))
+
+# Categorize ages
+gbd <- gbd %>%
+  mutate(
+    age = factor(
+      if_else(
+        age %in% c("10 to 14", "15 to 19", "20 to 24", "25 to 29", "30 to 34"), 
+        "13-34", 
+        "35+"
+      )
+    )
+  )
+```
+
+```{r}
+# Aggregate to new age groups
+gbd <- gbd %>% 
+  group_by(country, year, sex, age, outcome) %>%
+  summarise(
+    val = mean(val, na.rm = TRUE),
+    se = sqrt(mean(se^2))  # average standard error
+  ) %>%
+  ungroup()
+```
+
 ## Population
@@
       destination = "cldr.short.en"
-    )
+    ),
+    year = as.numeric(year)
   )
@@
 dir.create("data", FALSE)
-write_rds(gwp, "data/gwp.rds")
+write_rds(gwp, "data-raw/gwp.rds")
+write_rds(gbd, "data/gbd.rds")
 write_rds(pop, "data/population.rds")

### 2022-11-09 ms.Rmd

@@
 bibliography: "references.bib"
-floatsintext: yes
+floatsintext: yesnc
 linenumbers: yes
@@
 FB estimates yearly DAU & MAU with their corresponding means from June 1 to August 31, and rounds values greater than 10,000,000 to three significant digits, and values less than 10,000,000 to the nearest 10,000.
-We report analyses based on DAU in the main manuscript, and MAU in the online supplement.
 Facebook calculates DAU and MAU estimates separately for individuals aged 13-34 and 35+.
@@
 We allowed all coefficients to vary randomly across the 72 countries, except the between-country predictor.
-Because we aggregated the outcomes, we included to standard errors of the outcome in the model to account for the varying group sizes and resulting uncertainties in the modelled data.
+Because we aggregated the outcomes, we included standard errors of the outcome in the model to account for the varying group sizes and resulting uncertainties in the modelled data.
 Formally, we specified the model as
@@
   mutate(
-    outcome = case_when(
-      outcome == "Life_satisfaction" ~ "LS",
-      outcome == "Negative_experiences" ~ "NE",
-      outcome == "Positive_experiences" ~ "PE",
-      TRUE ~ outcome
-    )
-  ) %>%
-  mutate(
     across(c(Mean, CI_low, CI_high), list("str" = ~number(., .01))),
@@
 tab_world %>% 
-  filter(Outcome %in% c("LS", "NE", "PE")) %>% 
-  mutate(
+  filter(Outcome %in% oo[1:3]) %>% 
+  mutate(
+    Outcome = str_replace(Outcome, "_", " "),
     Predictor = str_to_upper(predictor), 
@@
   ) %>% 
-  rename(X = Predictor, Y = Outcome) %>% 
   mutate(
@@
 They measure the extent to which Facebook adoption in a given country predicted well-being in that country, adjusting for temporal trends in the country's well-being outcome.
-For the average country and across age and sex, we found that within-country increases in DAU predicted greater levels of life satisfaction and positive experiences, and lower levels of negative experiences, although only the latter association's 95%CI excluded zero (Table \@ref(tab:tab-world); Within-country).
+For the average country and across age and sex, we found that within-country increases in DAU predicted greater levels of life satisfaction and positive experiences, and lower levels of negative experiences, although only the positive experience association's 95%CI excluded zero (Table \@ref(tab:tab-world); Within-country).
 
@@
 To test this possibility, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor.
-Both the between- and within-country associations linking MAU and well-being were very similar to those linking DAU and well-being, although in general of smaller magnitude, and the within-country link between MAU and negative experiences was not credibly different from zero.
+Both the between- and within-country associations linking MAU and well-being were very similar to those linking DAU and well-being, although in general of smaller magnitude.
+Moreover, the within-country link between MAU and negative experiences' credibility interval was narrowly centered on zero, indicating relative certainty that the association is practically equivalent to zero.
 
@@
   scale_fill_manual(values = c("white", "white", "#E41A1C", "#377EB8")) +
-  geom_vline(xintercept = 0, lty = 2, size = .25, col = "grey50") +
+  geom_vline(xintercept = 0, lty = 2, linewidth = .25, col = "grey50") +
   geom_linerangeh(

### 2023-02-03 ms.Rmd
Edits

@@
 
-To better understand the plausible range of associations, we linked data tracking Facebook's global adoption with three indicators of well-being.
+To better understand the plausible range of associations, we conducted a descriptive study that linked data tracking Facebook's global adoption with three indicators of well-being.
 We examined 72 countries' per capita active Facebook users in two age brackets (13-34 and 35+ years) as predictors of life satisfaction (LS), negative (NE), and positive psychological experiences (PE) at the level of years spanning 2008 to 2019.
@@
 As a supplementary analysis, we replicated and present these analyses on meta-analytic mental health outcomes in an appendix.
+Due to the exploratory and descriptive nature of our study, we did not have a priori hypotheses about the directions or magnitudes of the potential associations.
 
@@
 young users reporting an older age.) Accordingly, Facebook has trimmed 0.008% of total MAU to exclude accounts with unrealistic or non-reported ages.
+FB chose the 13-34 and 35+ age categories in order to maximize the accuracy of the data.
+Nevertheless, the lower age category includes groups typically defined as adolescents and young adults [@sawyerAgeAdolescence2018].
 
@@
 Facebook defines users as individuals who visited Facebook or used Messenger during the appropriate period.
+Any use (e.g.
+login) during the period was counted.
 Although accurately captured, these numbers are not perfect indicators of actual user numbers because of possible duplicate and false accounts.
@@
 For PE, these items are: "Did you feel well-rested yesterday?", "Were you treated with respect all day yesterday?", "Did you smile or laugh a lot yesterday?", "Did you learn or do something interesting yesterday?, and "(Did you experience the following feelings during a lot of the day yesterday?) How about enjoyment?".
-
 The NE items are responses to "Did you experience the following feelings during a lot of the day yesterday?" for "physical pain", "worry", "sadness", "stress", and "anger".
 For analyses we used the means of these scales.
-Life satisfaction in the moment was measured with one 11-step Likert item, "Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top.
+
+Prior studies using the NE and PE scales have found them to display acceptable validity and measurement invariance, and that response-style differences across world regions are small [@jebbSubjectiveWellBeingWorld2020].
+In addition, Gallup claims that its questions are developed "using a global network of research and political scientists [The Brookings Institution, World Bank, USAID, United Nations, Daniel Kahneman, Ed Diener, Deepak Chopra, Richard Florida, John Helliwell, Jeffrey Sachs and Arthur Stone] who understand key issues concerning question development and construction and data gathering" [@gallupWorldPollMethodology2022, p.5].
+Although not extensively validated, we believe these items and scales to be uniquely valuable for our goals due to their extensive scope across time, geo-, and demographics.
+
+Life satisfaction in the moment was measured with one 11-step Likert item, the Cantril Self Anchoring Scale (or "Cantril ladder"): "Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top.
 The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you.
-On which step of the ladder would you say you personally feel you stand at this time?".
+On which step of the ladder would you say you personally feel you stand at this time?" [@cantril1965pattern].
+In addition to inclusion in the data, we were motivated to use this scale due to its widespread use [@oecdHowLife20202020], and because of prior work establishing its reliability and validity [@kapteynDimensionsSubjectiveWellbeing2015].
+
 For analyses, we scaled these variables to percentages, and aggregated the `r number(gwp_n, big.mark = ",")` individuals’ data to means and standard errors for each country, year, sex, and age (15-34 and 35+) combination (`r number(gwp_n_groups, big.mark = ",")` cells).
@@
 @kellySocialMediaUse2018; but see @kreskiSocialMediaUse2021].
+However, those studies focused on slightly younger individuals (from 10 to 15 years old), which could at least partly explain the different findings.
 
@@
 It is therefore possible that these results would not generalize beyond the sample of 72 nations studied.
+
+We also highlight the fact that while Facebook adoption remains the overall dominant social media platform, our results do not necessarily generalize across different platforms.
+For instance, in the United States, 13 to 17 year olds are more likely to use TikTok, Instagram, and Snapchat than Facebook, so the user base of FB now consists of relatively more older individuals [@pewresearchcenterTeensSocialMedia2022].
+In addition to the demographic shifts between social media platforms, the platforms themselves change over time and their associations with well-being might therefore not be consistent over time or different countries [@vuorreThereNoEvidence2021].
+Moreover, studying a single platform cannot provide a complete picture of the overall associations that social media as a whole might have with well-being, because different platforms are used by different people and for different purposes, all of which might serve to moderate any potential associations.
 

### 2023-02-06 ms.Rmd
Save intermediates for submission

@@
     number_sections: false
-    keep_tex: false
+    keep_tex: true
   papaja::apa6_docx: 
@@
   plot_annotation(tag_levels = "A")
+ggsave("Figure-1.pdf", width = 7, height = 6, dpi = 300)
 ```
@@
   )
+ggsave("Figure-2.pdf", width = 7.2, height = 7.8, dpi = 300)
 ```
@@
   )
+ggsave("Figure-A1.pdf", width = 7.2, height = 7.8, dpi = 300)
 ```

### 2023-07-06 ms.Rmd
Clarify FB metrics

@@
 floatsintext: yesnc
-linenumbers: yes
+linenumbers: no
 draft: no
@@
 
-We studied two metrics of Facebook adoption, daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (see Figure \@ref(fig:fig-forest)).
-FB estimates yearly DAU & MAU with their corresponding means from June 1 to August 31, and rounds values greater than 10,000,000 to three significant digits, and values less than 10,000,000 to the nearest 10,000.
+We studied two metrics of Facebook adoption at the level of years and countries; daily (DAU) and monthly active users (MAU), from 2008 to 2019 for 72 countries (see Figure \@ref(fig:fig-forest)).
+DAU indicates the number of individuals who used Facebook or Messenger on a given day, and accounts for any use of either product (e.g.
+a login to Facebook).
+The FB definition of DAU was "A registered and logged-in Facebook user who visited Facebook through our website or a mobile device, or used our Messenger application (and was also a registered Facebook user), on a given day." For MAU, it was "A registered and logged-in Facebook user who visited Facebook through our website or a mobile device, or used our Messenger application (and was also registered Facebook user), in the last 30 days as of the date of measurement."
+
+To aggregate DAU to the level of years and countries as analyzed here, FB used the mean DAU in the time period from June 1st to August 31st for each year and country.
+Values greater than 10,000,000 were rounded to three significant digits, and values lower than 10,000,000 to the nearest 10,000.
+MAU was calculated identically, but accounts for any use within a one month window.
+
 Facebook calculates DAU and MAU estimates separately for individuals aged 13-34 and 35+.
@@
 
-Facebook defines users as individuals who visited Facebook or used Messenger during the appropriate period.
-Any use (e.g.
-login) during the period was counted.
 Although accurately captured, these numbers are not perfect indicators of actual user numbers because of possible duplicate and false accounts.
@@
 Because internal criteria and methodology for determining duplicate and false accounts can change over time, estimates of MAU and DAU can also change.
+
+Then, to make DAU and MAU comparable across countries and age groups, we converted them to proportions of each country's and age group's yearly population sizes using population data from the United Nations Department of Economic and Social affairs (<https://population.un.org/wpp/Download/Standard/Population/>).
+Thus, each value of DAU (MAU) below refers to the proportion of population in a given country in a given year that used Facebook or Messenger on a daily (monthly) basis.
+No observations were removed for analyses.
 
@@
 ## Data analysis
-
-Before analysing the data, we converted Facebook DAU and MAU to proportions of each country's and age group's yearly population sizes using population data from the United Nations Department of Economic and Social affairs (<https://population.un.org/wpp/Download/Standard/Population/>).
-No observations were removed for analyses.
 

### 2023-07-11 ms.Rmd

@@
   - name: Matti Vuorre
-    affiliation: 1
-    address: Oxford Internet Institute, University of Oxford
-    email: matti.vuorre@oii.ox.ac.uk
+    affiliation: "1,2"
+    address: Tilburg University
+    email: m.j.vuorre@tilburguniversity.edu
     role:
@@
   - name: Andrew K. Przybylski
-    affiliation: 1
     corresponding: yes
-    address: Oxford Internet Institute, University of Oxford
+    affiliation: "2"
     email: andy.przybylski@oii.ox.ac.uk
@@
       - Writing
-
 affiliation:
   - id: 1
+    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
+  - id: 2
     institution: Oxford Internet Institute, University of Oxford
@@
   \noindent \textbf{This manuscript is not yet peer-reviewed.}
-
   This research was supported by the Huo Family Foundation and Economic and Social Research Council Grant ES/T008709/1. 
-
   This study and methodology was reviewed and approved by the Oxford Internet Institute's Departmental Research Ethics Committee (SSH_OII_CIA_21_084). The authors declare no conflicts of interest.
@@
 We found no evidence suggesting that the global penetration of social media is associated with widespread psychological harm: Facebook adoption predicted life satisfaction and positive experiences positively, and negative experiences negatively, both between countries and within countries but over time.
-The observed associations were small.
-Facebook adoption predicted well-being more positively for younger individuals, but country-specific results were mixed.
+Nevertheless, the observed associations were small and did not reach a conventional 97.5% one-sided credibility threshold in all cases.
+Facebook adoption predicted aspects of well-being more positively for younger individuals, but country-specific results were mixed.
 To move beyond studying aggregates and to better understand social media's roles in people's lives, and their potential causal effects, we need more transparent collaborative research between independent scientists and the technology industry.
@@
     keep_tex: true
-  papaja::apa6_docx: 
-    number_sections: false
 always_allow_html: true
@@
 library(ggh4x)
-library(kableExtra)
 library(ggstance)
@@
 )
-
-# For tables: Show NAs as blanks
-options(knitr.kable.NA = '')
 
@@
 The first social media with broad adoption, MySpace (launched 2003) saw 115 million users in 2008---the year in which it was replaced as the leading platform by Facebook (2004).
-Today (2022-Q1), Facebook reports 2.94 billion monthly active users [@metaMetaReportsFirst2022], or about one third of the global population.
+In 2022 (Q1), Facebook reported 2.94 billion monthly active users [@metaMetaReportsFirst2022], or about one third of the global population.
 Along with social media's global penetration, debate surrounding their potential effects on individual and collective well-being has intensified.
 
-Although reports of negative psychological outcomes associated with social media are common in academic and popular writing [@krossFacebookUsePredicts2013; @thompsonSocialMediaAttention2021], evidence for harms is, on balance, more speculative than conclusive [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020].
+Although reports of negative psychological outcomes associated with social media are common in academic and popular writing [@krossFacebookUsePredicts2013; @thompsonSocialMediaAttention2021], empirical evidence for harms is, on balance, more speculative than conclusive [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020].
 Recent results on the associations between social media use and well-being are mixed and depend on arbitrary analytic choices [@orbenSocialMediaEnduring2019].
@@
 
-To better understand the plausible range of associations, we conducted a descriptive study that linked data tracking Facebook's global adoption with three indicators of well-being.
+Here, we took a different approach to understanding how social media might relate to well-being.
+Instead of focusing on individual-level data, we focused on trends and associations at the broad level of demographic groups within countries but over time.
+This broad approach allowed us to investigate a dramatically broader scope of geographies and demographies than previous attempts [@ghaiSocialMediaAdolescent2022].
+
+We conducted a descriptive study that linked data tracking Facebook's global adoption with three indicators of well-being.
 We examined 72 countries' per capita active Facebook users in two age brackets (13-34 and 35+ years) as predictors of life satisfaction (LS), negative (NE), and positive psychological experiences (PE) at the level of years spanning 2008 to 2019.
 The well-being data represented 946,798 individuals' responses from the nationally representative Gallup World Poll Survey [@gallupHowDoesGallup2014].
+
 We joined these unique datasets to conduct a descriptive study to answer three basic yet important questions: First, to what extent is Facebook adoption associated with well-being?
-Second, do these associations differ by age or sex.
+Second, do these associations differ by age or sex [@borAreChildAdolescent2014; @orbenSocialMediaEnduring2019; @orbenWindowsDevelopmentalSensitivity2022].
 And finally, how might these associations have differed between countries?
@@
 #| fig.height: 4.4
-#| fig.width: 3.5
+#| fig.width: 8
 #| fig.cap: "A.
@@
 The same 72 countries' mean responses to three well-being scales in the Gallup World Poll from 2008 to 2019, separated by age category and sex.
-LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences."
+LS: Life satisfaction, NE: Negative experiences: PE: Positive experiences.
+C.
+Country-year means of daily active Facebook users and three well-being metrics from 2008 to 2019 for a random sample of countries."
 
@@
   # geom_smooth(group = 1, method = "gam", se = F) +
-  facet_grid(name~age) +
+  facet_grid(
+    name~age, scales = "free_y"
+  ) +
   theme(
@@
 
-((p_a / p_b) &
+set.seed(99)
+countries_sample <- sample(unique(d$country), 6)
+p_c <- bind_rows(
+  d_fb %>% 
+    filter(country %in% countries_sample) %>% 
+    group_by(country, year) %>% 
+    summarise(val = mean(dau)) %>% 
+    ungroup() %>% 
+    mutate(outcome = "Daily active FB users"),
+  d %>% 
+    filter(
+      country %in% countries_sample,
+      outcome %in% oo[1:3]
+    ) %>% 
+    group_by(country, year, outcome) %>% 
+    summarise(val = mean(val)) %>% 
+    ungroup()
+) %>% 
+  ggplot(aes(year, val, col = outcome)) +
+  coord_cartesian(ylim = c(0, 1)) +
+  stat_summary(geom = "line") +
+  scale_color_brewer(
+    palette = "Set1",
+    labels = ~str_replace(., "_", " ")
+  ) +
+  scale_x_continuous(
+    "Year", 
+    breaks = seq(2008, 2018, by = 2), 
+    labels = ~str_replace(., "20", "'"),
+    expand = expansion(0.01)
+  ) +
+  scale_y_continuous(
+    "Value", 
+    expand = expansion(.01),
+    breaks = extended_breaks(),
+    labels = ~percent(.)
+  ) +
+  facet_wrap("country", nrow = 1) +
+  guides(color = guide_legend(override.aes = list(linewidth = 1))) +
+  theme(
+    legend.position = "bottom", 
+    legend.title = element_blank()
+  )
+
+((((p_a | p_b) + plot_layout(widths = c(4, 6))) / p_c) &
     theme(
@@
     )) +
-  plot_layout(heights = c(4, 6)) +
+  plot_layout(heights = c(7, 3)) +
   plot_annotation(tag_levels = "A")
-ggsave("Figure-1.pdf", width = 7, height = 6, dpi = 300)
+ggsave("Figure-1.pdf", width = 8, height = 4.8, dpi = 300)
 ```
@@
 At the same time, we did not observe correspondingly large and uniform changes across measures of well-being; life satisfaction had remained relatively stable, whereas both negative and positive experiences had slightly increased (Figure \@ref(fig:fig-data)B) [@vuorreGlobalWellbeingMental2022].
+We show these data in more detail in Figure \@ref(fig:fig-data)C to allow a visual comparison of Facebook adoption and well-being trends within those nations.
 
@@
 While these associations indicate relations within countries and adjust for confounders that vary linearly with time by including time as a predictor, they are still susceptible to confounders and do not indicate causal relations.
-Rather, this association describes that all else being equal, years with greater Facebook adoption tended to be those with greater levels of well-being.
+Rather, this association describes that all else being equal, years with greater Facebook adoption tended to be those with greater levels of positive experiences for the average country.
 
@@
 #| fig.height: 9
-#| fig.width: 7
+#| fig.width: 8
 #| out.width: "\\textwidth" 
@@
     axis.title.y = element_blank(),
+    strip.text = element_text(size = rel(0.7)),
     panel.grid.major = element_line(
@@
     outcome, 
-    cred = pd > .975, 
-    direction = sign(Mean)
+    cred = if_else(pd > .975, "Credible", "Not credible"), 
+    direction = if_else(sign(Mean) == 1, "Positive", "Negative")
   ) %>% 
@@
   # mutate(n = percent(n / sum(n), 1)) %>% 
-  mutate(x = interaction(cred, direction)) %>% 
+  mutate(x = interaction(cred, direction, sep = " & ")) %>% 
   select(-cred, -direction) %>% 
-  pivot_wider(names_from=x, values_from=n) %>% 
-  replace_na(list(`FALSE.-1` = 0, `FALSE.1` = 0, `TRUE.1` = 0, `TRUE.-1` = 0))
+  pivot_wider(names_from = x, values_from = n) %>% 
+  mutate(across(everything(), ~ifelse(is.na(.), 0, .)))
 tmp
@@
 To answer our third question, we computed country-specific estimates for each sex and age group (Figure \@ref(fig:fig-forest)).
-For life satisfaction, `r tmp[1, 5]` countries had credibly positive, and `r tmp[1, 6]` negative average associations with DAU.
-For negative experiences, `r tmp[2, 5]` countries had credibly positive and `r tmp[2, 6]` had negative average association.
-`r tmp[3, 5]` countries had a credibly positive average association but `r tmp[3, 6]` had a negative association, between DAU and positive experiences.
+For life satisfaction, `r tmp[1, "Credible & Positive"]` countries had credibly positive, and `r tmp[1, "Credible & Negative"]` countries negative, average associations with DAU.
+For negative experiences, `r tmp[2, "Credible & Positive"]` countries had credibly positive and `r tmp[2, "Credible & Negative"]` had negative average association.
+`r tmp[3, "Credible & Positive"]` countries had a credibly positive average association but `r tmp[3, "Credible & Negative"]` had a negative association between DAU and positive experiences.
 The corresponding results but with MAU as the predictor were very similar.
-Although the country-level estimates were generally associated with large uncertainty, these results aligned with the general pattern of positive or inconclusive, rather than negative, associations between Facebook adoption and country-level well-being.
+Overall, the country-level estimates did not lend support to the idea of widespread negative associations between social media adoption and psychological well-being.
+Nevertheless, we note that with limited data, it is difficult to determine these associations with great confidence for any given country.
 
@@
 In this descriptive study we used the broadest data available to describe how two measures of Facebook adoption relate to three well-being outcomes across 72 countries over a 12-year period.
-We found generally positive associations between Facebook adoption and well-being which were partially qualified by demographics and not uniform across countries.
+We found generally positive associations between country-level Facebook adoption and well-being which were partially qualified by demographics and not uniform across countries.
 We did not find evidence that increased social media adoption is consistently negatively associated with well-being.
 
-Overall, per capita active Facebook users predicted positive experiences positively, and negative experiences negatively.
-These associations held when comparing countries to other countries as well as countries to themselves over time.
-Associations between Facebook adoption and life satisfaction were less certain within-countries, but strong when comparing countries to each other.
-While these descriptive results do not speak to causal effects, they align with other recent findings suggesting that technology use has not become increasingly associated with negative psychological outcomes over time [@vuorreThereNoEvidence2021], and that the increased adoption of internet technologies in general is not, overall, associated with widespread psychological harms [@vuorreGlobalWellbeingMental2022].
-We also found that Facebook adoption predicted young demographics' positive well-being more strongly than it did older demographics', and that, although males' associations were generally slightly more positive, the sex differences in this dataset were very small and not credibly different from zero.
+Overall, a country's per capita daily active Facebook users predicted that nation's demography-aggregated levels of positive experiences positively, and negative experiences negatively.
+In addition, the associations between countries were similar, but the uncertainty cutoff of 97.5% for posterior probabilities of direction was strictly only met for positive experiences (Table \@ref(tab:tab-world)).
+Associations between Facebook adoption and life satisfaction were less certain within-countries, but stronger when comparing countries to each other.
+While these descriptive results do not speak to causal effects, they align with other findings suggesting that technology use has not become increasingly associated with negative psychological outcomes over time [@vuorreThereNoEvidence2021], and that the increased adoption of internet technologies in general is not, overall, associated with widespread psychological harms [@vuorreGlobalWellbeingMental2022].
+We also found that Facebook adoption predicted young demographics' positive well-being more strongly than it did older demographics', and that sex differences in this dataset were very small and not credibly different from zero.
 These demography-based differences, and lack therein, were notable in light of previous literature that has reported young girls to be more at-risk of screen- and technology-based effects than young males [e.g.
 @kellySocialMediaUse2018; but see @kreskiSocialMediaUse2021].
-However, those studies focused on slightly younger individuals (from 10 to 15 years old), which could at least partly explain the different findings.
+However, those studies focused on younger individuals (from 10 to 15 years old), which likely partly explains the different findings.
 
@@
 
-In this study, we aimed to accurately describe how nation-level trends in well-being are associated with Facebook adoption.
-As such, these data are aggregated and there are likely to be large differences within countries in the degree of social media adoption and well-being that we could not address.
-Our analyses also cannot address qualitative dimensions of engagement thought to moderate associations between social media use and well-being, such as whether the use is active or passive, or whether user motivations are goal-directed or mere procrastination [@dienlinImpactDigitalTechnology2020; @verduynSocialNetworkSites2017].
+In this study, we aimed to accurately describe how broad demographic groups' trends in well-being are associated with Facebook adoption at the level of individual countries.
+That is, we did not investigate whether e.g.
+days during which individuals use more social media are also days in which they report better or worse well-being.
+Instead, our investigation was focused on broader trends and associations.
+For example, social media use might have indirect relations to well-being among groups of individuals, such that even if an individual abstains from use, their peer group might be affected and transmit any negative effects via social contagion.
+
+For the same reason, there are likely to be large differences within countries in our aggregated data in the degree of social media adoption and well-being that we could not address.
+Our analyses also cannot address qualitative dimensions of individuals' social media use thought to moderate associations between social media use and well-being, such as whether the use is active or passive, or whether user motivations are goal-directed or mere procrastination [@dienlinImpactDigitalTechnology2020; @verduynSocialNetworkSites2017].
 In addition, our descriptive analyses cannot and do not rule out the possibility of causal effects, either negative or positive, between social media use and well-being.
